### 2014-11-18 ch2-mdf_ims.tex
First commit with initial chapter 2

\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}

An intersection is a highly-dynamic scenario that can be monitored using a wide range of sensors. For this reason, an efficient and accurate fusion of the information is needed. This chapter is divided into two sections. In the first section a brief overview of multisensor data fusion is presented, remarking in different architectures proposed in the literature and different approaches used for laser and video data fusion.
The second section contains a short review on intelligent transportation systems and intersection management systems, including current research on this topic. Finally, there will be presented some projects that include fusion of laser and video data for intersection managing applications.

\section {Multisensor Data Fusion}

Data fusion, also referred as mutisensor data fusion, information fusion or sensor fusion, has received several definitions from different authors in the literature. For example, Joint Directors of Laboratories defined data fusion as "multi-level, multifaceted process handling the automatic detection, association, correlation, estimation, and combination of data and information from several sources"\cite{White1991}. Luo refers to multisensor fusion and integration as "synergistic combination of sensory data from multiple sensors to provide more reliable and accurate information"\cite{Luo2002} and "to achieve inferences that are not feasible from each individual sensor operating separately"\cite{Luo2011}. Elmenreich states that sensor fusion is "the combining of sensory data or data derived from sensory data such that the resulting information is in some sense better than would be possible when these sources were used individually"\cite{Elmenreich2007}. In \cite{Bostrom2007} there is a compilation of more definitions of information fusion and the author summarize in his own statement, i.e., "Information fusion is the study of efficient methods for automatically or semi-automatically transforming information from different sources and different points in time into a representation that provides effective support for human or automated decision making".

% Elmenreich in [Elmenreich07]: Sensor fusion as "the combining of sensory data or data derived from sensory data such that the resulting information is in some sense better than would be possible when these sources were used individually"

%Khaleghi in [Kaleghi11]: "Multisensor data fusion is a technology to enable combining information from several sources in order to form a unified picture"

%White, JDL in [White91]: Data fusion as "multi- level, multifaceted process handling the automatic detection, association, correlation, estimation, and combination of data and information from several sources"

%Bostrom in [Bostrom07]: "Information fusion is the study of efficient methods for automatically or semi-automatically transforming information from different sources and different points in time into a representation that provides effective support for human or automated decision making"

%Luo refers to multisensor fusion and integration as "synergistic combination of sensory data from multiple sensors to provide more reliable and accurate information"\cite{Luo2002} and "to achieve inferences that are not feasible from each individual sensor operating separately"

All of previous definitions can be seen as a way to answer these three questions about data fusion:
\begin{itemize}
	\item {What is involved in data fusion?\\Combine, merge or integrate homogeneous or heterogeneous data.}
	\item {What is the aim of data fusion?\\Get a better representation of a process or the environment, infer underlying information, improve quality of the data.}
	\item {How to apply data fusion?\\Data fusion is a multi-level task, depending of the nature of the sensors, the final application and the environment.}
\end{itemize}

It is clear, now, that multisensor data fusion also is a multidisciplinary field, because information in a typical process, flows from sensors to applications, passing by stages of filtering, data enhancement and data extraction. Is for this that knowledge in a wide range of fields are required, e.g. signal processing, machine learning, probability and statistics, etc. Also, it would be pointless to try to define a general method, technique or architecture that fits the requirements of any system, for applying data fusion in it.

%\subsection{Overview}
\subsection{Architectures}

Although there is not a general rule of how to design or implement a sensor fusion system, many authors have proposed some architectures and guidelines for this task. One of the first proposals of fusion architecture, and probably one of the most widely used, is the JDL fusion model, originated from the US Joint Directors of Laboratories and described by Hall and Llinas in \cite{Hall1997} and \cite{Llinas1998}. The JDL fusion model was conceived to aid the developments of military applications and comprises 5 levels of data processing at which data fusion could be done. These levels and a database are connected by a bus (\ref{JDLmodel}), and are not meant to be execute sequentially and can also be executed concurrently.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.4]{fig/2/jdlmodel}
\caption{JDL fusion model. (from \cite{Hall1997}).}
\label{JDLmodel}
\end{figure}

\subsection{Laser and Video Data Fusion}

\section{Intersection Management Systems}
\subsection{Taxonomy}
\subsection{Intersection Management Systems and Multisensor Data Fusion}

\section{Conclusions}

Multisensor data fusion can be defined as the process of combine, merge or integrate data from homogeneous or heterogeneous set of sensors in order to get a better representation of a process, the environment or a situation, through the inference of underlying information and the improve of quality of data. Depending of the nature of the sensors and the source of information, fusion can be done in several manners, i.e., sensor-level fusion, feature-level fusion or decision-level fusion.

### 2014-11-18 main.tex
First commit with initial chapter 2

%
\documentclass{book}

\usepackage[utf8]{inputenc}
%\usepackage[spanish]{babel}
%\usepackage[spanish]{isodate}
\usepackage[final]{listings}
\usepackage{courier}

\usepackage[pdftex]{graphicx}

%\renewcommand{\chaptername}{Capítulo}
\renewcommand{\figurename}{Figure}

\lstset{	
	basicstyle=\footnotesize\ttfamily,
	language=bash,
	breaklines=true,
	fontadjust=true
}

\begin{document}

\title{Multisensor Architecture for an Intersection Management System}
\author{Gustavo Velasco-Hernández}
\date{\today}
\maketitle

\tableofcontents
\setcounter{tocdepth}{3}

\input{ch1-introduction}
\input{ch2-mdf_ims}
%\input{CH3-ES}

\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}

### 2015-01-14 ch2-mdf_ims.tex
Updated bibliography. Changed bibliography style

@@
-\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}
+%\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}
 
@@
 This chapter is divided into two sections.
-In the first section a brief overview of multisensor data fusion is presented, remarking in different architectures proposed in the literature and different approaches used for laser and video data fusion.
+In the first section a brief overview of multisensor data fusion is presented, remarking in different architectures proposed in the literature and different approaches used for laser and video data fusion are described.
 The second section contains a short review on intelligent transportation systems and intersection management systems, including current research on this topic.
-Finally, there will be presented some projects that include fusion of laser and video data for intersection managing applications.
+Finally, some projects that include fusion of laser and video data for intersection managing applications are presented.
 
-\section {Multisensor Data Fusion}
+\section{Multisensor Data Fusion}
 
@@
 Elmenreich states that sensor fusion is "the combining of sensory data or data derived from sensory data such that the resulting information is in some sense better than would be possible when these sources were used individually"\cite{Elmenreich2007}.
-In \cite{Bostrom2007} there is a compilation of more definitions of information fusion and the author summarize in his own statement, i.e., "Information fusion is the study of efficient methods for automatically or semi-automatically transforming information from different sources and different points in time into a representation that provides effective support for human or automated decision making".
+In \cite{Bostrom2007} there is a compilation of more definitions of information fusion and the author summarize in his own statement as follows: "Information fusion is the study of efficient methods for automatically or semi-automatically transforming information from different sources and different points in time into a representation that provides effective support for human or automated decision making".
 
@@
 
-It is clear, now, that multisensor data fusion also is a multidisciplinary field, because information in a typical process, flows from sensors to applications, passing by stages of filtering, data enhancement and data extraction.
-Is for this that knowledge in a wide range of fields are required, e.g.
+It is clear, now, that multisensor data fusion is a multidisciplinary field, because information in a typical process, flows from sensors to applications, passing through stages of filtering, data enhancement and data extraction.
+It is for this that knowledge in a wide range of fields are required, e.g.
 signal processing, machine learning, probability and statistics, etc.
@@
 %\subsection{Overview}
-\subsection{Architectures}
+\subsection{Data Fusion Architectures and Models}
 
-Although there is not a general rule of how to design or implement a sensor fusion system, many authors have proposed some architectures and guidelines for this task.
+Although there is not a general rule of how to design or implement a sensor fusion system, many authors have proposed some models, architectures and guidelines for this task.
+Three well-known models are Waterfall model, JDL fusion model and Multisensor integration fusion model.
+
+\subsubsection{Waterfall model}
+
+Harris and Markin in \cite{Harris1998} and CITE, proposed a model named Waterfall, in which they describe the fusion process as an information flow through sensing to decision-making.
+They describe 3 levels of processing with 2 inner stages each ((\ref{WaterfallModel}).
+The first level is about transform the raw data from sensor to a better representation of the measured phenomena through signal processing and having in mind sensor models and nature of the process itself.
+The second level objective is to find a meaningful description of the data, reducing its volume while maximising information.
+This is done using feature extraction and pattern recognition techniques.
+The third level is the high level of the process in which situation assessment and decision making are performed, based on data available, configuration parameters, database information or human interaction.
+Finally, a feedback from high-level to low-level (sensor) is done, advising the whole system for re-calibration or reconfiguration.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.4]{fig/2/WaterfallModel.png}
+\caption{Waterfall model. (from \cite{Esteban2005}).}
+\label{WaterfallModel}
+\end{figure}
+
+\subsubsection{JDL fusion model}
+
 One of the first proposals of fusion architecture, and probably one of the most widely used, is the JDL fusion model, originated from the US Joint Directors of Laboratories and described by Hall and Llinas in \cite{Hall1997} and \cite{Llinas1998}.
@@
 \centering
-\includegraphics[scale=0.4]{fig/2/jdlmodel}
+\includegraphics[scale=0.4]{fig/2/jdlmodel.png}
 \caption{JDL fusion model. (from \cite{Hall1997}).}
@@
 
-\subsection{Laser and Video Data Fusion}
+The first stage, referred as level-0 is the source preprocessing in which raw data is handled to concentrate the more pertinent data for the current situation.
+The level-1 is for object refinement, starting with the alignment of the data in a commonly space-time reference frame.
+Then, performs identification and tracking of objects using different techniques.
+Situation refinement is at level-2, which takes observed and partially-observed object from level-1 and tries to find a contextual description between them.
+Level-3, threat refinement, is the level in which results from level-2 are interpreted looking for possible advantages and disadvantages for the system to operate, based on previous knowledge and predictions about executing an action.
+
+\subsubsection{Multisensor Fusion Integration model}
+
+Luo and Kai, in \cite{Luo1989, Luo1990}, proposed a full integration model for data fusion in which they define a three-level hierarchy for sensor fusion: data-fusion, feature-fusion and decision-fusion.
+This model separate MFI in five classes, based on Input/Output pair: Data in-data out fusion, data in-feature out fusion, feature in-feature out fusion, feature in-decision out fusion, and decision in-decision out fusion \cite{Luo2011} (figure \ref{fusionClasses}).
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.25]{fig/2/fusionClasses.png}
+\caption{Five classes of Multisensor Fusion.}
+\label{fusionClasses}
+\end{figure}
+
+Also, they made a clear distinction between multisensor fusion and multisensor integration, being the former the process in which information provided by a set of sensors is combined in any of the three levels aforementioned, and the latter is how sensor fusion could be integrated in a full system in order to assist in a particular task.
+As is depicted in figure \ref{MFIArch}, sensor fusion is an element of the whole MFI architecture, which also includes block for sensor managing tasks, like control, selection and registration of sensors, previously to the fusion process.
+A sensor processing stage and a system controlling module are also included after the sensor fusion stage.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.4]{fig/2/MFIArch.png}
+\caption{Multisensor Fusion Integration architecture (from \cite{Luo2011}).}
+\label{MFIArch}
+\end{figure}
+
+\subsection{Classification of Data Fusion Architectures}
+
+Elmenreich in \cite{Elmenreich2007} classify fusion models in three categories: Abstract models, generic architectures and rigid architectures.
+Abstract model are not intended to show how to implement a sensor fusion system, but to explain which processes are done in it.
+Generic architectures gives an outline on how a system could be implemented in an application, but do not specify what type of hardware, database or communication system could be used.
+Finally, rigid architectures, are a good guide for implementation  of data fusion in certain applications, at the cost that several design decisions have been already taken, making expensive the migration to another architecture.
+
+In addition to models previously mentioned, there exists more proposal for data fusion architectures in literature, as can be viewed in figure \ref{fusionModelsClas}.
+
+% TODO: Change for a table
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.6]{fig/2/fusionModelsClas.png}
+\caption{Classification of some data fusion models}
+\label{fusionModelsClas}
+\end{figure}
+
+\subsection{Algorithms in Data Fusion}
+
+Different types of algorithms have been used in implementing data fusion systems, depending on a variety of conditions like, level of fusion, type of the data, nature of environment, etc.
+Constrains like processing and memory limitations, centralised or distributed schemes, human-interactive or completely autonomous process, also determine which algorithms should be used in fusion process.
+
+Khaleghi in \cite{Khaleghi2013} describes a classification for fusion algorithms based on challenging problems that arise from the data to be fused, due to the variety of sensors and the nature of the application environment.
+This classification is not on the algorithms directly, but on the theory or framework in which they originate.
+Four types of data are enumerated: Imperfect data, correlated data, inconsistent data and disparate data.
+For thi
+
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.275]{fig/2/fusionAlg.png}
+%\caption{Fusion algorithms based on level of fusion. (from \cite{Luo2011})}
+%\label{fusionAlgs}
+%\end{figure}
+
+%\subsection{Laser and Video Data Fusion}
 
 \section{Intersection Management Systems}
-\subsection{Taxonomy}
-\subsection{Intersection Management Systems and Multisensor Data Fusion}
+
+Intelligent Transportation Systems includes a wide range of applications and services transversal to many knowledge areas.
+For classifying those services, some taxonomies have been proposed like the ones presented in \cite[Ch.1]{Sussman2005} and \cite{Williams2008}.
+From described categories and classes, Advanced Traffic Management Systems have to be considered when an intelligent handling of traffic needs to be deployed.
+
+One of the most desirable scenarios to improve efficiency and safety is an intersection.
+This because intersections are places where vehicles arrive from different directions at different velocities, increasing the chances for incidents and crashes.
+Choi \cite{Choi2010} states that 40\% of reported traffic accidents in the US, were intersection related.
+Also, in  \cite{CorporacionFondodePrevencionVial2010}, is reported that for Colombia in 2011, most of the accidents in the main cities were at intersections.
+
+%El concepto de sistemas inteligentes de transporte (ITS), presenta un amplio campo de acci\'{o}n transversal a diferentes \'{a}reas del conocimiento e igualmente presenta una gran variedad de aplicaciones y servicios.
+Para la clasificación de estos servicios se han definido diferentes taxonom\'{i}as como las descritas en \cite[Ch.1]{Sussman2005} y en \cite{Williams2008}.
+De las clases y categor\'{i}as descritas, se tiene un subgrupo de los ITS que debe ser contemplado para cumplir con el objetivo de este proyecto, que es el que incluye los servicios y sistemas para la administraci\'{o}n y operaci\'{o}n del tr\'{a}fico (o Sistemas Avanzados de Administraci\'{o}n de Tr\'{a}fico, del ingl\'{e}s ATMS, Advanced Traffic Management Systems).
+%
+%Uno de los escenarios donde se busca mejorar la eficiencia y la seguridad usando estos sistemas son las intersecciones viales, ya que son puntos donde se encuentran veh\'{i}culos en diferentes direcciones a diferentes velocidades, lo cual incrementa la probabilidad de incidentes y choques.
+Cerca del 40\% de los accidentes de tr\'{a}nsito reportados en Estados Unidos en 2008, estaban relacionados con intersecciones \cite{Choi2010}.
+En Colombia, para el 2011 la mayor\'{i}a de accidentes en las principales ciudades del pa\'{i}s se concentraba en intersecciones \cite{CorporacionFondodePrevencionVial2010}.
+
+%\section[Types of IMS]{Types of Intersection Management Systems}
+
+Different types of applications and systems appear in order to address this issues.
+Some tasks these systems realize are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others.
+Communication approaches in these systems are based in the interaction between vehicles and infrastructure, commonly divided in three groups: Vehicle-to-vehicle communication (V2V) , Vehicle-to-infrastructure communication (V2I) and the combination of both of them (V2X).
+
+%Para afrontar esta problem\'{a}tica aparecen diferentes tipos de aplicaciones y sistemas para realizar tareas como monitoreo y administraci\'{o}n de intersecciones, detecci\'{o}n de veh\'{i}culos, advertencia de incidentes, prevenci\'{o}n de colisiones, entre otros.
+El esquema de comuniciaci\'{o}n de estos sistemas se basa en la interacci\'{o}n entre los veh\'{i}culos y la infraestructura, com\'{u}nmente dividida en 3 tipos: Comunicaci\'{o}n veh\'{i}culo a veh\'{i}culo (V2V), veh\'{i}culo a infraestructura (V2I) y la combinaci\'{o}n de las dos anteriores (V2X).
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.75]{fig/2/fig1}
+\caption{Generic block diagram of an Intersection Management System (from \cite{Chan2005}).}
+\label{arch}
+\end{figure}
+
+Figure \ref{arch}, presents a generic block diagram of an Intersection Management System composed by three main components: (a) Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, and also could be vehicle sensors.
+(b) Decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and environment in order to predict future incidents, control traffic and generate safe decisions and warnings alerts.
+Finally, (c) is the presentation and displaying of the output of decision system.
+It could be at the infrastructure using dynamic signals, semaphore controlling, or vehicle-directed through on-board visualization/notification system.
+
+%En la figura \ref{arch}, se presenta un diagrama de bloques general de un sistema de administraci\'{o}n de una intersecci\'{o}n en donde se destacan 3 componentes: (a) Las fuentes de los datos, que pueden ser sensores en la infraestructura, como sensores inductivos, sensores de rango, c\'{a}maras, o sensores en el veh\'{i}culo.
+(b) Sistema  de decisi\'{o}n o administraci\'{o}n, que es el encargado de analizar la informaci\'{o}n de los veh\'{i}culos y el entorno, predecir incidentes futuros y enviar se\~{n}ales de alerta.
+y (c) La presentaci\'{o}n de informaci\'{o}n de control, que puede ser en la infraestructura con se\~{n}ales din\'{a}micas, control de los sem\'{a}foros, como tambi\'{e}n puede ser en el veh\'{i}culo mediante un dispositivo de visualizaci\'{o}n.
+
+\subsection{Applications in IMS}
+
+Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications as traffic analysis, counting and classification of vehicles or pedestrians, events and incident detection, accidents prevention and security and surveillance applications.
+
+To complete these tasks, many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure.
+For example, monitoring mobile wireless network like Bluetooth \cite{Friesen2013}, detecting vehicle presence using inductive loops or RFID tags, identifying vehicles and pedestrian using cameras \cite{Buch2011, Strigel2013}, single or multiple laser-scanners \cite{Meissner2010, Meissner2012, Zhao2006, Zhao2008, Zhao2012}, and multi-sensor integrated systems \cite{Meissner2013, Meissner2013a, Meissner2014, GoldHammer2012, Zhao2009}.
+
+Other application are traffic-control oriented, rather than to sensing and data-processing stage.
+The aim of these applications are to maximise vehicle flow, reduce accidents and improve safety.
+Many works have been done and although its objective is the same, are diversity between them regarding its communication approach (V2V, V2I or V2X), sensors and information that are used, the execution scenario (simulation, real implementation or augmented reality) and the nature of vehicle driving (Human driver or autonomous vehicles).
+
+%El monitoreo en las intersecciones viales es una tarea requerida en los sistemas inteligentes de transporte para aplicaciones de alto nivel como  an\'{a}lisis de tr\'{a}fico, conteo y  clasificaci\'{o}n de veh\'{i}culos, detecci\'{o}n de eventos, prevenci\'{o}n de accidentes y aplicaciones de seguridad y vigilancia.
+Para cumplir con estas tareas se han propuesto diversas soluciones para obtener la informaci\'{o}n del entorno, ya sea proveniente de los veh\'{i}culos, por ejemplo monitoreando conexiones a redes m\'{o}viles, como Bluetooth \cite{Friesen2013}, detectando su presencia usando sensores inductivos o etiquetas RFID, y tambi\'{e}n tomando datos desde la infraestructura, usando c\'{a}maras  \cite{Buch2011}, sensores l\'{a}ser o arreglos de estos \cite{Zhao2012} o sistemas que integran m\'{u}ltiples tipos de sensores \cite{Zhao2009}\cite{Pyykonen2010}.
+Otras aplicaciones adem\'{a}s de monitorear y supervisar las intersecciones, est\'{a}n orientadas al control del tr\'{a}fico en estas con  el objetivo de maximizar el flujo, disminuir la accidentalidad y aumentar la seguridad.
+Diversos trabajos se han hecho y aunque su finalidad es similar, existe variedad entre s\'{i}, ya sea seg\'{u}n el tipo de comunicaci\'{o}n en la que se basan (V2V, V2I o V2X), el tipo de sensores e informaci\'{o}n que usan, el entorno de ejecuci\'{o}n (simulaci\'{o}n, real o realidad aumentada) y el tipo de veh\'{i}culos (con conductores humanos o veh\'{i}culos aut\'{o}nomos).
+
+In \cite{Ball2010} and \cite{Azimi2012}, intervehicular-communication based architectures are proposed.
+In these, each vehicle send to the others its own information about position, velocity, destination and more, and then they coordinate how the access to the intersection should be done.
+In \cite{Guerrero-Ibanez2013}, is presented a system capable of work in V2I mode, additional to V2V, using inductive loops and RFID information for detecting vehicles.
+The information is gathered by an intersection controller which manage the access to the crossroad.
+Another V2I based systems is presented in \cite{Basma2011}, where wireless magnetic nodes are used to detect presence and to send data to a base station, which determines possible collisions and warns driver through a visualisation system in infrastructure.
+Furthermore, in \cite{Dresner2008} and \cite{CondeBento2012}, are presented simulation-based systems for traffic controlling, using agents and applied to autonomous vehicles.
+In \cite{Quinlan2010}, an augmented reality implementation of the system proposed in \cite{Dresner2008} is done.
+In this work, approaching vehicles request to an intersection manager for authorisation to cross and is the manager which decides if it is safe to cross or not, depending on the defined traffic policies.
+
+%En \cite{Ball2010} y \cite{Azimi2012} se proponen arquitecturas basadas en comunicaci\'{o}n intervehicular, donde cada auto env\'{i}a a los dem\'{a}s informaci\'{o}n correspondiente a su posici\'{o}n, velocidad, destino y otros datos, y as\'{i} coordinan el acceso a la intersecci\'{o}n.
+En \cite{Guerrero-Ibanez2013} se presenta un sistema que adem\'{a}s de trabajar en modo V2V, presenta la opción V2I que incluye sensores inductivos y m\'{o}dulos RFID para detectar veh\'{i}culos.
+La informaci\'{o}n adquirida es procesada por un controlador de intersecci\'{o}n, el cu\'{a}l se encarga de administrar el ingreso al cruce vial.
+Otro sistema basado en V2I es \cite{Basma2011} donde tambien se usan nodos de sensores magnéticos inalámbricos que se comunican con una estación base, la cual mediante algoritmos de predicción determina posibles colisiones y advierte a los conductores mediante un sistema de visualización en la infraestructura.
+Por otro lado, \cite{Dresner2008} y \cite{CondeBento2012} presentan aplicaciones en simulación para el control de las intersecciones usando agentes y aplicado en vehículos autónomos.
+En \cite{Quinlan2010} se hace una implementación en realidad aumentada del sistema propuesto por Dresner y Stone \cite{Dresner2008}.
+En esta implementación, los vehículos que se aproximan a la intersección solicitan autorización al controlador para ingresar y es este quien decide cuando pueden cruzar, dependiendo de las politicas de administración definidas.
+
+%\subsection{Taxonomy}
+
+%\subsection{Intersection Management Systems and Multisensor Data Fusion}
 
@@
 Depending of the nature of the sensors and the source of information, fusion can be done in several manners, i.e., sensor-level fusion, feature-level fusion or decision-level fusion.
+
+Several models, architectures and frameworks have been proposed in literature; some of them to show how a data fusion system should work and some other providing guidelines on how to implement it in a given application.

### 2015-01-14 ch3-arch_sys.tex
Created draft for chapter 3

% Architecture Description and system specifications
% 	* Multisensor IMS
%		
%		* Processing Stages
%		* Fusion approaches
%		* Methods and techniques
%		* Architecture proposal

%	* Validation approaches
%		* Transportation and Traffic Simulations
%			* Simulators Classification
%		* Intersection monitoring Datasets
%			* POSSi Dataset
%			* KoPER Dataset

### 2015-03-20 ch2-mdf_ims.tex
Some corrections and modifications

@@
 
-Different types of applications and systems appear in order to address this issues.
-Some tasks these systems realize are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others.
+Different types of applications and systems are conceived to address these issues.
+Some tasks those systems realize are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others.
 Communication approaches in these systems are based in the interaction between vehicles and infrastructure, commonly divided in three groups: Vehicle-to-vehicle communication (V2V) , Vehicle-to-infrastructure communication (V2I) and the combination of both of them (V2X).
@@
 The aim of these applications are to maximise vehicle flow, reduce accidents and improve safety.
-Many works have been done and although its objective is the same, are diversity between them regarding its communication approach (V2V, V2I or V2X), sensors and information that are used, the execution scenario (simulation, real implementation or augmented reality) and the nature of vehicle driving (Human driver or autonomous vehicles).
+Many works have been done and although their objective is the same, are diverse between them regarding its communication approach (V2V, V2I or V2X), sensors and information that are used, the execution scenario (simulation, real implementation or augmented reality) and the nature of vehicle driving (Human driver or autonomous vehicles).
 

### 2015-03-20 ch2-mdf_ims.tex
Updated bibliography and redesigned figure 2.5 to a table

@@
 
+\begin{table}
+\centering
+\begin{tabular}{c c}
+Category & Data Fusion Model \\
+
+\hline
+\multirow{2}{*}{Abstract Model} & Waterfall Model \cite{Harris1998} \\
+& Boyd Loop \cite{Boyd1987} \\
+\hline
+\multirow{3}{*}{Generic Architecture} & JDL Model \cite{White1991} \\
+& Multisensor Fusion Integration Model \cite{Luo1989} \\
+& Omnibus model \cite{Bedworth2000} \\
+\hline
+\multirow{3}{*}{Rigid Architecture} & LAAS Architecture \cite{Alami1998} \\
+& DFuse Architecture \cite{Kumar2003} \\
+& Time-triggered Model \cite{Elmenreich2001} \\
+\hline
+\end{tabular}
+\caption{Classification of data fusion models.}
+\end{table}
+
 \subsection{Algorithms in Data Fusion}
@@
 Constrains like processing and memory limitations, centralised or distributed schemes, human-interactive or completely autonomous process, also determine which algorithms should be used in fusion process.
+
+Luo in \cite{Luo2011} propose a classification for fusion algorithms based on the level of fusion.
+Low-level fusion refers to the merge of raw data or signals, mid-level fusion refers to the fusion of features and High-level fusion refers to the process of fuse decisions.
 
@@
 
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=0.275]{fig/2/fusionAlg.png}
-%\caption{Fusion algorithms based on level of fusion. (from \cite{Luo2011})}
-%\label{fusionAlgs}
-%\end{figure}
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.175]{fig/2/ims_graph.png}
+\caption{Fusion algorithms based on level of fusion. (from \cite{Luo2011})}
+\label{fusionAlgs}
+\end{figure}
 

### 2015-03-20 ch2-mdf_ims.tex
Finished table of fusion models.

@@
 
-In addition to models previously mentioned, there exists more proposal for data fusion architectures in literature, as can be viewed in figure \ref{fusionModelsClas}.
+In addition to models previously mentioned, there exists more proposal for data fusion architectures in literature, as can be viewed in table \ref{fusionModelsClas}.
 
 % TODO: Change for a table
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.6]{fig/2/fusionModelsClas.png}
-\caption{Classification of some data fusion models}
-\label{fusionModelsClas}
-\end{figure}
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.6]{fig/2/fusionModelsClas.png}
+%\caption{Classification of some data fusion models}
+%\label{fusionModelsClas}
+%\end{figure}
 
@@
 \centering
-\begin{tabular}{c c}
-Category & Data Fusion Model \\
-
+\begin{tabular}{|c | c|}
+\hline
+\textbf{Category} & \textbf{Data Fusion Model} \\
 \hline
@@
 \end{tabular}
-\caption{Classification of data fusion models.}
+\caption{Classification of data fusion models}
+\label{fusionModelsClas}
 \end{table}

### 2015-03-22 ch2-mdf_ims.tex
Started table of fusion algorithms.
Fusion algorithms section finished. Enhancement in tables. Included enumitem package.

@@
 \includegraphics[scale=0.4]{fig/2/WaterfallModel.png}
-\caption{Waterfall model. (from \cite{Esteban2005}).}
+\caption{Waterfall model (from \cite{Esteban2005}).}
 \label{WaterfallModel}
@@
 \begin{table}
+\footnotesize
 \centering
@@
 Low-level fusion refers to the merge of raw data or signals, mid-level fusion refers to the fusion of features and High-level fusion refers to the process of fuse decisions.
-
 Khaleghi in \cite{Khaleghi2013} describes a classification for fusion algorithms based on challenging problems that arise from the data to be fused, due to the variety of sensors and the nature of the application environment.
@@
 Four types of data are enumerated: Imperfect data, correlated data, inconsistent data and disparate data.
-For thi
+These two approaches of fusion algorithms classification are summarized in tables \ref{fusionAlgClasLuo} and \ref{fusionAlgClasKhaleghi}.
+
+\begin{table}[ht!]
+\footnotesize
+\centering
+\begin{tabular}{|c|c|c|c|}
+\hline
+\multicolumn{2}{|c|}{\textbf{Low level fusion}} & \textbf{Medium level fusion} & \textbf{High level fusion} \\
+\hline
+\multicolumn{2}{|c|}{\textit{Estimation methods}} & \textit{Classification methods} & \textit{Inference methods} \\
+\hline
+\parbox{2.5cm}{
+	Recursive:
+	\begin{itemize}[leftmargin=.07in]
+		\item Kalman filter
+		\item Extended Kalman filter
+	\end{itemize}
+	Non-Recursive:
+	\begin{itemize}[leftmargin=.07in]
+		\item Weighted average
+		\item Least squares
+	\end{itemize}
+	}
+ & 
+ \parbox{2.5cm}{	 
+ 	Covariance-based:
+	\begin{itemize}[leftmargin=.07in]
+		\item Cross covariance
+		\item Covariance intersection
+		\item Covariance union
+	\end{itemize}
+	}
+&
+ \parbox{3cm}{	 
+	\begin{itemize}[leftmargin=.07in, noitemsep]
+		\item Parametric templates
+		\item Cluster analysis
+		\item K-means clustering
+		\item Learning vector quantization
+		\item Kohonen feature map
+		\item Artificial neural networks
+		\item Support vector machines
+	\end{itemize}
+	}
+&
+\parbox{3cm}{	 
+	\begin{itemize}[leftmargin=.07in, noitemsep]
+		\item Bayesian inference
+		\item Particle filters
+		\item Dempster-Shafer theory
+		\item Expert systems
+		\item Fuzzy logic
+	\end{itemize}
+	} \\
+\hline
+\end{tabular}
+\caption{Classification of fusion algorithms based on level of fusion}
+\label{fusionAlgClasLuo}
+\end{table}
+
+\begin{table}[ht!]
+\footnotesize
+\centering
+\begin{tabular}{|c|c|}
+\hline
+\textbf{Data Problem} & \textbf{Framework} \\
+\hline
+\multirow{7}{*}{Imperfection} & Probabilistic \\
+& Evidential \\
+& Fuzzy reasoning \\
+& Possibilistic \\
+& Rough set theoretic \\
+& HYbridization \\
+& Random set theoretic \\
+\hline
+\multirow{2}{*}{Correlation} & Correlation elimination \\
+& Correlation presence \\
+\hline
+\multirow{6}{*}{Inconsistency} & Sensor validation \\
+& Stochastic sensor modeling\\
+& Prediction \\
+& Augmented state framework \\
+& Combination rules \\
+& Dempsters' rule \\
+\hline
+\multirow{3}{*}{Disparateness} & Dempster-Shafer theoretic framework \\
+& Human-centered data fusion \\
+& Hard-soft data fusion \\
+\hline
+\end{tabular}
+\caption{Classification of fusion algorithms based on challeging problems in data}
+\label{fusionAlgClasKhaleghi}
+\end{table}
 

### 2015-03-22 ch2-mdf_ims.tex
Some corrections and parragraph added to ch2. conclusions

@@
-%\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}
+%\begin{document}
+
+\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}
 
@@
 Several models, architectures and frameworks have been proposed in literature; some of them to show how a data fusion system should work and some other providing guidelines on how to implement it in a given application.
+Also, a wide range of algorithms have been used to perform fusion of data, some classified by the nature of the fusion or by the nature of the data, but is finally the environment and the application itself which determines the approach to use.
+
+%\end{document}

### 2015-03-25 ch2-mdf_ims.tex
IMS components graph relocated
Enhanced first part of section IMS

@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.175]{fig/2/ims_graph.png}
-\caption{Fusion algorithms based on level of fusion. (from \cite{Luo2011})}
-\label{fusionAlgs}
-\end{figure}
-
 %\subsection{Laser and Video Data Fusion}
@@
 Different types of applications and systems are conceived to address these issues.
-Some tasks those systems realize are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others.
-Communication approaches in these systems are based in the interaction between vehicles and infrastructure, commonly divided in three groups: Vehicle-to-vehicle communication (V2V) , Vehicle-to-infrastructure communication (V2I) and the combination of both of them (V2X).
+Some tasks performed by those are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others.
+A typical Intersection Management System is composed by three main components: Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, along vehicle sensors and traveling data; decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and authorities in order identify objects, recognise patterns, predict future incidents, control traffic and generate safe decisions and warnings alerts; and finally, is the presentation and displaying of the output of decision system, through infrastructure using dynamic signals, semaphore controlling, or using direct communication with drivers or vehicles through on-board visualisation/notification system.
+A block diagram of a generic IMS is presented in figure \ref{arch}
 
@@
 \centering
-\includegraphics[scale=0.75]{fig/2/fig1}
-\caption{Generic block diagram of an Intersection Management System (from \cite{Chan2005}).}
+\includegraphics[scale=0.55]{fig/2/genericIMS.png}
+\caption{Generic block diagram of an Intersection Management System.}
 \label{arch}
 \end{figure}
-
-Figure \ref{arch}, presents a generic block diagram of an Intersection Management System composed by three main components: (a) Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, and also could be vehicle sensors.
-(b) Decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and environment in order to predict future incidents, control traffic and generate safe decisions and warnings alerts.
-Finally, (c) is the presentation and displaying of the output of decision system.
-It could be at the infrastructure using dynamic signals, semaphore controlling, or vehicle-directed through on-board visualization/notification system.
 
@@
 
-\subsection{Applications in IMS}
+\subsection{Components in IMS application}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.2125]{fig/2/ims_graph2.png}
+\caption{Components of an interesection management system application.}
+\label{fusionAlgs}
+\end{figure}
 
@@
 
-%\subsection{Intersection Management Systems and Multisensor Data Fusion}
+\subsection{Developments in Intersection Management Systems}
 

### 2015-03-25 ch2-mdf_ims.tex
Added list of figures and tables. Corrected some typos.
Added paragraph for ims components

@@
 & Rough set theoretic \\
-& HYbridization \\
+& Hybridization \\
 & Random set theoretic \\
@@
 
+Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection, accidents prevention and security and surveillance systems.
+Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approachesa and objectives.
+In order to organise and compare IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development.
+In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.
+
 \begin{figure}[ht!]
@@
 \includegraphics[scale=0.2125]{fig/2/ims_graph2.png}
-\caption{Components of an interesection management system application.}
-\label{fusionAlgs}
+\caption{Components of an Intersection Management System application.}
+\label{imsComps}
 \end{figure}
 
-Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications as traffic analysis, counting and classification of vehicles or pedestrians, events and incident detection, accidents prevention and security and surveillance applications.
-
-To complete these tasks, many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure.
+many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure.
 For example, monitoring mobile wireless network like Bluetooth \cite{Friesen2013}, detecting vehicle presence using inductive loops or RFID tags, identifying vehicles and pedestrian using cameras \cite{Buch2011, Strigel2013}, single or multiple laser-scanners \cite{Meissner2010, Meissner2012, Zhao2006, Zhao2008, Zhao2012}, and multi-sensor integrated systems \cite{Meissner2013, Meissner2013a, Meissner2014, GoldHammer2012, Zhao2009}.

### 2015-03-27 ch2-mdf_ims.tex
Corrected typo

@@
 Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection, accidents prevention and security and surveillance systems.
-Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approachesa and objectives.
-In order to organise and compare IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development.
+Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approaches and objectives.
+In order to study and compare IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development.
 In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.

### 2015-04-06 ch2-mdf_ims.tex
Added first IMS component paragraph

@@
 
-Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection, accidents prevention and security and surveillance systems.
+Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection and security and surveillance systems.
 Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approaches and objectives.
-In order to study and compare IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development.
+In order to study IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development.
 In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.
@@
 \end{figure}
+
+\subsubsection{Application}
+
+Application component could be seen as the final objective of the system.
+Generally, this includes high-level tasks like monitoring, analysis or control.
+Monitoring or surveillance systems execute actions like recognition, detection and/or tracking of objects in the scene.
+Other systems analyse the behaviour and interactions between detected objects to recognise path patterns, determine the context of the environment and predict some events of interest.
+In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, generate warnings to drivers or issue traffic tickets when a rule violation exists.
+\subsubsection{Data Source}
+\subsubsection{Target}
+\subsubsection{Communication}
+\subsubsection{Implementation}
 

### 2015-04-06 ch3-arch_sys.tex
Some corrections and modifications
Created a draft for the structure of Chapter 3
First paragraph of chapter 3

@@
 % 	* Multisensor IMS		
-%		
 %		* Processing Stages
@@
 %		* Architecture proposal
-
 %	* Validation approaches
@@
 %			* KoPER Dataset
+
+\chapter {Architecture Description and System Specification}
+
+Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors and computing capabilities.
+These enhancements have allowed to deploy more of these types of sensors per scenario and is required to define some processing stages from raw data capture through decision and control.
+Also is needed to test and validate the developments prior to a real and full functional implementation.
+The first part of this chapter describe main stages in a intersection management system based on image and range sensors, fusion approaches and methods used in these stages and an architeture proposal for the implementation.
+In the second part, two validation tools for IMS application are compared, simulators and datasets.
+
+\section{Multisensor IMS}
+Multicamera and multilasers monitoring systems offer more information about environment that can be merged to provide a better representation of the whole scene, and detect more acurately the objects in the intersection and prevent possible incidents.
+\subsection{Processing Stages}
+\subsection{Fusion approaches}
+\subsection{Methods and techniques}
+\subsection{Architecture proposal}
+\section{Validation approaches}
+\subsection{Transportation and Traffic Simulations}
+\subsubsection{Simulators Classification}
+\subsection{Intersection monitoring Datasets}
+\subsubsection{POSSi Dataset}
+\subsubsection{KoPER Dataset}

### 2015-04-06 ch2-mdf_ims.tex
Added second IMS component paragraph, data source

@@
 In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, generate warnings to drivers or issue traffic tickets when a rule violation exists.
+
 \subsubsection{Data Source}
+
+The origin of data is considered an independent component because the variety of possible sources.
+From infrastructure side, data can be captured using a wide range of sensors like inductive loops, lasers, lidars and cameras.
+Also, monitoring connections to networks, like bluetooth, to estimate vehicle traffic through a place, have been used recently.
+
 \subsubsection{Target}

### 2015-04-06 ch2-mdf_ims.tex
Added third IMS component paragraph, Target

--- 2015-04-06 ch2-mdf_ims.tex
@@
 This chapter is divided into two sections.
-In the first section a brief overview of multisensor data fusion is presented, remarking in different architectures proposed in the literature and different approaches used for laser and video data fusion are described.
-The second section contains a short review on intelligent transportation systems and intersection management systems, including current research on this topic.
-Finally, some projects that include fusion of laser and video data for intersection managing applications are presented.
+In the first section a brief overview of multisensor data fusion is presented, remarking in different architectures proposed in the literature and different algorithms and frameworks used for this task.
+The second section contains a short review on intelligent transportation systems and intersection management systems, including a description of elements involved in the development of an IMS application.
+Finally, some projects that include multisensor data for intersection managing applications are presented.
 
@@
 In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, generate warnings to drivers or issue traffic tickets when a rule violation exists.
+
 \subsubsection{Data Source}
+
+The origin of data is considered an independent component because of the variety of possible sources and posterior processing stages.
+From infrastructure side, data can be captured using a wide range of sensors like inductive loops, lasers, lidars and cameras.
+Also, monitoring connections to networks, like bluetooth, to estimate vehicle traffic through a place, have been used recently \cite{Friesen2013, Friesen2014}.
+On the other side, data from vehicles is also useful for the system to enhance its representation of the scene and take decisions.
+This could be low-level data like vehicle state variables, for example, speed, orientation, acceleration, etc., or high-level data like travel information.
+
 \subsubsection{Target}
+
+In an intersection many objects of different kinds interact between them.
+Pedestrian and vehicles are found at intersections, and latter includes bicycles, motorcycles, cars, vans, buses, trucks and some other types of vehicles.
+For this reason some applications are designed for a specific element or group of elements.
+Pedestrian tracking, motorcycles recognition or car counting are examples of targeted applications.
+
 \subsubsection{Communication}
+
 \subsubsection{Implementation}

### 2015-04-07 ch2-mdf_ims.tex
Added fourth IMS component paragraph, Communication

@@
 
+One of the keypoints of ITS is how information technologies and communication advances are included in transportation.
+The main goal of this is to allow that information to be shared between vehicles and infrastructure entities.
+For this reason, 3 communication approaches appear: Vehicle-to-vehicle or Inter-vehicle communication (V2V), vehicle-to-infrastructure communication (V2I) and vehicle to both vehicle and infrastructure (V2X).
+Several protocols and standars have been proposed for these communication approaches, for example DSRC, WAVE and IEEE 802.11p, but research and development on this component is still active.
+
 \subsubsection{Implementation}

### 2015-04-08 ch2-mdf_ims.tex
Added fifth and last IMS component paragraph, Implementation Added another conclusion in chapter 2

@@
 
-many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure.
+Not all IMS applications are implementable on a real scenario, maybe because is not the scope of the application or because it is in a early stage and it could be validated in other ways.
+This types of developments are sometimes implemented and evaluated using simulators, making functional prototypes or deploying scale-models.
+Some other projects use datasets to evaluate new algorithms and data processing techniques, and then compare obtained results with previous works.
+Augmented reality is also used as a tool for evaluating and validate developmens, taking advantage of the interaction of a real system with a simulated/artificial scenario.
+
+%many approaches have been proposed for information capture stage, both taking data from vehicle or from the infrastructure.
 For example, monitoring mobile wireless network like Bluetooth \cite{Friesen2013}, detecting vehicle presence using inductive loops or RFID tags, identifying vehicles and pedestrian using cameras \cite{Buch2011, Strigel2013}, single or multiple laser-scanners \cite{Meissner2010, Meissner2012, Zhao2006, Zhao2008, Zhao2012}, and multi-sensor integrated systems \cite{Meissner2013, Meissner2013a, Meissner2014, GoldHammer2012, Zhao2009}.
 
-Other application are traffic-control oriented, rather than to sensing and data-processing stage.
+%Other application are traffic-control oriented, rather than to sensing and data-processing stage.
 The aim of these applications are to maximise vehicle flow, reduce accidents and improve safety.
@@
 
-In \cite{Ball2010} and \cite{Azimi2012}, intervehicular-communication based architectures are proposed.
+%In \cite{Ball2010} and \cite{Azimi2012}, intervehicular-communication based architectures are proposed.
 In these, each vehicle send to the others its own information about position, velocity, destination and more, and then they coordinate how the access to the intersection should be done.
@@
 
+On the other hand, intersection management systems are highly required to improve safety and mobility in transportation, due to the high complexity present in these places, for drivers and authorities too.
+There is not an IMS application that address all the needs and problems in an intersection, for this reason many developments with narrow scopes and many topics involved have been proposed through the years.
+To handle all these works and proposals, a new component-based classification scheme for IMS application has been proposed.
 %\end{document}

### 2015-04-09 ch2-mdf_ims.tex
Brief change

@@
 Other systems analyse the behaviour and interactions between detected objects to recognise path patterns, determine the context of the environment and predict some events of interest.
-In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, generate warnings to drivers or issue traffic tickets when a rule violation exists.
+In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, control intersection access, generate warnings to drivers or issue traffic tickets when a rule violation exists.
 

### 2015-04-10 ch2-mdf_ims.tex
Added Kamijo1999 and Kamijo2000 to Bibliography

--- 2015-04-08 ch2-mdf_ims.tex
@@
 Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection and security and surveillance systems.
-Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approaches and objectives.
-In order to study IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development.
-In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.
+Those applications have to take into account some of the elements depicted in figure \ref{arch} and developments in IMS have a wide range of approaches and objectives.
+In order to study IMS applications, five components have been defined, which are present on these applications, and on most cases, more than one component could be involved in the same development.
+In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them and then, a description of each component is given.
 
@@
 Other systems analyse the behaviour and interactions between detected objects to recognise path patterns, determine the context of the environment and predict some events of interest.
-In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, generate warnings to drivers or issue traffic tickets when a rule violation exists.
+In \cite{Kamijo1999, Kamijo2000} is presented a system for accident detection and classification at intersections.In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, control intersection access, generate warnings to drivers or issue traffic tickets when a rule violation exists.
 

### 2015-04-15 ch3-arch_sys.tex
Added new paragraph and figure in chapter 3, processing stages.

@@
 
-\chapter {Architecture Description and System Specification}
+%\chapter {Architecture Description and System Specification}
+\chapter {System Description}
 
@@
 \section{Multisensor IMS}
+
 Multicamera and multilasers monitoring systems offer more information about environment that can be merged to provide a better representation of the whole scene, and detect more acurately the objects in the intersection and prevent possible incidents.
+For designing an single-sensor or multi-sensor IMS system, there are some basic processing stages to have into account.
+In the case of a multisensor system, it is also required to analyse and determine what is the better fusion approach to use and in which of the processing stages this fusion should be performed to get better result that a single-sensor based system.
+Below, processing stages, fusion approaches, methods and architecture proposal are presented.
+
 \subsection{Processing Stages}
+
+In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: Filtering, feature extraction, pattern recognition and situation assessment.
+The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene and remove noise and irrelevant data.
+In the second stage, the objective is to identify elements within the foreground and extract relevant features of them.
+The third stage receives the set of features from the previous stage and performs recognition and classification tasks.
+Also, tracking and prediction of objects'state is performed based on historic information.
+In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest.
+This output could be delivered to an optional fifth stage of decision and control, or to a human operator, traffic agent or institution, for taking immediate actions on traffic control, issuing of traffic tickets, warning drivers about possible incidents or improving transporation policies in a long-term.
+In figure \ref{proc_stages}, are depicted the previously described stages, and how the data volume is reduced while data meaning increases in the last stages.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.55]{fig/3/proc_stages.png}
+\caption{Processing stages in an IMS.}
+\label{proc_stages}
+\end{figure}
+
 \subsection{Fusion approaches}

### 2015-06-06 ch2-mdf_ims.tex
Some text improvements and figure changed in pdf

@@
 Different types of applications and systems are conceived to address these issues.
-Some tasks performed by those are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others.
-A typical Intersection Management System is composed by three main components: Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, along vehicle sensors and traveling data; decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and authorities in order identify objects, recognise patterns, predict future incidents, control traffic and generate safe decisions and warnings alerts; and finally, is the presentation and displaying of the output of decision system, through infrastructure using dynamic signals, semaphore controlling, or using direct communication with drivers or vehicles through on-board visualisation/notification system.
+Some tasks performed by those systems are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others.
+A typical Intersection Management System is composed by three main components: Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, and vehicle sensors and traveling data; decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and authorities in order to identify objects, recognise patterns, predict future incidents, control traffic and generate safe decisions and warnings alerts; and finally, is the presentation and displaying of the output of decision system, through infrastructure using dynamic signals, traffic light controlling, or using direct communication with drivers or vehicles through on-board visualisation/notification system.
 A block diagram of a generic IMS is presented in figure \ref{arch}
@@
 In order to study IMS applications, five components have been defined, which are present on these applications, and on most cases, more than one component could be involved in the same development.
-In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them and then, a description of each component is given.
+In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them, and next, a description of each component is given.
 
@@
 \centering
-\includegraphics[scale=0.2125]{fig/2/ims_graph2.png}
+\includegraphics[scale=0.25]{fig/2/ims_graph5.png}
 \caption{Components of an Intersection Management System application.}
@@
 Other systems analyse the behaviour and interactions between detected objects to recognise path patterns, determine the context of the environment and predict some events of interest.
-In \cite{Kamijo1999, Kamijo2000} is presented a system for accident detection and classification at intersections.In a higher level there are the control or decisions made based on detection of certain traffic conditions to handle traffic lights, control intersection access, generate warnings to drivers or issue traffic tickets when a rule violation exists.
+At a higher level there are systems which make decisions based on detection of certain traffic conditions to handle traffic lights, control intersection access, generate warnings to drivers or issue traffic tickets when a rule violation exists.
 
@@
 From infrastructure side, data can be captured using a wide range of sensors like inductive loops, lasers, lidars and cameras.
-Also, monitoring connections to networks, like bluetooth, to estimate vehicle traffic through a place, have been used recently \cite{Friesen2013, Friesen2014}.
+Also, monitoring connections to wireless networks.
 On the other side, data from vehicles is also useful for the system to enhance its representation of the scene and take decisions.
@@
 One of the keypoints of ITS is how information technologies and communication advances are included in transportation.
-The main goal of this is to allow that information to be shared between vehicles and infrastructure entities.
+The main goal of this is to allow information sharing between vehicles and infrastructure entities.
 For this reason, 3 communication approaches appear: Vehicle-to-vehicle or Inter-vehicle communication (V2V), vehicle-to-infrastructure communication (V2I) and vehicle to both vehicle and infrastructure (V2X).
@@
 Some other projects use datasets to evaluate new algorithms and data processing techniques, and then compare obtained results with previous works.
-Augmented reality is also used as a tool for evaluating and validate developmens, taking advantage of the interaction of a real system with a simulated/artificial scenario.
+Augmented reality is also used as a tool for evaluating and validate developments, taking advantage of the interaction of a real system with a simulated/artificial scenario.
 
@@
 
+In the next table is presented a compilation of several developments within IMS field. For each work a brief overview and a remark of how each component is related to it are given.
+
+\section{Sensor Fusion in Intersection Management}
+
 \section{Conclusions}

### 2015-06-09 ch2-mdf_ims.tex
Added table of IMS review, and added new bibtex entries to .bib file

@@
 
-In the next table is presented a compilation of several developments within IMS field. For each work a brief overview and a remark of how each component is related to it are given.
+In the table \ref{reviewtable} is presented a compilation of several developments within IMS field.
+For each work a brief comment is given, and a remark of how certain components (Data source, communication and application) are related to it.
+Target and implementation components could be infered from the comment.
+
+\begin{center}
+\footnotesize
+\begin{longtable}{|c|p{0.3\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}|c|}
+%\begin{tabular}
+\hline
+\multicolumn{5}{|c|}{ \textbf{Developments on Intersection Management Systems} } \\
+
+\hline
+\textbf{Reference} & 
+\pbox{0.3\linewidth}{\textbf{Comment}} & 
+\pbox{0.15\linewidth}{\textbf{Application}} & 
+\pbox{0.1\linewidth}{\textbf{Data Source}} & 
+\textbf{Communication} \\
+
+\hline
+\endfirsthead
+\hline
+\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
+\hline
+\endhead
+
+\cite{Kamijo1999, Kamijo2000} & 
+{They show an intersection monitoring system based on a fixed camera.
+This system is divided in three stages: Background modeling, object tracking and accident detection.
+They propose an innovative feature for accident detection using HMM.} &
+{Accident  detection} & 
+Camera & 
+N/A \\
+\hline
+
+\cite{Veeraraghavan2002} &
+{Passive video-based system for monitoring an intersection.
+They implemented Stauffer's Method for background modeling, PCA for oriented bounding box computation, and Graph-based tracking and motion estimation.
+Also a simple methods for classification and calibration are described.} &
+{Accident  detection} & 
+Camera & 
+N/A \\
+\hline
+
+\cite{Gehrig2003} & & & & \\
+\hline
+
+\cite{Veeraraghavan2003} &
+They present 4 stages for IMS: background modeling, motion tracking, feature extraction, calibration.
+They propose a 2-level tracking: Blob tracking as low-level and position using Kalman filter as high-level.
+&
+Accident detection / prediction &
+Camera & 
+N/A \\
+\hline
+
+\cite{Messelodi2004} & & & & \\
+\hline
+\cite{Dogan2004} & & & & \\
+\hline
+
+\cite{Chan2004} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Atev2005} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Chan2005} &
+ &
+ &
+ &
+ \\
+\hline
+\cite{Avila2005} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Veeraraghavan2005} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Zhao2006} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Eguchi2007} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Kuramoto2007} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Dresner2008} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Jarupan2008} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Zhao2008} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Rawashdeh2008} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Mundewadikar2008} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Zhao2009} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Abbas2009} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Babaei2010} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Meissner2010} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Quinlan2010} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Ball2010} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Babaei2011} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Basma2011} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Azimi2012} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{CondeBento2012} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Zhao2012} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Jin2012} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Meissner2012} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Goldhammer2012} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{Friesen2013} &
+ &
+ &
+ &
+ \\
+\hline
+
+\cite{} &
+ &
+ &
+ &
+ \\
+\hline
+
+\hline
+%\end{tabular}
+\caption{Developments related to Intersection Management Systems.}
+\label{reviewtable}
+\end{longtable}
+\end{center}
 

### 2015-06-10 ch2-mdf_ims.tex
IMS Review table updated and moved to an independent file.

--- 2015-06-06 ch2-mdf_ims.tex
@@
 
-In the next table is presented a compilation of several developments within IMS field. For each work a brief overview and a remark of how each component is related to it are given.
+In the table \ref{reviewtable} is presented a compilation of several developments within IMS field.
+For each work a brief comment is given, and a remark of how certain components (Data source, communication and application) are related to it.
+Target and implementation components could be infered from the comment.
+
+\input{extra/ims_review_table}
 
@@
 
-On the other hand, intersection management systems are highly required to improve safety and mobility in transportation, due to the high complexity present in these places, for drivers and authorities too.
-There is not an IMS application that address all the needs and problems in an intersection, for this reason many developments with narrow scopes and many topics involved have been proposed through the years.
-To handle all these works and proposals, a new component-based classification scheme for IMS application has been proposed.
+On the other hand, intersection management systems are highly required to improve safety and mobility in transportation, due to the high complexity present in these places for drivers and for authorities too.
+There is not an IMS application that address all the needs and problems in an intersection, for this reason many developments with narrow scopes and with many topics involved have been proposed through the years.
+To handle all these works and proposals, a new component-based classification scheme for IMS application has been proposed, and a review of developments in Intersection Management Systems is presented.
+
 %\end{document}

### 2015-06-10 extra/ims_review_table.tex
IMS Review table updated and moved to an independent file.

% IMS review table
\begin{center}
\footnotesize
\begin{longtable}{|c|p{0.3\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}|c|}
%\begin{tabular}
\hline
\multicolumn{5}{|c|}{ \textbf{Developments on Intersection Management Systems} } \\

\hline
\textbf{Reference} & 
\pbox{0.3\linewidth}{\textbf{Comment}} & 
\pbox{0.15\linewidth}{\textbf{Application}} & 
\pbox{0.1\linewidth}{\textbf{Data Source}} & 
\textbf{Communication} \\

\hline
\endfirsthead
\hline
\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
\hline
\endhead

\cite{Kamijo1999, Kamijo2000} & 
{They show an intersection monitoring system based on a fixed camera. This system is divided in three stages: Background modeling, object tracking and accident detection. They propose an innovative feature for accident detection using HMM.} & 
{Accident  detection} & 
Camera & 
N/A \\
\hline

\cite{Veeraraghavan2002} &
{Passive video-based system for monitoring an intersection. They implemented Stauffer's Method for background modeling, PCA for oriented bounding box computation, and Graph-based tracking and motion estimation. Also a simple methods for classification and calibration are described.} &
{Accident  detection} & 
Camera & 
N/A \\
\hline

%\cite{Gehrig2003} & & & & \\ \hline

\cite{Veeraraghavan2003} &
They present 4 stages for IMS: background modeling, motion tracking, feature extraction, calibration. They propose a 2-level tracking: Blob tracking as low-level and position using Kalman filter as high-level. &
Accident detection / prediction &
Camera & 
N/A \\
\hline

\cite{Messelodi2004} &
A Full implementation of an IMS in a town in northern Italy. The system claims to be independent of intersection geometry and it is based on a monocular camera. Processing stages of the system and classification approaches are described. &
Intersection Monitoring &
Camera &
N/A \\
\hline

\cite{Dogan2004} &
Development of a simulator for an Intersection Collision Warning System. Physical and MAC layers were modeled &
Intersection collision warning simulator &
N/A &
V2V \\
\hline

\cite{Chan2004} &
 Traffic monitoring for two context: Left-Turn-Across-Path-Opposite-Direction and Dilemma zone and red light violation &
Intersection Monitoring &
Radar &
N/A \\
\hline

\cite{Atev2005} &
A collision prediction system based on computational geometry is presented. The two main stages are low-level vision system for foreground optimization, with shaking compensation and noise removal, and a collision prediction system based on bounding boxes instead of bounding rectangles. &
Collision prediction &
Camera &
N/A \\
\hline

\cite{Chan2005} &
Analysis of Left-Turn-Across-Path-Opossite-Direction conflict situation. &
Intersection Monitoring &
Radar; Steering, speed sensors and GPS on-board &
V2X \\
\hline

\cite{Avila2005} &
Based on \cite{Dogan2004}, this works includes and improvement, including network layer and driver behaviour model. &
Intersection Simulator Architecture &
N/A &
V2X \\
\hline

\cite{Veeraraghavan2005} &
Tracking system based on Kalman filter for tracking and event detection at intersections, capable of detect 4 events: Acceleration, uniform velocity, stop and turns. &
Tracking and event detection &
Camera &
N/A \\
\hline

\cite{Zhao2006} &
Object tracking and classification at intersection using a single laser scanner. The system identifies 3 classes: Pedestrians, 2-wheeled vehicle and cars. It is based on points clustering, KL transform and markov chains &
Object tracking and classification &
Laser &
N/A \\
\hline

\cite{Eguchi2007} &
A system for discriminate an approaching vehicle to an intersection is described. It use a monocular camera and define a number of features for classification. Motion vectors are used too and determine the level of approaching. &
Vehicle detection &
Camera &
N/A \\
\hline

\cite{Kuramoto2007} &
A communication scheme based on nearest to intersection is described. Two zones are defined: nearest zone and quasi-nearest zone. Based on which zone vehicles are, communicaton is performed. Validation of proposal is done using a custom microscopic simulator. &
Intersection Communication Scheme &
N/A &
V2I \\
\hline

\cite{Dresner2008} &
A multiagent-based intersection control protocol called autonomous intersection management (AIM) is proposed. Based on a custom simulation, vehicles are modeled and they comunicate with an intersection manager which allows or deny access to intersection. It is possible to set different traffic policies, even for emulate current control approaches lke stop lights and traffic lights. &
Intersection Management &
On-board state sensors &
V2I \\
\hline

\cite{Jarupan2008} &
Based on \cite{Dogan2004} and \cite{Avila2005}, this simulator architecture emphasize on wireless communications. Now the system allows to compare different communication protocols and traffic configurations. &
Intersection Simulator Architecture &
N/A &
V2V \\
\hline

\cite{Zhao2008} &
Based on \cite{Zhao2006}, the system now includes more laser sensor for get a better representation of the scene, solving some occlusion issues. Clustering is used for grouping readings from different sensors belonging to the same object and a tracking approach based on angle of beam, range and time is presented. &
Intersection monitoring &
Lasers &
N/A \\
\hline

\cite{Rawashdeh2008} &
Proposal of a communication architecture for vehicles approaching to an intersection. Two zones are defined: Control Channel Zone (CCHZ) and Service Channel Zone (SCHZ). Also, 3 different methods are described for the system to be implmented &
Collision avoidance &
N/A &
V2I \\
\hline

\cite{Mundewadikar2008} &
Proposal of a physical-layer protocol for V2I communication at intersections. The system is evaluated in simulation using MATLAB &
Collision detection and warning &
N/A &
V2I \\
\hline

\cite{Zhao2009} &
Based on \cite{Zhao2008}, now the system includes a camera for video capture. In this video, data obtained from the lasers-based system are projected, drawing bounding boxes for vehicles and lines for trajectories. &
Intersection monitoring &
Camera, Lasers &
N/A \\
\hline

\cite{Abbas2009} &
Monitoring dilemma zone and efectiveness of control policies using cameras and loop detectors on an intersection &
Intersection monitoring &
Cameras, loop detectors &
N/A \\
\hline

\cite{Babaei2010} &
Author presents a system for foreground extraction, vehicle detection and tracking. A novel algorithm is proposed based on image division in traffic zones to perform background removal and vehicle detection. This proposal is compared with traditional MoG approach. &
Intersection monitoring &
Camera &
N/A \\
\hline

\cite{Meissner2010} &
A semi-automatic calibration method for a network of lidar sensors is presented using a custom simulation environment. Also, a calibration object were designed based on simulation results. &
Intersection Monitoring &
Lidars &
N/A \\
\hline

\cite{Quinlan2010} &
An augmented reality implementation of the system proposed in cite{Dresner2008} is presented. In this work, an autonomous vehicle is deployed in a mixed-reality platform and request to an virtual intersection manager for authorisation to cross and is the manager which decides if it is safe to cross or not, depending on the defined traffic policies and the state of virtual vehicles. &
Intersection management &
On-board state sensors &
V2I \\
\hline

\cite{Ball2010} &
The use of intelligent objects in vehicles is proposed. With sharing vehicle state information and jouney plans, the system aims to better control traffic in intersection using a novel back-off protocol instead of time traffic control system. &
Traffic control &
On-board state sensors, Journey plans &
V2V \\
\hline

\cite{Babaei2011} &
A system for traffic flow measurement based on anormalities detection is presented. Multiple cameras are used SIFT and unsupervised SVM-based clustering are performed for trajectories analysis. &
Intersection monitoring &
Cameras &
N/A \\
\hline

\cite{Basma2011} &
In presented system, wireless magnetic nodes are used to detect presence and to send data to a base station, which determines possible collisions and warns driver through a visualisation system in infrastructure. &
Collision Avoidance	 &
Presence sensors &
N/A \\
\hline

\cite{Azimi2012} &
An intersection control protocol based on V2V communication is proposed. This protocol is in charge of handling other vehicles messages and determines if is it safe or not to cross. They present two policies for managing intersection access: Concurrent Crossing- Intersection Protocol (CC-IP) and Maximum Progression-Intersection Protocol (MP-IP). &
Intersection management &
N/A &
V2V \\
\hline

\cite{CondeBento2012} &
A microscopic simulator was developed, with a spatial-temporal-based approach for managing the intersection. It is possible to implement different traffic policies for comparison purposes and the system works on crossroads and roundabouts. &
Intersection management &
On-board state sensors &
V2X \\
\hline

\cite{Zhao2012} &
A novel approach for detecting moving objects and track them is presented. The focus of this work relies on process merged data from laser sensors (\cite{Zhao2009}) to get better results at tracking. &
Object detection and tracking &
Lasers &
N/A \\
\hline

\cite{Jin2012} &
A Multiagent-based system is proposed. They define a Vehicle Agent and and Intersection Agent and propose a protocol for controlling intersection access based on timeslots, Also, the present a vehicle motion planning algorithm. Validation and testing was done using SUMO platform &
Intersection Management &
On-board state sensors &
V2I \\
\hline

\cite{Meissner2012} &
A set of laser scanners is used for detect and track pedestrians. GMM and DBSCAN are proposed for detection stage. For tracking purpose, a random finite set particle filter is used. &
Pedestrians detection and tracking &
Lasers &
N/A \\
\hline

\cite{Goldhammer2012} &
In this work is presented the setting and configuration of a multisensor network, based on 14 lasers, 10 cameras, GPS and V2I unit. Calibration and spatial-temporal alignment is performed. &
System Architecture &
Cameras, Lasers &
V2I \\
\hline

\cite{Friesen2013} &
A set of wireless probes are deployed to estimate traffic flow based on bluetooth connections. Then, using Zigbee, data is send to a master node which handle data for forwarding to a server / database for further processing. &
Traffic monitoring &
Wireless sensor network &
N/A \\
\hline

\cite{Guerrero-Ibanez2013} &
Two modes of Intersection Access Control: V2I mode and V2V mode. Implementation was done using minirobots in a scale model of an intersection. &
Intersection access control &
Loop detectors and RFID nodes &
V2X \\
\hline

%\cite{Meissner2013,Meissner2013a} &
% &
% &
% &
% \\
%\hline

\cite{Meissner2013b} &
A new method for object detection based on lidars data is proposed. After perform background removal, they use DBGridSCAN for 3D clustering and 2D pathway tracking. Then a combination of 2D-3D is done. The proposal is validated using OSPA metric. &
Object Detection &
Lasers &
N/A \\
\hline

\cite{Au2015} &
On top of AIM (\cite{Dresner2008}) Semi-AIM protocol is proposed. Assuming that human-driven vehicles to autonomous vehicles transition will be long, this system is intended for semi-autonomous vehicles. Also the author describe the human relation to a semi-autonomous vehicle and analyse how the features of autonomy employed by the car affects the traffic delay. &
Intersection Management &
On-board state sensors &
V2I \\
\hline

%\cite{} &
% &
% &
% &
% \\
%\hline

%\cite{} &
% &
% &
% &
% \\
%\hline

%\cite{} &
% &
% &
% &
% \\
%\hline

%\cite{} &
% &
% &
% &
% \\
%\hline

%\cite{} &
% &
% &
% &
% \\
%\hline

%\cite{} &
% &
% &
% &
% \\
%\hline

\hline
%\end{tabular}
\caption{Developments related to Intersection Management Systems.}
\label{reviewtable}
\end{longtable}
\end{center}

### 2015-06-10 ch2-mdf_ims.tex
Added content to the last section of chapter 2

@@
 
+Cameras are a wide used sensor for surveillance and monitoring applications because they provide a lot of information for scene understanding, but the transmitting and processing of such information requires high computational resources.
+For this reason low resolution cameras and low frame rates configurations are commonly deployed.
+On the other hand, range sensor, such as lasers and lidars, have been recently included in Intersection management systems, as unique sensors or with cameras too.
+One of the benefits of range sensors is that because of information volume is less than provided by cameras, its processing requirements are lower.
+Using both cameras and range sensors for intersection management systems makes it possible to take advantages of each type of sensor, and obtain a better representation of the environment.
+
 \section{Conclusions}

### 2015-06-10 ch2-mdf_ims.tex
Semi-Finished chapter 2

@@
 
+Although many works based on cameras are found, there are two main developments that make use of range sensors along cameras to implement an IMS.
+The first one, developed by POSS research group at Peking University\footnote{http://www.poss.pku.edu.cn/index.html}, is the POSSi project which main objective is monitoring a dynamic environment through fusion of laser and video.
+In this project, a set of laser scanners are deployed on corners of an intersection and a camera is installed over a pedestrian bridge.
+They perform a fusion over laser data and after detection and recognition of vehicles and pedstrians, this info is backprojected on video stream.
+
+The second relevant project, Ko-PER project\footnote{http://ko-fas.de/english/ko-per---cooperative-perception.html}, was developed by the Institute of Measurement, Control and Microtechnology at Ulm University under Ko-FAS research initiative.
+Ko-PER project aims to capture a complete picure of the local traffic environment.
+In order to do so, a full deployment of infrastructure was made, using 14 laserscanners, 10 cameras, a GPS and a V2I communication unit.
+Also, they perform a low-level fusion over same type sensor first, and then they merge outputs of each subsystem for improve detection and analysis results.
+
+In the proposed work, there is not a deployment of sensors in an intersection scenario, but datasets from the previous mentioned projects will be used instead.
+Also, one of the objectives is to explore and propose a modular fusion architecture/framework for IMS based on cameras and laser sensors.
+In table X a summary of aforementioned developments is presented, including proposed work.
+
+\begin{table}
+\begin{tabular}{|c|c|p{0.125\linewidth}|p{0.15\linewidth}|c|c|c|c|}
+\hline
+
+\textbf{References} & \textbf{Project} & \textbf{Sensors} & \textbf{Target} & \textbf{Fusion} & \textbf{Framework} \\
+\hline
+
+\cite{Zhao2006} & POSSi & Laser & Vehicles, pedestrians & No & No \\
+\hline
+
+\cite{Song2008} & POSSi & Lasers & Pedestrians & Yes & No \\
+\hline
+
+\cite{Zhao2008} & POSSi & Lasers & Vehicles, pedestrians & Yes & No \\
+\hline
+
+\cite{Zhao2009} & POSSi & Lasers, Camera & Vehicles, pedestrians & Yes & No \\
+\hline
+
+\cite{Zhao2012} & POSSi & Lasers & Vehicles, pedestrians & Yes & No \\
+\hline
+
+\cite{Goldhammer2012} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Yes & No \\
+\hline
+
+\cite{Meissner2012} & Ko-PER & Lasers & Pedestrians & Yes & No \\
+\hline
+
+\cite{Meissner2013} & Ko-PER & Lasers & Vehicles, pedestrians & Yes & No \\
+\hline
+
+\cite{Meissner2013a, Meissner2013b} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Yes & No \\
+\hline
+
+\cite{Strigel2013} & Ko-PER & Cameras & Vehicles & Yes & No \\
+\hline
+
+\cite{Meissner2014} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Yes & No \\
+\hline
+
+%\cite{} &  &  &  &  &  \\
+%\hline
+
+Proposed work & - & Lasers, Cameras & Vehicles & Multilevel & Yes \\
+\hline
+
+\end{tabular}
+\end{table}
+
 \section{Conclusions}

### 2015-06-10 ch2-mdf_ims.tex
Update reference to table and added caption and label

@@
 Also, one of the objectives is to explore and propose a modular fusion architecture/framework for IMS based on cameras and laser sensors.
-In table X a summary of aforementioned developments is presented, including proposed work.
+In table \ref{summary_FusIMS} a summary of aforementioned developments is presented, including proposed work.
 
-\begin{table}
+\begin{table}[!t]
 \begin{tabular}{|c|c|p{0.125\linewidth}|p{0.15\linewidth}|c|c|c|c|}
@@
 
-Proposed work & - & Lasers, Cameras & Vehicles & Multilevel & Yes \\
+\textbf{Proposed work} & - & \textbf{Lasers, Cameras} & \textbf{Vehicles} & \textbf{Yes} & \textbf{Yes} \\
 \hline
@@
 \end{tabular}
+\caption{Summary of recent developments involving sensor fusion for Intersection Management Systems}
+\label{summary_FusIMS}
 \end{table}

### 2015-06-11 ch3-arch_sys.tex
Few typos

@@
 Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors and computing capabilities.
-These enhancements have allowed to deploy more of these types of sensors per scenario and is required to define some processing stages from raw data capture through decision and control.
-Also is needed to test and validate the developments prior to a real and full functional implementation.
-The first part of this chapter describe main stages in a intersection management system based on image and range sensors, fusion approaches and methods used in these stages and an architeture proposal for the implementation.
-In the second part, two validation tools for IMS application are compared, simulators and datasets.
+These enhancements have allowed to deploy more of these types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control.
+Also it is needed to test and validate the developments prior to a real and full functional implementation.
+The first part of this chapter describe main stages in a intersection management system based on image and range sensors, fusion approaches and methods used in these stages, and an architeture proposal for the implementation.
+In the second part, two validation tools for IMS applications are described, simulators and datasets.
 
@@
 
-Multicamera and multilasers monitoring systems offer more information about environment that can be merged to provide a better representation of the whole scene, and detect more acurately the objects in the intersection and prevent possible incidents.
+Multicamera and multilasers monitoring systems offer more information about environment that can be merged to provide a better representation of the whole scene, and to detect more acurately the objects in the intersection and prevent possible incidents.
 For designing an single-sensor or multi-sensor IMS system, there are some basic processing stages to have into account.
-In the case of a multisensor system, it is also required to analyse and determine what is the better fusion approach to use and in which of the processing stages this fusion should be performed to get better result that a single-sensor based system.
+In the case of a multisensor system, it is also required to analyse and determine what is the better fusion approach to use and in which of the processing stages this fusion should be performed, in order to get better results than a single-sensor based system.
 Below, processing stages, fusion approaches, methods and architecture proposal are presented.
@@
 The third stage receives the set of features from the previous stage and performs recognition and classification tasks.
-Also, tracking and prediction of objects'state is performed based on historic information.
+Also, tracking and prediction of objects' state is performed based on historic information.
 In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest.
-This output could be delivered to an optional fifth stage of decision and control, or to a human operator, traffic agent or institution, for taking immediate actions on traffic control, issuing of traffic tickets, warning drivers about possible incidents or improving transporation policies in a long-term.
+This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, for taking immediate actions on traffic control, issuing of traffic tickets, warning drivers about possible incidents or improving transportation policies in a long-term.
 In figure \ref{proc_stages}, are depicted the previously described stages, and how the data volume is reduced while data meaning increases in the last stages.

### 2015-06-11 ch4-laser.tex
Created new chapters files (4, 5)

% ch4-laser

\chapter{Laser-Based System}

\section{Preprocessing and Background removal}
\section{Object Recognition}
\section{Feature Extraction}
\section{Tracking and Classification}

### 2015-06-11 ch3-arch_sys.tex
New content on chapter 3. Updated .gitignore

@@
 Also it is needed to test and validate the developments prior to a real and full functional implementation.
-The first part of this chapter describe main stages in a intersection management system based on image and range sensors, fusion approaches and methods used in these stages, and an architeture proposal for the implementation.
-In the second part, two validation tools for IMS applications are described, simulators and datasets.
+The first part of this chapter describe main stages in a intersection management system based on image and range sensors, and methods used in these stages.
+Then an architecture proposal for the implementation of such a system is presented.
+Finally, two validation tools for IMS applications are described, simulators and datasets.
 
@@
 In the case of a multisensor system, it is also required to analyse and determine what is the better fusion approach to use and in which of the processing stages this fusion should be performed, in order to get better results than a single-sensor based system.
-Below, processing stages, fusion approaches, methods and architecture proposal are presented.
 
@@
 This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, for taking immediate actions on traffic control, issuing of traffic tickets, warning drivers about possible incidents or improving transportation policies in a long-term.
-In figure \ref{proc_stages}, are depicted the previously described stages, and how the data volume is reduced while data meaning increases in the last stages.
+In figure \ref{proc_stages}, are depicted previously described stages, and also is shown how the data volume is reduced while data meaning increases in the last stages.
 
@@
 \subsection{Fusion approaches}
-\subsection{Methods and techniques}
-\subsection{Architecture proposal}
+
+Depending on system design, if it has multiple sensors of the same type or different type, a data fusion approach should be chosen.
+When data came from same-type sensors, it is usually fused at low levels using techniques for temporal and/or spatial alignment, depending on sensors configuration.
+This is the case for a network of lasers or lidars or for multi-camera systems.
+If the system have different type of sensors, data from them may be fused at mid level, based on  extracted features or classes on each subsystem; or may be fused at high level if each subsystem delivers control or decision outputs.
+
+\section{Methods and techniques}
+
+\subsection{Preprocessing and Background removal}
+\subsection{Object Recognition}
+\subsection{Feature Extraction}
+\subsection{Tracking and Classification}
+
 \section{Validation approaches}
+
+Before deploying an IMS, it is needed to test some of its components and validate their results.
+Two commonly used tools for this purpose are traffic simulators and datasets, depending on the component to be tested.
+Below, a description of each one is presented.
+
 \subsection{Transportation and Traffic Simulations}
@@
 \subsubsection{KoPER Dataset}
+
+\section{Architecture proposal}

### 2015-06-11 ch3-arch_sys.tex
Content added to chapter 3

@@
 Then an architecture proposal for the implementation of such a system is presented.
-Finally, two validation tools for IMS applications are described, simulators and datasets.
+Finally, two validation tools for IMS applications are described, simulation models and datasets.
 
@@
 Before deploying an IMS, it is needed to test some of its components and validate their results.
-Two commonly used tools for this purpose are traffic simulators and datasets, depending on the component to be tested.
+Two commonly used tools for this purpose are traffic simulation models and datasets, depending on the component to be tested.
 Below, a description of each one is presented.
 
-\subsection{Transportation and Traffic Simulations}
+\subsection{Transportation and Traffic Simulation}
+
+A more detailed analysis of traffic simulation models and simulation platforms could be found in \cite{AdamsBoxill2000, Barcelo2000, Kitamura2005, Lieberman1992}
 \subsubsection{Simulators Classification}
 \subsection{Intersection monitoring Datasets}
-\subsubsection{POSSi Dataset}
-\subsubsection{KoPER Dataset}
+
+As mentioned in section \ref{s23}, POSS-i and Ko-PER projects are leading the development of multisensor Intersection Management Systems.
+One of contribution of these project is the creation of datasets of such systems.
+They provide camera and laser information of a monitored intersection in Peking, China and Aschaffenburg, Germany, respectively.
+Next, a description of these two datasets will be given.
+
+\subsubsection{POSSi Dataset }
+
+POSSi dataset\footnote{Available at http://www.poss.pku.edu.cn/download.html}
+\subsubsection{KoPER Dataset }
+
+Ko-PER dataset\footnote{Available at http://www.uni-ulm.de/in/mrm/forschung/datensaetze.html}
+
+The full description of this dataset is presented in \cite{Strigel2014}.
 

### 2015-06-11 ch4-laser.tex
Initiated chapter 4

@@
 
+In this chapter is described the development of a laser based system for intersection monitoring
+
 \section{Preprocessing and Background removal}
+
+The first step in processing laser data is the removal of irrelevant frames, maybe due to communication errors or due to corrupted data.
+For this stage is proposed a filter based on the of entropy of data, calculated for each frame.
+
 \section{Object Recognition}

### 2015-06-12 ch4-laser.tex
Updated chapter 4

@@
 The first step in processing laser data is the removal of irrelevant frames, maybe due to communication errors or due to corrupted data.
-For this stage is proposed a filter based on the of entropy of data, calculated for each frame.
+For this stage is proposed a filter based on the of entropy of data, calculated for each frame, because it is not expected to have sudden changes in entropy between consecutive frames.
+
+In this case histogram-based entropy estimation is used, which is commonly used in image processing.
+The first step is to compute histogram $P$ of the frame $f$ using 256 bins, then $P$ is normalized using the sum of each bin value.
+After this, entropy $H$ of frame $f$ is calculated as follows:
+
+\begin{equation}
+ H(P)=-\sum_{i=0}^{255}{ p_i.\log_{2}{p_i}} 
+\end{equation}
+
+In figure \ref{entropy_frames} is depicted the evolution of entropy calculated on 300 frames of a laser reading.
+It can be seen that there are frames with abrupt changes in entropy value, for example frames 97 and 283.
+
+\begin{figure}[ht!]
+\centering
+\input{fig/4/entropy_frame.tex}
+\caption{Entropy of frames 1 to 300 of laser readings from sensor 7.}
+\label{entropy_frames}
+\end{figure}
+
+Figure \ref{l7-f283} shows the actual laser data of frame 283 and its neighbours and also entropy values aroud objective frame.
+It is clear now that frame 283 is inconsistent with frames 282 and 284, for this reason this frame is considered as corrupted and should be discarded for next stages
+
+\begin{figure}[ht!]
+\centering
+\input{fig/4/l7-f283.tex}
+\caption{Detailed visualisation of entropy around frame 283.}
+\label{l7-f283}
+\end{figure}
 

### 2015-09-30 ch3-arch_sys.tex
Some corrections and chapter labels reviewed

@@
 
-%\chapter {Architecture Description and System Specification}
-\chapter {System Description}
+\chapter [Architecture Description and System Specification]{Architecture Description and System Specification}
+\chaptermark {System Description}
 
 Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors and computing capabilities.
-These enhancements have allowed to deploy more of these types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control.
+Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step.
 Also it is needed to test and validate the developments prior to a real and full functional implementation.
-The first part of this chapter describe main stages in a intersection management system based on image and range sensors, and methods used in these stages.
+The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages.
 Then an architecture proposal for the implementation of such a system is presented.
@@
 
-Multicamera and multilasers monitoring systems offer more information about environment that can be merged to provide a better representation of the whole scene, and to detect more acurately the objects in the intersection and prevent possible incidents.
-For designing an single-sensor or multi-sensor IMS system, there are some basic processing stages to have into account.
-In the case of a multisensor system, it is also required to analyse and determine what is the better fusion approach to use and in which of the processing stages this fusion should be performed, in order to get better results than a single-sensor based system.
+Multicamera and multilasers monitoring systems offer more information about environment that can be merged to provide a better representation of the whole scene, detect with more accuracy the objects in the intersection, and prevent possible incidents.
+For designing a single-sensor or multi-sensor IMS, there are some basic processing stages to have into account.
+In the case of a multisensor system, it is also required to analyse and determine which is the better fusion approach to use and in which of the processing stages this fusion should be performed, in order to get better results than a single-sensor based system.
 
@@
 
-In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: Filtering, feature extraction, pattern recognition and situation assessment.
+In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: filtering, feature extraction, pattern recognition and situation assessment.
 The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene and remove noise and irrelevant data.
@@
 In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest.
-This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, for taking immediate actions on traffic control, issuing of traffic tickets, warning drivers about possible incidents or improving transportation policies in a long-term.
-In figure \ref{proc_stages}, are depicted previously described stages, and also is shown how the data volume is reduced while data meaning increases in the last stages.
+This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
+In figure \ref{proc_stages}, previously described stages are depicted, and also is shown how the data volume is reduced while data meaning increases in the last stages.
 

### 2015-10-16 ch3-arch_sys.tex
Fixed some typos in chapter 3 and added new figure 3.2

@@
 
-In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: filtering, feature extraction, pattern recognition and situation assessment.
-The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene and remove noise and irrelevant data.
+In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment.
+The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene, remove noise and irrelevant data.
+Spatio-temporal alignment of data is also performed in this stage.
 In the second stage, the objective is to identify elements within the foreground and extract relevant features of them.
@@
 \includegraphics[scale=0.55]{fig/3/proc_stages.png}
-\caption{Processing stages in an IMS.}
+\caption{Dataflow through processing stages in an IMS.}
 \label{proc_stages}
@@
 
-\subsection{Preprocessing and Background removal}
-\subsection{Object Recognition}
-\subsection{Feature Extraction}
-\subsection{Tracking and Classification}
+Different tasks could be performed in each aforementioned stages, as is referred in figure \ref{proc_stages_tasks}.
+Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data.
+Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
+\caption{Processing stages and tasks performed.}
+\label{proc_stages_tasks}
+\end{figure}
+
+\subsection{Preprocessing}
+\subsubsection{Background subtraction}
+\subsubsection{Time-space alignment}
+\subsection{Feature Analysis}
+\subsubsection{Segmentation}
+\subsubsection{Feature extraction}
+\subsection{Pattern Recognition}
+\subsubsection{Object association}
+\subsubsection{Object tracking}
+\subsubsection{Object classification}
+\subsection{Situation Assessment}
 
@@
 As mentioned in section \ref{s23}, POSS-i and Ko-PER projects are leading the development of multisensor Intersection Management Systems.
-One of contribution of these project is the creation of datasets of such systems.
+One of the contributions of these projects is the creation of datasets of such systems.
 They provide camera and laser information of a monitored intersection in Peking, China and Aschaffenburg, Germany, respectively.

### 2015-10-16 ch3-arch_sys.tex
Updated ch3, added some paragraphs about traffic simulation.

@@
 
-Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors and computing capabilities.
+Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors manufacturing and computing capabilities.
 Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step.
@@
 In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment.
-The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene, remove noise and irrelevant data.
-Spatio-temporal alignment of data is also performed in this stage.
+The aim of the first stage is to extract data of interest from the raw sensor information, using filtering to remove noise and irrelevant data, and background subtraction techniques to get the foreground of the scene.
+Spatial-temporal alignment of data is also performed in this stage.
 In the second stage, the objective is to identify elements within the foreground and extract relevant features of them.
@@
 Depending on system design, if it has multiple sensors of the same type or different type, a data fusion approach should be chosen.
-When data came from same-type sensors, it is usually fused at low levels using techniques for temporal and/or spatial alignment, depending on sensors configuration.
+When data came from same-type sensors, it is usually fused at low levels using techniques for temporal-spatial alignment, depending on sensors configuration.
 This is the case for a network of lasers or lidars or for multi-camera systems.
@@
 
-Different tasks could be performed in each aforementioned stages, as is referred in figure \ref{proc_stages_tasks}.
+Different tasks could be performed in each one of aforementioned stages, as is referred in figure \ref{proc_stages_tasks}.
 Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data.
@@
 \subsection{Preprocessing}
+\subsubsection{Time-space alignment}
 \subsubsection{Background subtraction}
-\subsubsection{Time-space alignment}
-\subsection{Feature Analysis}
+\subsubsection{Filtering}
+\subsection{Feature analysis}
 \subsubsection{Segmentation}
 \subsubsection{Feature extraction}
-\subsection{Pattern Recognition}
+\subsubsection{Feature selection}
+\subsection{Pattern recognition}
 \subsubsection{Object association}
@@
 \subsubsection{Object classification}
-\subsection{Situation Assessment}
+\subsection{Situation assessment}
 
@@
 \subsection{Transportation and Traffic Simulation}
+
+Transportation is a highly complex activity where different elements, like infrastructure, vehicles and pedestrians, affect efficiency, safety and quality of traffic.
+Intersections are special cases because there exists a high interaction between those mentioned elements making of these places critical points for mobility.
+For this reason, it is needed to have traffic models to allow the simulation of new policies or deployments intended to enhance transportation.
+
+Three widely-known models for this kind of analysis are macroscopic model, microscopic model and mesoscopic model.
+The macroscopic model of traffic flow is based on a hydrodynamic analogy, modeling traffic as a fluid process characterized by three main variables, density, volume and speed, and the objective is to describe time-space evolution of those variables.
 

### 2015-11-20 paper01/paper.tex
Created paper draft

% Single laser work
\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{graphicx} % for \includegraphics[scale=•]{•}

\begin{document}
\title{Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data}

\author{Gustavo Velasco-Hernandez, Eduardo Caicedo-Bravo \\
Universidad del Valle\\
{\tt\small velasco.gustavo@correounivalle.edu.co, eduardo.caicedo@correounivalle.edu.co}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, mei vulputate argumentum an, usu vidit labitur ancillae et, quot accusamus cum et. Recteque dissentiet vim ea, est virtute alterum ea, mei dico scribentur in. Et eam paulo soleat graeci. Ius viderer habemus scriptorem ut, no mea vocibus albucius. Sed no perpetua suscipiantur, pro diam nullam erroribus id. Pro labore audire et, tale eligendi mediocrem his cu, te sonet adipisci ius. Exerci regione noluisse mea no, no usu mazim mediocrem assentior, at audire volumus eam. Soluta oporteat recteque ut ius, nam an sumo solet facilisis, rebum aeque eam et. Pri quot graece in. Dictas liberavisse.
\end{abstract}

\section{Introduction}

\section{Stages Definition}
In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment. The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene, remove noise and irrelevant data. Spatio-temporal alignment of data is also performed in this stage. In the second stage, the objective is to identify elements within the foreground and extract relevant features of them. The third stage receives the set of features from the previous stage and performs recognition and classification tasks. Also, tracking and prediction of objects' state is performed based on historic information. In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest. This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis. In figure \ref{proc_stages}, previously described stages are depicted, and also is shown how the data volume is reduced while data meaning increases in the last stages.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{../fig/3/proc_stages.png}
\caption{Dataflow through processing stages in an IMS.}
\label{proc_stages}
\end{figure}

Different tasks could be performed in each aforementioned stages, as is referred in figure \ref{proc_stages_tasks}. Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data. Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{../fig/3/processing_stages_and_tasks.png}
\caption{Processing stages and tasks performed.}
\label{proc_stages_tasks}
\end{figure}

\section{Laser-based System Implementation}

\subsection{Dataset}
 The dataset used for this work was provided by POSS research group
\subsection{Preprocessing}
\subsection{Feature Analysis}
\subsection{Pattern Recognition}
\subsection{Situation Assesment}

\section{Results}

\section{Conclusions and Future Work}

{\small
\bibliographystyle{plain}
\bibliography{../bibliography}
}

\end{document}

### 2015-11-20 paper01/paper.tex
Added preprocessing paragraph

@@
 \centering
-\includegraphics[scale=0.55]{../fig/3/proc_stages.png}
+\includegraphics[scale=0.35]{../fig/3/proc_stages.png}
 \caption{Dataflow through processing stages in an IMS.}
@@
 \centering
-\includegraphics[scale=0.55]{../fig/3/processing_stages_and_tasks.png}
+\includegraphics[scale=0.35]{../fig/3/processing_stages_and_tasks.png}
 \caption{Processing stages and tasks performed.}
@@
 \end{figure}
+\subsection{Preprocessing}
+ In the preprocessing stage raw data from sensor is received and the purpose is to enhance this data through filtering noise, removing outliers and discarding corrupted data.
+Also, in order to extract meaningful data, background removal techniques are applied in this stage.
+For doing this, a background model should be generated.
+One typical approach to generate a background model is to use a threshold to determine if certain measure corresponds to background or foreground.
+This threshold is computed based on a peak value found in histogram information of the measure within a time window.
+Another approach consist in describe de data using a probability distribution function.
+\subsection{Feature Analysis}
+\subsection{Pattern Recognition}
+\subsection{Situation Assesment}
 
@@
 \subsection{Dataset}
- The dataset used for this work was provided by POSS research group
+ The dataset used for this work was provided by POSS research group and was used for \cite{Zhao2009}.
+The dataset consist of ten minutes of laser scanner raw data from six sensors arranged horizontally over an intersection near Peking University.
+Background model and calibration data for each laser scanner is also provided.
+Additionally, dataset contains trajectory info of objects in the scene, generated by their algorithm.
+
 \subsection{Preprocessing}
+
 \subsection{Feature Analysis}

### 2015-11-20 paper01/paper.tex
few changes

@@
 \section{Introduction}
+Lorem ipsum dolor sit amet, mei vulputate argumentum an, usu vidit labitur ancillae et, quot accusamus cum et.
+Recteque dissentiet vim ea, est virtute alterum ea, mei dico scribentur in.
+Et eam paulo soleat graeci.
+Ius viderer habemus scriptorem ut, no mea vocibus albucius.
+Sed no perpetua suscipiantur, pro diam nullam erroribus id.
+Pro labore audire et, tale eligendi mediocrem his cu, te sonet adipisci ius.
+Exerci regione noluisse mea no, no usu mazim mediocrem assentior, at audire volumus eam.
+Soluta oporteat recteque ut ius, nam an sumo solet facilisis, rebum aeque eam et.
+Pri quot graece in.
+Dictas liberavisse.
 
@@
 In the designing of an IMS, there are four main stages that have to be performed from the data source to final output: preprocessing, feature analysis, pattern recognition and situation assessment.
+
 The aim of the first stage is to extract data of interest from the raw sensor information, using filtering and background subtraction techniques to get the foreground of the scene, remove noise and irrelevant data.
@@
 In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest.
-This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
+
+The output of the fourth stage could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
 In figure \ref{proc_stages}, previously described stages are depicted, and also is shown how the data volume is reduced while data meaning increases in the last stages.

### 2015-11-23 paper01/paper.tex
Added DBSCAN reference to bibliogrphy. Added content to paper01

@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, mei vulputate argumentum an, usu vidit labitur ancillae et, quot accusamus cum et.
-Recteque dissentiet vim ea, est virtute alterum ea, mei dico scribentur in.
-Et eam paulo soleat graeci.
-Ius viderer habemus scriptorem ut, no mea vocibus albucius.
-Sed no perpetua suscipiantur, pro diam nullam erroribus id.
-Pro labore audire et, tale eligendi mediocrem his cu, te sonet adipisci ius.
-Exerci regione noluisse mea no, no usu mazim mediocrem assentior, at audire volumus eam.
-Soluta oporteat recteque ut ius, nam an sumo solet facilisis, rebum aeque eam et.
-Pri quot graece in.
-Dictas liberavisse.
+In this work is described a stage-oriented design of an intersection management system based on a laser scanner sensor.
+After an introduction of the use of laser scanners in traffic monitoring, four stages are defined in the process flow of such a systems: preprocessing, feature analysis, pattern recognition and situation assesment.
+Then, an example implementation using a laser scanner dataset is presented.
 \end{abstract}
@@
 Different tasks could be performed in each aforementioned stages, as is referred in figure \ref{proc_stages_tasks}.
-Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data.
-Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.
+Below there is a description of common concepts and techniques associated with each of these tasks.
 
@@
 \subsection{Preprocessing}
+
  In the preprocessing stage raw data from sensor is received and the purpose is to enhance this data through filtering noise, removing outliers and discarding corrupted data.
-Also, in order to extract meaningful data, background removal techniques are applied in this stage.
+Also, in order to extract meaningful information, background removal techniques are applied in this stage.
 For doing this, a background model should be generated.
 One typical approach to generate a background model is to use a threshold to determine if certain measure corresponds to background or foreground.
-This threshold is computed based on a peak value found in histogram information of the measure within a time window.
-Another approach consist in describe de data using a probability distribution function.
+This threshold is computed based on a peak value found in histogram of the measure within a time window.
+Another approach consist in describe the data using a probability distribution function, using maximum likelihood estimation, commonly of a gaussian model.
+
+Sometimes, the threshold technique is enough for modeling static backgrounds like walls, buildings or ground.
+But in other cases, it could be found a non-stable background, for example, when there exist moving vegetation or object borders, and a mixture of models may retrieve a better representation of the data instead.
+
 \subsection{Feature Analysis}
+
+After obtaining the foreground of the scene, it is needed to extract relevant points that could represent objects of interest.
+Clustering is used to group points that belong to the same object, specially algorithms where estimated number of cluster is not needed.
+
 \subsection{Pattern Recognition}
@@
 
+As mentioned before, the dataset provides a background model for each laser scanner.
+This model was generated using a histogram of each sampling angle of scanning, then a peak is found indicating a motionless object, considered as background.
+With the peak values at all sampling angles the background model is obtained.
+Now, when a new frame comes from the laser scanner, the measure at certain angle is compared with the peak value associated with that angle.
+If the difference is larger than a given threshold, the measured value is considered to belong to a moving object at the intersection.
+
 \subsection{Feature Analysis}
+
+With the set of points marked as foreground, clustering is performed to identify the set of points belonging to the same object.
+The algorithm used in this implementation is DBSCAN, which stands for Density-Based Spatial Clustering of Applications with Noise.
+This algorithm does not need an estimated number of clusters as input, instead of this, it requires only two parameters: a minimum number of points per cluster, m, and a neighbourhood measure, $\epsilon$.
+A detailed description of the algorithm, can be found in \cite{Ester96}.
 \subsection{Pattern Recognition}

### 2015-11-23 paper01/paper.tex
Added new figures and paper was organized

@@
 
-\usepackage{graphicx} % for \includegraphics[scale=•]{•}
+\usepackage[pdftex]{graphicx} % for \includegraphics[scale=•]{•}
+\usepackage{color}
 
 \begin{document}
-\title{Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data}
+\title{[DRAFT] - Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data}
 
@@
 \subsection{Pattern Recognition}
+
+-TODO-
+
 \subsection{Situation Assesment}
+
+-TODO-
 
@@
 Additionally, dataset contains trajectory info of objects in the scene, generated by their algorithm.
+Figure \ref{inter_cfg} show intersection scenario, indicating position and orientation of each laser scanner inlcuded in dataset.
+
+\begin{figure}[ht!]
+\centering
+
+\input{fig/intersection_config.tex}
+\caption{System setup}
+\label{inter_cfg}
+\end{figure}
 
@@
 If the difference is larger than a given threshold, the measured value is considered to belong to a moving object at the intersection.
+In figure \ref{bg_proc} is described the background removal process.
+
+\begin{figure}[ht!]
+\centering
+
+\input{fig/bg_process.tex}
+\caption{Example of background removal applied to frame 123 from laser scanner 2 of dataset.
+In the upper plot, the raw data from the laser scanner is depicted.
+In the lower plot, red points represent the background model estimated based on peak values of the histogram.
+Black points are those marked as foreground after comparison of raw data with background data.
+The threshold used was 20.
+(Axis in centimeters).}
+\label{bg_proc}
+\end{figure}
 
@@
 A detailed description of the algorithm, can be found in \cite{Ester96}.
+
 \subsection{Pattern Recognition}
+
+-TODO-
+
 \subsection{Situation Assesment}
+
+-TODO-
 
@@
 
+-TODO-
+
 \section{Conclusions and Future Work}
+
+-TODO-
 

### 2015-11-24 paper01/paper.tex
Added alignment info

@@
 
- In the preprocessing stage raw data from sensor is received and the purpose is to enhance this data through filtering noise, removing outliers and discarding corrupted data.
-Also, in order to extract meaningful information, background removal techniques are applied in this stage.
+ In the preprocessing stage raw data from sensor is received and the purpose is to enhance this data through filtering, removing noise and discarding corrupted data.
+Also, space and time alignment is done in this stage.
+
+\subsubsection{Background Removing}
+
+In order to extract meaningful information, background removal techniques are applied in this stage.
 For doing this, a background model should be generated.
@@
 But in other cases, it could be found a non-stable background, for example, when there exist moving vegetation or object borders, and a mixture of models may retrieve a better representation of the data instead.
+
+\subsubsection{Space and Time alignment}
+
+In some cases, it could be desired to have a fixed base of time for trigger sensor readings, for synchronisation purposes or for implement fusion between different sensors within a time slot.
+Is for this reason that time alignment of data is done.
+
+On the other side, in the case of laser scanners, the measures are referenced to its own coordinate systems.
+Calibration is needed to transform those measures to a global coordinate systems which represents the whole intersection scenario.
 

### 2016-11-08 paper01/paper.tex
Abstract modified in paper, added bg_process.eps

@@
 \begin{abstract}
-In this work is described a stage-oriented design of an intersection management system based on a laser scanner sensor.
-After an introduction of the use of laser scanners in traffic monitoring, four stages are defined in the process flow of such a systems: preprocessing, feature analysis, pattern recognition and situation assesment.
-Then, an example implementation using a laser scanner dataset is presented.
+The supervision of vehicular intersections is a major need for improving transportation systems because intersections are complex scenarios where different traffic actors interact between them.
+Recently, laser-based systems have been proposed and implemented to sense and to monitor intersections, giving good results as those based on cameras.
+In this work a stage-oriented design of an intersection management system based on laser scanner sensor data is proposed.
+The main objective of the proposed architecture is that it should have scalability, modularity, and high integrability.
+In order to achieve those objectives, the process flow of an intersection management system (IMS) is divided into four stages: preprocessing, feature analysis, pattern recognition, and situation assessment.
+Each of these stages is explained and some commonly used techniques are described.
+Finally, we present an example implementation using a laser scanner dataset, and a comparison between a single-laser approach and a multi-laser approach.
+
 \end{abstract}

### 2017-02-28 paper01/paper.tex
late commit

@@
 \begin{abstract}
-The supervision of vehicular intersections is a major need for improving transportation systems because intersections are complex scenarios where different traffic actors interact between them.
+The supervision of vehicular intersections is a major need for improving transportation systems because these are complex scenarios where different traffic elements interact between them.
 Recently, laser-based systems have been proposed and implemented to sense and to monitor intersections, giving good results as those based on cameras.
-In this work a stage-oriented design of an intersection management system based on laser scanner sensor data is proposed.
+In this work a stage-oriented design of an intersection management system based on laserscanner sensor data is proposed.
 The main objective of the proposed architecture is that it should have scalability, modularity, and high integrability.
@@
 Each of these stages is explained and some commonly used techniques are described.
-Finally, we present an example implementation using a laser scanner dataset, and a comparison between a single-laser approach and a multi-laser approach.
+Finally, we present an example implementation using a laserscanner dataset, both in a single-laser approach and a multi-laser approach.
 
@@
 \section{Introduction}
-Lorem ipsum dolor sit amet, mei vulputate argumentum an, usu vidit labitur ancillae et, quot accusamus cum et.
-Recteque dissentiet vim ea, est virtute alterum ea, mei dico scribentur in.
-Et eam paulo soleat graeci.
-Ius viderer habemus scriptorem ut, no mea vocibus albucius.
-Sed no perpetua suscipiantur, pro diam nullam erroribus id.
-Pro labore audire et, tale eligendi mediocrem his cu, te sonet adipisci ius.
-Exerci regione noluisse mea no, no usu mazim mediocrem assentior, at audire volumus eam.
-Soluta oporteat recteque ut ius, nam an sumo solet facilisis, rebum aeque eam et.
-Pri quot graece in.
-Dictas liberavisse.
+
+-TODO-
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.85]{fig/carReferenceSystem.png}
+\caption{Vehicle reference coordinate system}
+\label{vehicle_cs}
+\end{figure}
+
+In figure \ref{vehicle_cs} is shown a commonly used reference coordinate system for vehicles.
+Based on this, several laser-based systems have been proposed taking a plane as the main plane for laser scanner positioning.
+For example, F{\"u}erstenberg in  \cite{Fuerstenberg2000} proposes the use XZ plane scanning for vehicle classification and scanning on YZ plane for vehicle counting.
+Related to YZ plane, in \cite{Harlow2001} and \cite{Vivet2013} present a deployment for vehicle monitoring scanning from the top and Gómez in \cite{Gomez2013} presents a side-view scanning for vehicle classification fused with a vision system.
+In \cite{Goldhammer2012} and \cite{Strigel2014}, Goldhammer and Striegel, respectively, detail an implemetation using a set of multilayer laser scanners deployed in different configurations for scanning from the top of the road, some using YZ plane and some using XZ plane.
+Recently, the use of XY plane has increased, and two main approaches arise: on-road and on-board systems.
+On-road systems are installed in infrastructure, aiming to detect passing vehicles, while on-board systems are installed on vehicles to detect the sourrounding environment.
+Both of them take the XY plane as main plane for scanning.
+Some examples of on-road sytems could be found in \cite{Zhao2006, Zhao2008, Zhao2009, Zhao2012} and \cite{Perng2014}.
+Petrovskaya in \cite{Petrovskaya2009} presents an On-board implementation.
 
@@
 {\small
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{../bibliography}

### 2017-06-08 paper01/paper.tex
Introduction completed

@@
 
--TODO-
+In transportation systems one of the most desirable scenarios to improve efficiency and safety are intersections.
+This because intersections are places where vehicles arrive from different directions at different velocities, increasing the chances for incidents and crashes.
+Choi \cite{Choi2010} states that 40\% of reported traffic accidents in the US, were intersection related.
+Also, in  \cite{CorporacionFondodePrevencionVial2010}, is reported that for Colombia in 2011, most of the accidents in the main cities were at intersections.
+
+Several approaches for monitoring intersections are based on sensors on infrastructure like inductive loops, range scanners and cameras.
+Inductive loops detects presence of vehicles, which is simple for processing but information that could be extracted from they is limited.
+Cameras, on the other side, offer a high volume of data, but their processing requirements are high for extracting information.
+Range scanners are an intermediate option in which data from them is much high than from inductive loops, but not as high as from cameras and processing techniques for range data are not computational expensive as those for treating images or videos.
 
@@
 \centering
-\includegraphics[scale=0.85]{fig/carReferenceSystem.png}
+\includegraphics[scale=0.8]{fig/carReferenceSystem.png}
 \caption{Vehicle reference coordinate system}
@@
 
-In figure \ref{vehicle_cs} is shown a commonly used reference coordinate system for vehicles.
+For range-based traffic monitoring systems there are three commonly used reference coordinate system for vehicles (Figure \ref{vehicle_cs}).
 Based on this, several laser-based systems have been proposed taking a plane as the main plane for laser scanner positioning.
 For example, F{\"u}erstenberg in  \cite{Fuerstenberg2000} proposes the use XZ plane scanning for vehicle classification and scanning on YZ plane for vehicle counting.
-Related to YZ plane, in \cite{Harlow2001} and \cite{Vivet2013} present a deployment for vehicle monitoring scanning from the top and Gómez in \cite{Gomez2013} presents a side-view scanning for vehicle classification fused with a vision system.
+Related to YZ plane, \cite{Harlow2001} and \cite{Vivet2013} present a deployment for vehicle monitoring scanning from the top and Gómez in \cite{Gomez2013} presents a side-view scanning for vehicle classification fused with a vision system.
 In \cite{Goldhammer2012} and \cite{Strigel2014}, Goldhammer and Striegel, respectively, detail an implemetation using a set of multilayer laser scanners deployed in different configurations for scanning from the top of the road, some using YZ plane and some using XZ plane.
@@
 Petrovskaya in \cite{Petrovskaya2009} presents an On-board implementation.
+
+All of the previous developments share a common processing stages that could be enumarated: preprocessing, feature analysis, pattern recognition, and situation assessment.
+In the section 2, these stages are explained and some common processing substages for each one are introduced.
+In section 3 is presented an example implementation based on a dataset and showing some methods and techniques used in the proposed stages.
+Section 4 presents the result of a single-laser and a multi-laser deployments.
+Finally, in section 6 are summarized the conclusions and some future work perspectives are proposed.
 

### 2017-09-21 paper01/paper.tex
fixed redundancy
Added details for feature analysis and pattern recognition

@@
 In some cases, it could be desired to have a fixed base of time for trigger sensor readings, for synchronisation purposes or for implement fusion between different sensors within a time slot.
-Is for this reason that time alignment of data is done.
+It is for this reason that time alignment of data is done.
 
@@
 
-After obtaining the foreground of the scene, it is needed to extract relevant points that could represent objects of interest.
-Clustering is used to group points that belong to the same object, specially algorithms where estimated number of cluster is not needed.
+After obtaining the foreground of the scene, it is needed to extract relevant points that could represent elements of interest in the intersection, like vehicles, pedestrians or obstacles.
+In this stage clustering is used to group points that belong to the same object, and for the nature of the environment, algorithms where estimated number of cluster is not needed are prefered.
 
@@
 
--TODO-
+From the previous stage we have a set of blobs as result of clustering, and based on the features of those blobs, different classes of objects could be recognized.
+Different classification types are implemented depending on the type of application, binary classification or multiclass classification.
+
+When objects are identified, some relations between objects should be extracted to get more information about the scene.
+Relations between objects of the same class, objects of different classes or objects and environment are possible, both in a single timeslot or in sucesive timeslots.
 
@@
 
-With the set of points marked as foreground, clustering is performed to identify the set of points belonging to the same object.
+Clustering is performed on the foreground extracted to identify the set of points belonging to the same object.
 The algorithm used in this implementation is DBSCAN, which stands for Density-Based Spatial Clustering of Applications with Noise.
@@
 
--TODO-
+At this stage, a bounding box is computed for each cluster found in previous stage.
+Them, the area and center of the bounding box are calculated and this is stored as a Blob entity.
+Now, blob information and scen model are analyzed in order to get more knowledge about how are blobs distributed over the legs of intersection.
 

### 2017-09-21 paper01/paper.tex
Added subsections titles in result section

@@
 
--TODO-
+Three different scene configurations were defined in order to test the system proposal: using a single laser scanner, using three laser scanners and another with all the six laser scanners available in the dataset.
+
+\subsection{Scene 1: Single laser scanner}
+
+For this configuration laser scanner LMS2 is chosen because it has a good coverage of intersection and leg 2.
+
+\subsection{Scene 2: Three laser scanners}
+
+In this configuration selected laser scanners are LMS1, LMS2 and LMS3 trying to have a general coverage of the intersection from different views
+
+\subsection{Scene 3: Six laser scanners}
+This configuration uses all the available laser from the dataset.
 

### 2018-01-23 ch3-arch_sys.tex
Restructured chapter 3 and added redis reference to bib

@@
 %		* Fusion approaches		
-%		* Methods and techniques
-%		* Architecture proposal
 %	* Validation approaches
@@
 %			* KoPER Dataset
+%	* Architecture proposal
 
@@
 Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step.
-Also it is needed to test and validate the developments prior to a real and full functional implementation.
+It is also needed to test and validate the developments prior to a real and full functional implementation.
 The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages.
@@
 This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
-In figure \ref{proc_stages}, previously described stages are depicted, and also is shown how the data volume is reduced while data meaning increases in the last stages.
+In figure \ref{proc_stages}, previously described stages are depicted, including common task performed at each of these stage and also is shown how the data volume is reduced while data meaning increases in the last stages.
 
@@
 \centering
-\includegraphics[scale=0.55]{fig/3/proc_stages.png}
-\caption{Dataflow through processing stages in an IMS.}
+\includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
+\caption{Dataflow through processing stages in an IMS an commonly performed tasks}
 \label{proc_stages}
@@
 
-Depending on system design, if it has multiple sensors of the same type or different type, a data fusion approach should be chosen.
+Depending on wheter the system has multiple sensors of the same type or different type, a data fusion approach should be chosen.
 When data came from same-type sensors, it is usually fused at low levels using techniques for temporal-spatial alignment, depending on sensors configuration.
@@
 If the system have different type of sensors, data from them may be fused at mid level, based on extracted features or classes on each subsystem; or may be fused at high level if each subsystem delivers control or decision outputs.
+The tasks shown in each of the processing stages (\ref{proc_stages}), could be used as fusion blocks for homogeneous or heterogeneous data.
 
@@
 Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
-\caption{Processing stages and tasks performed.}
-\label{proc_stages_tasks}
-\end{figure}
-
-\subsection{Preprocessing}
-\subsubsection{Time-space alignment}
-\subsubsection{Background subtraction}
-\subsubsection{Filtering}
-\subsection{Feature analysis}
-\subsubsection{Segmentation}
-\subsubsection{Feature extraction}
-\subsubsection{Feature selection}
-\subsection{Pattern recognition}
-\subsubsection{Object association}
-\subsubsection{Object tracking}
-\subsubsection{Object classification}
-\subsection{Situation assessment}
 
@@
 \section{Architecture proposal}
+
+The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output.
+The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from.
+
+\subsection{Data Model}
+
+\subsection{Communication scheme}
+
+In order to isolate the processing tasks of the communication system, a Publisher-Subscriber approach is selected.
+The benefits of this option is that data can be shared between diferent blocks without generating a dependency from publishers to subscribers.
+Another benefit is that exposing a defined mechanism for publishing or subscribing, allows the system to be implementation agnostic.
+
+Taking these reasons into account, Redis is chosen as communication platform.
+As stated in their website, "Redis is an open source (BSD licensed), in-memory data structure store, used as a database, cache and message broker"\cite{Redis} which support Publisher-Subscriber paradigm, allowing greater scalability and a more dynamic network topology.
+
+\subsection{Processing Blocks}

### 2018-02-18 ch1-introduction.tex
Updated chapter 1 and 3

% Introduction
\chapter [Introduction]{Introduction}
\chaptermark{Introduction}

\section{Goals}

The main goal for this proposal is to conceive a multisensor architecture for an intersection management system and deploy it in a simulated scenario. In order to achieve this goal, these objectives were set:

\begin{itemize}
\item To make a literature review on intelligent transportation systems, focusing on developments about intersection management
\item To define system architecture and specifications, and choose a platform which fits requirements for the deployment
\item To develop and implement an intersection monitoring system based on laser and video sensors using sensor fusion techniques
\item To propose and deploy a method for incident estimation and warning generation
\item To set a test and evaluation protocol for the developments made on the choosen platform 
\end{itemize}

### 2018-02-18 ch3-arch_sys.tex
Updated chapter 1 and 3

@@
 Although several types of sensors are used for intersection monitoring and supervision, the use of cameras, lasers and lidars has increased due to advances in sensors manufacturing and computing capabilities.
-Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control step.
+Such enhancements allows to deploy more of those types of sensors per scenario and it is required to define some processing stages from raw data capture through decision and control stages.
 It is also needed to test and validate the developments prior to a real and full functional implementation.
-The first part of this chapter describes the main stages in a intersection management system based on image and range sensors, and the methods used in these stages.
-Then an architecture proposal for the implementation of such a system is presented.
-Finally, two validation tools for IMS applications are described, simulation models and datasets.
+The first part of this chapter describes the main stages in a intersection management system, from data preprocessing to situation assesment.
+Then, two validation tools for IMS applications are described, simulation models and datasets.
+And finally, the proposed architecture for the implementation of an IMS system is presented.
 
@@
 Also, tracking and prediction of objects' state is performed based on historic information.
-In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situation or events of interest.
+In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situations or events of interest.
 This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
@@
 The tasks shown in each of the processing stages (\ref{proc_stages}), could be used as fusion blocks for homogeneous or heterogeneous data.
-
-\section{Methods and techniques}
-
-Different tasks could be performed in each one of aforementioned stages, as is referred in figure \ref{proc_stages_tasks}.
-Below there is a description of common concepts and methods associated with each of these tasks, some of them are sensor-independent and others are focused on a specific sensor or type of data.
-Additionally, these tasks could be used as fusion blocks for homogeneous or heterogeneous data.
 
@@
 The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from.
+Three main components of the architecture are defined: Data model, communication scheme and  processing blocks.
 
 \subsection{Data Model}
+
+The data model proposed for the system includes the abstraction of the sensing elements and the intersection itself.
+For the sensing elements is created a Sensor base class and two derived classes for different type of sensors, Laser class and Camera class.
 

### 2018-02-18 ch3-arch_sys.tex
Updated communication subsection

@@
 If the system have different type of sensors, data from them may be fused at mid level, based on extracted features or classes on each subsystem; or may be fused at high level if each subsystem delivers control or decision outputs.
-The tasks shown in each of the processing stages (\ref{proc_stages}), could be used as fusion blocks for homogeneous or heterogeneous data.
+The tasks shown in each of the processing stages (Figure \ref{proc_stages}), could be used as fusion blocks for homogeneous or heterogeneous data.
 
@@
 The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from.
-Three main components of the architecture are defined: Data model, communication scheme and  processing blocks.
-
-\subsection{Data Model}
-
-The data model proposed for the system includes the abstraction of the sensing elements and the intersection itself.
-For the sensing elements is created a Sensor base class and two derived classes for different type of sensors, Laser class and Camera class.
+Three main components of the architecture are defined: communication scheme, data model and  processing blocks.
 
@@
 
+For publishers and subscribers to exchange messages, channels are defined with labels using a namespace approach that describe the source of data and the kind of data.
+For example a channel containing raw data from a laser scanner could be labeled as "".
+%\/sensors\/range\/laser_N\/data\/raw
+Redis is also used as in-memory storage for configuration data, which is not dynamic as the date from the processing flow.
+
+\subsection{Data Model}
+
+The data model proposed for the system includes the abstraction of the sensing elements and the intersection itself.
+For the sensing elements is created a Sensor base class and two derived classes for different type of sensors, Laser class and Camera class.
+
 \subsection{Processing Blocks}

### 2018-02-21 ch3-arch_sys.tex
Updated communication scheme and data model

@@
 For publishers and subscribers to exchange messages, channels are defined with labels using a namespace approach that describe the source of data and the kind of data.
-For example a channel containing raw data from a laser scanner could be labeled as "".
-%\/sensors\/range\/laser_N\/data\/raw
-Redis is also used as in-memory storage for configuration data, which is not dynamic as the date from the processing flow.
+For example a channel containing raw data from a laser scanner could be labeled as "/sensors/range/laser\_N/data/raw".
+
+Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options.
+This information is loaded into Redis from a JSON file and it is available for any client requiring it.
 
@@
 
-The data model proposed for the system includes the abstraction of the sensing elements and the intersection itself.
-For the sensing elements is created a Sensor base class and two derived classes for different type of sensors, Laser class and Camera class.
+The data model proposed for the system includes the abstraction of the sensing elements, the intersection model and the data used and generated by the processing blocks.
+For the sensing elements, a Sensor base class and two derived classes, Laser class and Camera class, are defined.
+
+---TODO: Describe and add UML of classes --
+-- describe intersection model
+--Describe data from flow
 

### 2018-02-22 ch3-arch_sys.tex
Updated data model section

@@
 ---TODO: Describe and add UML of classes --
+
+The intersection has been modeled as a class with attributes like a label, a Map object, a set of RangeSensors and CameraSensors objects, a set of Leg objects, and a set of Area objects, for inner area of the intersection.
+The Map class contains information about the geometry of the intersection and the coordinate system, including a image intended for visualization of configuration and processing.
+
+The sensors sets are composed of zero or more sensor objects, as defined previously.
+An Area class is defined as having a bounding box and a label	.
+From this class, a derived class Leg is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type.
+
+The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing.
 -- describe intersection model

### 2018-02-27 ch3-arch_sys.tex
Updated data model section and added UML diagram

@@
 The data model proposed for the system includes the abstraction of the sensing elements, the intersection model and the data used and generated by the processing blocks.
-For the sensing elements, a Sensor base class and two derived classes, Laser class and Camera class, are defined.
+For the sensing elements, a Sensor base class and two derived classes, RangeSensor class and ImageSensor class, are defined.
 
----TODO: Describe and add UML of classes --
-
-The intersection has been modeled as a class with attributes like a label, a Map object, a set of RangeSensors and CameraSensors objects, a set of Leg objects, and a set of Area objects, for inner area of the intersection.
+The intersection has been modeled as a class with attributes like a label, a Map object, a set of RangeSensors and CameraSensors objects, a set of Leg objects, and a set of Area objects, for inner areas of the intersection.
 The Map class contains information about the geometry of the intersection and the coordinate system, including a image intended for visualization of configuration and processing.
@@
 From this class, a derived class Leg is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type.
+In figure \ref{data_model} is shown an UML diagram for the aforementioned classes and their relationships
 
-The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing.
--- describe intersection model
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.55]{fig/3/data_model.pdf}
+\caption{UML diagram of defined entities and their relationships}
+\label{data_model}
+\end{figure}
+
+The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to.
+
 --Describe data from flow

### 2018-02-28 ch3-arch_sys.tex
Started processing blocks section and some little fixes

@@
 This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
-In figure \ref{proc_stages}, previously described stages are depicted, including common task performed at each of these stage and also is shown how the data volume is reduced while data meaning increases in the last stages.
+In figure \ref{proc_stages}, previously described stages are depicted, including a list of common tasks performed at each of these stages and also it is shown how the data volume is reduced while data meaning increases in the last stages.
 
@@
 \includegraphics[scale=0.55]{fig/3/processing_stages_and_tasks.png}
-\caption{Dataflow through processing stages in an IMS an commonly performed tasks}
+\caption{Processing stages in an IMS and commonly performed tasks within each of them}
 \label{proc_stages}
@@
 For publishers and subscribers to exchange messages, channels are defined with labels using a namespace approach that describe the source of data and the kind of data.
-For example a channel containing raw data from a laser scanner could be labeled as "/sensors/range/laser\_N/data/raw".
+For example a channel containing raw data from a laser scanner could be labeled as \texttt{/sensors/range/laser\_1/data/raw}.
 
@@
 
-The data model proposed for the system includes the abstraction of the sensing elements, the intersection model and the data used and generated by the processing blocks.
+The data model proposed for the system includes the abstraction of the sensing elements and the intersection model.
 For the sensing elements, a Sensor base class and two derived classes, RangeSensor class and ImageSensor class, are defined.
@@
 An Area class is defined as having a bounding box and a label	.
-From this class, a derived class Leg is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type.
+From this class, a derived class, Leg, is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type.
 In figure \ref{data_model} is shown an UML diagram for the aforementioned classes and their relationships
@@
 \centering
-\includegraphics[scale=0.55]{fig/3/data_model.pdf}
+\includegraphics[scale=0.5]{fig/3/data_model.pdf}
 \caption{UML diagram of defined entities and their relationships}
@@
 
-The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to.
-
---Describe data from flow
+The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to.
+For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"}.
+Or channel \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{"leg\_3"}.
 
 \subsection{Processing Blocks}
+
+As stated in previous section, there are defined four stages in the processing flow, namely, preprocessing, feature analysis, pattern recognition and situation assessment.
+Within each of these stages there are different methods and techniques used to process the data and it is possible that those methods are suitable to perform fusion between homogeneous or heterogeneous data.
+
+Below are detailed different processing blocks implemented as part of the whole architecture proposal, classified by the stage of processing in which are located in the process flow.
+Also, it is shown the format of data input, data output and parameters needed for configuration and execution.
+
+\subsubsection{Preprocessing}
+\subsubsection{Feature Analysis}
+\subsubsection{Pattern Recognition}
+\subsubsection{Situation Assesment}
+\subsubsection{Tools and Utilities}

### 2018-03-02 ch3-arch_sys.tex
Added figures for processing blocks section

@@
 The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to.
-For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"}.
-Or channel \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{"leg\_3"}.
+For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.
 
@@
 \subsubsection{Preprocessing}
+\begin{description}
+\item[laser\_background\_remove]laser\_bg\_remove
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/laser_bg_remove.pdf}
+\caption{laser\_bg\_remove}
+\label{laser_bg_remove}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/polar2cart.pdf}
+\caption{polar\_to\_cartesian}
+\label{polar_to_cartesian}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/laser_cart_merge.pdf}
+\caption{laser\_cart\_merge}
+\label{laser_cart_merge}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/points_to_clusters.pdf}
+\caption{points\_to\_clusters}
+\label{points_to_clusters}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/points_to_grid.pdf}
+\caption{points\_to\_grid}
+\label{points_to_grid}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/grid_to_occupancy_level.pdf}
+\caption{grid\_to\_occupancy\_level}
+\label{grid_to_occupancy_level}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/clusters_to_occupancy_level.pdf}
+\caption{clusters\_to\_occupancy\_level}
+\label{clusters_to_occupancy_level}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/occupancy_level_merge.pdf}
+\caption{occupancy\_level\_merge}
+\label{occupancy_level_merge}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/occupancy_level2int_state.pdf}
+\caption{occupancy\_level\_to\_intersection\_state}
+\label{occupancy_level2int_state}
+\end{figure}
+
+\end{description}
+
+%{laser_background_remove}
 \subsubsection{Feature Analysis}

### 2018-05-31 ch3-arch_sys.tex
Added information structure section

@@
 The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from.
-Three main components of the architecture are defined: communication scheme, data model and  processing blocks.
+Four main components of the architecture are defined: communication scheme, data model, information structure and processing blocks.
 
@@
 The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to.
-For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.
+For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.
+
+\subsection{Information Structure}
+
+Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.
+
+\subsubsection{.imscfg file}
+
+For running, the systems requires first a .imscfg file which describes the scenario and the sensors configuration.
+This information is stored as a JSON object with the properties decribed in table \ref{imscfg_file}.
+
+\begin{table}[ht!]
+\footnotesize
+\centering
+\begin{tabular}{|c | c|}
+\hline
+\textbf{Property} & \textbf{Description} \\
+\hline
+name & Name of the configuration \\
+\hline
+map & Information of the scene, including map, coordinate system \\ 
+ & and region of interest. \\
+\hline
+cameras & List of camera sensors information \\
+\hline
+range\_sensors & List of range sensors information \\
+\hline
+legs & List of legs information \\
+\hline
+intersection & Information of area of the intersection \\
+\hline
+\end{tabular}
+\caption{Properties in .imscfg JSON file}
+\label{imscfg_file}
+\end{table}
+
+\subsubsection{data messages and configuration parameters}
+
+In addition to .imscfg file, there are different types of messages and parameters which have its own structure, for example used for sensors configuration or processed data.
+The table \ref{desc_map} gives a description of the types of information used.
+A more detailed documentation is given in appendix TODO.
+
+\begin{table}[ht!]
+\footnotesize
+\centering
+\begin{tabular}{|c | p{8cm}|}
+\hline
+\textbf{Name} & \textbf{Description} \\
+\hline
+laser\_pol\_msg & Contains a timestamp, an array of N angles and and array of N measurements \\
+\hline
+laser\_cart\_msg & Contains a timestamp, an array of N (x, y) coordinates \\
+\hline
+laser\_cfg & Contains position and orientation information, also has a background model for the laser sensor \\
+\hline
+occgrid\_msg & Contains a timestamp and an occupancy grid in the form of an MxN array \\
+\hline
+\end{tabular}
+\caption{Description of diferent types of messages and parameters used}
+\label{desc_map}
+\end{table}
 
@@
 Also, it is shown the format of data input, data output and parameters needed for configuration and execution.
+
+Additionaly, there are included some tools and generic blocks used for dataset reading, data visualization and interactive control.
 

### 2018-06-01 ch3-arch_sys.tex
updated laser_bg_remove figure
Added bg_model description

@@
 \hline
+occgrid\_cfg & Contains occupancy grid configuration for the scene \\
+\hline
 \end{tabular}
@@
 \item[laser\_background\_remove]laser\_bg\_remove
+
+This block takes as input a message of type laser\_pol\_msg, which contains raw readings from laser sensor.
+Also, it takes a laser\_cfg parameter which includes a background model for the laser sensor, generated from a set of scans and taking the maximum measurement in each angle of scanning, defined as follows:
+
+Let suppose we have N scans from the laser and $d_{\theta i}$ be the distance measure at angle $\theta$ in scan $i$.
+Thus, the background value for that angle $\theta$ is $bg_\theta = max( \{d_{\theta i} | 1 < i < N\})$ and the background model is $bg = \{bg_\theta | \theta \in \Theta\} $ where $\Theta$ is the set of angles of scanning, in this case from -90\degree to 90\degree with 0.5\degree step.
 \begin{figure}[ht!]

### 2018-06-01 ch3-arch_sys.tex
Added pol2cart description

@@
 \begin{description}
-\item[laser\_background\_remove]laser\_bg\_remove
+\item[laser\_background\_remove] \hfill
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.8]{fig/3/laser_bg_remove.pdf}
+\caption{laser\_bg\_remove}
+\label{laser_bg_remove}
+\end{figure}
 
@@
 Thus, the background value for that angle $\theta$ is $bg_\theta = max( \{d_{\theta i} | 1 < i < N\})$ and the background model is $bg = \{bg_\theta | \theta \in \Theta\} $ where $\Theta$ is the set of angles of scanning, in this case from -90\degree to 90\degree with 0.5\degree step.
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.7]{fig/3/laser_bg_remove.pdf}
-\caption{laser\_bg\_remove}
-\label{laser_bg_remove}
-\end{figure}
+
+\item[laser\_polar2cart] \hfill
 
@@
 \centering
-\includegraphics[scale=0.7]{fig/3/polar2cart.pdf}
+\includegraphics[scale=0.8]{fig/3/polar2cart.pdf}
 \caption{polar\_to\_cartesian}
@@
 \end{figure}
+
+This block takes as input a message of type laser\_pol\_msg for converting it into cartesian coordinates referenced to global system.
+For this reason, it also takes a laser\_cfg parameter to include laser position information in the conversion.
+Output message contains a set of x, y points obtained from the following equations:
+
+\begin{eqnarray*}
+O_x = I_\rho*\cos{\phi}+S_x \\
+O_y = I_\rho*\sin{\phi} + S_y \\
+\phi = I_\theta + S_\theta
+\end{eqnarray*}
+
+Where:
+
+$(S_x, S_y, S_\theta)$: Position and orientation of the laser \\
+$(I_\rho, I_\theta )$: Input message (distance and angle arrays) \\
+$(O_x, O_y )$: Output message (x and y arrays) \\
+
+\item[laser\_cart\_merge] \hfill
 

### 2018-06-05 ch4-results.tex
Added new ch4

\chapter[Deployment and Results]{Deployment and Results}

\section{Test Configuration}

\subsection{Case 1: Single Laser}
\subsection{Case 2: Multiple Lasers}
\subsection{Case 3: Multiple Lasers and camera}

### 2018-06-05 ch3-arch_sys.tex
Updated figure scale
Updated occupancy grid description and new figures added

@@
 
+\todo{Simulators description (?)}
+
 A more detailed analysis of traffic simulation models and simulation platforms could be found in \cite{AdamsBoxill2000, Barcelo2000, Kitamura2005, Lieberman1992}
-\subsubsection{Simulators Classification}
+
 \subsection{Intersection monitoring Datasets}
@@
 POSSi dataset\footnote{Available at http://www.poss.pku.edu.cn/download.html}
+
+\todo{Dataset description (?)}
+
 \subsubsection{KoPER Dataset }
@@
 \hline
+clustering\_msg & Contains a set of clusters, each of them with an ID and a set of points \\
+\hline
+clustering\_cfg & Contains configuration about clustering algorithm and parameters \\
+\hline
 \end{tabular}
@@
 \centering
-\includegraphics[scale=0.7]{fig/3/laser_cart_merge.pdf}
+\includegraphics[scale=0.8]{fig/3/laser_cart_merge.pdf}
 \caption{laser\_cart\_merge}
@@
 
+This block takes as input messages of type laser\_cart\_msg coming from different sensors and merges them into a single message, based on a sampling period $T$.
+
+\item[points\_to\_cluster] \hfill
+
 \begin{figure}[ht!]
 \centering
-\includegraphics[scale=0.7]{fig/3/points_to_clusters.pdf}
+\includegraphics[scale=0.8]{fig/3/points_to_clusters.pdf}
 \caption{points\_to\_clusters}
@@
 
+The input message for this block is a set of points corresponding to objects scanned by lasers.
+Clustering is performed over this input to identify the points belonging to the same object.
+The algorithm used in this implementation is DBSCAN, which stands for Density-Based Spatial Clustering of Applications with Noise.
+This algorithm does not need an estimated number of clusters as input, instead of this, it requires only two parameters: a minimum number of points per cluster, m, and a neighbourhood measure, $\epsilon$.
+A detailed description of the algorithm, can be found in \cite{Ester96}.
+
+As output, a message of type clustering\_msg, containing information like clusters ID and set of points belonging to each cluster, is delivered.
+
+\item[points\_to\_occgrid] \hfill
+
 \begin{figure}[ht!]
 \centering
-\includegraphics[scale=0.7]{fig/3/points_to_grid.pdf}
+\includegraphics[scale=0.8]{fig/3/points_to_grid.pdf}
 \caption{points\_to\_grid}
@@
 
+This block generates a occupancy grid based on cartesian data from laser.
+As parameters, this block receives a cell size for the grid, the laser configuration and the scene configuration.
+The grid size is of $N_C$ Columns and $N_R$ rows, obtained as follows:
+
+\begin{eqnarray*}
+X = x_{max}-x_{min} \\
+Y = y_{max}-y_{min} \\
+N_C = ceil(X/C)+1 \\
+N_R = ceil(Y/C)+1 \\
+\end{eqnarray*}
+
+Where $(x_{min}, y_{min})$ and $(x_{max}, y_{max})$ are the bottom-left and top-right coordinates of the region of interest in the scene, respectively.
+
+Each cell of the grid will store a value indicating a probability of that cell being occupied.
+Initially, all cells have a value of $0.5$.
+In order, to update the grid using data from laser, the points corresponding to laser position and measures, should be located in a cell of the grid, and then mark it as occupied.
+The following equations show how a point $P = (P_x, P_y)$ is tranformed to a cell $C_{ij}$, where $i$ is the column and $j$ is the row in the grid:
+
+\begin{eqnarray*}
+i = ceil((P_x - x_{min})/C - 0.5) \\
+j = N_R - ceil((P_y - y_{min})/C - 0.5) \\
+\end{eqnarray*}
+
+Then, the cells that form a straigh line between the cell of laser position and the cells of each laser measure, should be marked as empty.
+To get the list of these cells Bresenham's algorithm \todo{Check bresenham algorithm reference} is used.
+This algorithm is widely used in computer graphics due to it simplicity and because it uses integer arithmetics, making it computationally cheap.
+
+The input of this algorithm is a pair of coordinates, the endpoints of the line, and as result, the set of points that completes the line between, is returned.
+
+Now, the update procedure for the probability in each cell is described for the function $f$:
+
+\todo{update policy}
+
 \begin{figure}[ht!]
 \centering
-\includegraphics[scale=0.7]{fig/3/grid_to_occupancy_level.pdf}
+\includegraphics[scale=0.8]{fig/3/grid_to_occupancy_level.pdf}
 \caption{grid\_to\_occupancy\_level}
@@
 \centering
-\includegraphics[scale=0.7]{fig/3/clusters_to_occupancy_level.pdf}
+\includegraphics[scale=0.8]{fig/3/clusters_to_occupancy_level.pdf}
 \caption{clusters\_to\_occupancy\_level}

### 2018-06-05 ch4-results.tex
Added images to chapter 4

@@
-\chapter[Deployment and Results]{Deployment and Results}
+\chapter [Deployment and Results]{Deployment and Results}
 
-\section{Test Configuration}
+\section{Test Configurations}
+In order to test the proposed architecture, three different configurations have been selected.
+The first configuration is using just one laser sensor.
+The second configuration is based on multiple laser sensors, Finally, the third configurations uses multiple lasers along with a camera.
+
+Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from sensors, lasers and cameras, to produce an output of higher level.
+In this case, vehicle counting and intersection occupation level are the metrics used for evaluation.
+
+The following table lists all used blocks and assigns an ID for each one.
+Those IDs are used in the graph description in its own section.
+Also, bold nodes and connections indicate multiple instance of the same element.
+
+\begin{table}[ht!]
+\footnotesize
+\centering
+\begin{tabular}{|c | c| c|}
+\hline
+\textbf{Block ID} & \textbf{Name} \\
+\hline
+A & laser\_publisher \\
+\hline
+B & laser\_bg\_remover \\
+\hline
+C & laser\_pol2cart \\
+\hline
+D & laser\_cart\_merge \\
+\hline
+E & points2clusters \\
+\hline
+F & clusters\_leg\_counter \\
+\hline
+G & leg\_counter\_merge \\
+\hline
+H & clusters2occ\_level \\
+\hline
+I & occ\_level\_merge \\
+\hline
+J & laser\_pol2cart \\
+\hline
+K & points2occgrid \\
+\hline
+L & occgrid\_merge \\
+\hline
+M & occgrid\_leg\_counter \\
+\hline
+N & occgrid2occ\_level \\
+\hline
+O & camera\_publisher \\
+\hline
+P & camera\_bg\_remover \\
+\hline
+Q & camera\_object\_filter \\
+\hline
+R & camera\_object2occgrid \\
+\hline
+\end{tabular}
+\caption{Description of processing blocks used in test configurations}
+\label{desc_test_config}
+\end{table}
 
 \subsection{Case 1: Single Laser}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/4/test_configuration1.pdf}
+\caption{Single laser configuration}
+\label{tconf1}
+\end{figure}
+
+TODO
+
 \subsection{Case 2: Multiple Lasers}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/4/test_configuration2.pdf}
+\caption{Single laser configuration}
+\label{tconf2}
+\end{figure}
+
+TODO
+
 \subsection{Case 3: Multiple Lasers and camera}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
+\caption{Single laser configuration}
+\label{tconf3}
+\end{figure}
+
+TODO
+
+\subsection{Results and Comparison}
+
+TODO

### 2018-06-06 ch5-conclusions.tex
Updated document structure

%ch5-conclusions
\chapter {Conclusions}

\section{Summary}
\section{Limitations}
\section{Future Work}
\section{Contributions}
\section{Final Remarks}

### 2018-06-07 ch5-conclusions.tex
Added draft of chapter 5 - conclusions

@@
 
-\section{Summary}
-\section{Limitations}
+\section{General Conclusions}
+\section{Contributions}
+
+A scalable, modular system for traffic control monitoring at intersection. Both for experimentation and real deployment.
+
+Set of software repositories for application and for available datasets containing intersection data.
+
+Pair of articles submmited to events, one for architecture description and example implementation and another for application comparison.
+
 \section{Future Work}
-\section{Contributions}
-\section{Final Remarks}
+
+Generation of our own dataset.
+
+Optimization of communication scheme.
+
+Integration of new types of sensors
+
+Creation of a more friendly user interface.

### 2018-06-12 title1.tex
Replaced \maketitle with titlepages

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}
        \Huge

        Multisensor Architecture for an Intersection Management System

        \vspace{4.5cm}
        \LARGE
        Gustavo Adolfo Velasco-Hernandez

        \vfill
        \large
        \vspace{0.8cm}

        %\includegraphics[width=0.4\textwidth]{university}

        School of Electrical and Electronics Engineering\\
        Universidad del Valle\\
        Colombia\\
        \today

    \end{center}
\end{titlepage}

### 2018-06-12 ch3-arch_sys.tex
Added epigraphe packages and section titles to chapter 3
Fixed list of processing blocks and images

@@
 \chaptermark {System Description}
+
+\epigraph{"Perfect is enemy of good"}{Voltaire}
 
@@
 
-\subsection{Processing Blocks}
+\subsection{Processing Blocks} \label{proc_blocks}
 
@@
 \centering
-\includegraphics[scale=0.8]{fig/3/laser_bg_remove.pdf}
+\includegraphics[scale=1]{fig/3/laser_bg_remove.pdf}
 \caption{laser\_bg\_remove}
@@
 \centering
-\includegraphics[scale=0.8]{fig/3/polar2cart.pdf}
+\includegraphics[scale=1]{fig/3/polar2cart.pdf}
 \caption{polar\_to\_cartesian}
@@
 \centering
-\includegraphics[scale=0.8]{fig/3/laser_cart_merge.pdf}
+\includegraphics[scale=1]{fig/3/laser_cart_merge.pdf}
 \caption{laser\_cart\_merge}
@@
 
+\item[camera\_background\_remove] \hfill
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/camera_bg_remove.pdf}
+\caption{camera\_background\_remove block}
+\label{cam_bg_remove}
+\end{figure}
+
+\end{description}
+
+\subsubsection{Feature Analysis}
+\begin{description}
 \item[points\_to\_cluster] \hfill
@@
 \centering
-\includegraphics[scale=0.8]{fig/3/points_to_clusters.pdf}
+\includegraphics[scale=1]{fig/3/points_to_clusters.pdf}
 \caption{points\_to\_clusters}
@@
 \centering
-\includegraphics[scale=0.8]{fig/3/points_to_grid.pdf}
+\includegraphics[scale=1]{fig/3/points_to_grid.pdf}
 \caption{points\_to\_grid}
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.8]{fig/3/grid_to_occupancy_level.pdf}
-\caption{grid\_to\_occupancy\_level}
-\label{grid_to_occupancy_level}
-\end{figure}
+\item[occgrid\_merge] \hfill
 
@@
 \centering
-\includegraphics[scale=0.8]{fig/3/clusters_to_occupancy_level.pdf}
+\includegraphics[scale=1]{fig/3/occgrid_merge.pdf}
+\caption{occgrid\_merge}
+\label{occgrid_merge}
+\end{figure}
+
+\item[camera\_blobs] \hfill
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/camera_blobs.pdf}
+\caption{camera\_blobs}
+\label{camera_blobs}
+\end{figure}
+
+\item[camera\_blobs2occgrid] \hfill
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/camera_blobs2occgrid.pdf}
+\caption{camera\_blobs2occgrid}
+\label{camera_blobs2occgrid}
+\end{figure}
+
+\end{description}
+
+\subsubsection{Pattern Recognition}
+\begin{description}
+
+\item[clusters\_vehicle\_counter] \hfill
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/clusters_veh_counter.pdf}
+\caption{clusters\_vehicle\_counter}
+\label{clusters_vehicle_counter}
+\end{figure}
+
+\item[clusters\_to\_occupancy\_level] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
 \caption{clusters\_to\_occupancy\_level}
@@
 
+\item[occgrid\_vehicle\_counter] \hfill
+
 \begin{figure}[ht!]
 \centering
-\includegraphics[scale=0.7]{fig/3/occupancy_level_merge.pdf}
+\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
+\caption{occgrid\_vehicle\_counter}
+\label{occgrid_vehicle_counter}
+\end{figure}
+
+\item[occgrid\_to\_occupancy\_level] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
+\caption{occgrid\_to\_occupancy\_level}
+\label{occgrid_to_occupancy_level}
+\end{figure}
+
+\end{description}
+
+\subsubsection{Situation Assesment}
+\begin{description}
+
+\item[vehicle\_counter\_merge] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
+\caption{vehicle\_counter\_merge}
+\label{vehicle_counter_merge}
+\end{figure}
+
+\item[occupancy\_level\_merge] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
 \caption{occupancy\_level\_merge}
@@
 
+\end{description}
+
+\subsubsection{Tools and Utilities}
+\begin{description}
+
+\item[laser\_publisher] \hfill
 \begin{figure}[ht!]
 \centering
-\includegraphics[scale=0.7]{fig/3/occupancy_level2int_state.pdf}
-\caption{occupancy\_level\_to\_intersection\_state}
-\label{occupancy_level2int_state}
+\includegraphics[scale=1]{fig/3/laser_publisher.pdf}
+\caption{laser\_publisher}
+\label{laser_publisher}
+\end{figure}
+
+\item[camera\_publisher] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
+\caption{camera\_publisher}
+\label{camera_publisher}
+\end{figure}
+
+\item[dataset\_control] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/dataset_ctrl.pdf}
+\caption{dataset\_control}
+\label{dataset_control}
+\end{figure}
+
+\item[data\_viewer] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/data_viewer.pdf}
+\caption{data\_viewer}
+\label{data_viewer}
 \end{figure}
@@
 
-%{laser_background_remove}
-\subsubsection{Feature Analysis}
-\subsubsection{Pattern Recognition}
-\subsubsection{Situation Assesment}
-\subsubsection{Tools and Utilities}
+\subsection{Conclusions}

### 2018-06-13 ch2-mdf_ims.tex
Added label to section 2.3
Some corrections and chapter labels reviewed
Fixed figure size
Some fixes in chapter 2

--- 2015-06-10 ch2-mdf_ims.tex
@@
 
-\chapter [Sensor Fusion and IMS]{Multisensor Data Fusion and Intersection Management Systems}
+\chapter [Multisensor Data Fusion and Intersection Management Systems]{Multisensor Data Fusion and Intersection Management Systems}
+\chaptermark{Sensor Fusion and IMS}
 
@@
 \centering
-\includegraphics[scale=0.25]{fig/2/fusionClasses.png}
+\includegraphics[scale=0.4]{fig/2/fusionClasses.png}
 \caption{Five classes of Multisensor Fusion.}
@@
 
-\section{Sensor Fusion in Intersection Management}
+\section{Sensor Fusion in Intersection Management} \label{s23}
 
-Cameras are a wide used sensor for surveillance and monitoring applications because they provide a lot of information for scene understanding, but the transmitting and processing of such information requires high computational resources.
+Cameras are a wide used sensors for surveillance and monitoring applications because they provide a lot of information for scene understanding, but the transmitting and processing of such information requires high computational resources.
 For this reason low resolution cameras and low frame rates configurations are commonly deployed.
@@
 Using both cameras and range sensors for intersection management systems makes it possible to take advantages of each type of sensor, and obtain a better representation of the environment.
+
+Although many works based on cameras are found, there are two main developments that make use of range sensors along cameras to implement an IMS.
+The first one, developed by POSS research group at Peking University\footnote{http://www.poss.pku.edu.cn/index.html}, is the POSSi project, for which main objective is monitoring a dynamic environment through fusion of laser and video.
+In this project, a set of laser scanners are deployed on corners of an intersection and a camera is installed over a pedestrian bridge.
+They perform a fusion over laser data and after detection and recognition of vehicles and pedstrians, this info is backprojected on video stream.
+
+The second relevant project, Ko-PER project\footnote{http://ko-fas.de/english/ko-per---cooperative-perception.html}, was developed by the Institute of Measurement, Control and Microtechnology at Ulm University under Ko-FAS research initiative.
+Ko-PER project aims to capture a complete picture of the local traffic environment.
+In order to do so, a full deployment of infrastructure was made, using 14 laserscanners, 10 cameras, a GPS and a V2I communication unit.
+Also, they perform a low-level fusion over same type sensor first, and then they merge outputs of each subsystem for improve detection and analysis results.
+
+In the proposed work, there is not a deployment of sensors in an intersection scenario, but datasets will be used instead for validations purposes.
+Also, one of the objectives is to explore and propose a modular fusion architecture/framework for IMS based on cameras and laser sensors.
+In table \ref{summary_FusIMS} a summary of aforementioned developments is presented, including proposed work.
+
+\begin{table}[!t]
+\begin{tabular}{|p{0.13\linewidth}|c|p{0.125\linewidth}|p{0.15\linewidth}|p{0.16\linewidth}|c|}
+\hline
+
+\textbf{Reference} & \textbf{Project} & \textbf{Sensors} & \textbf{Target} & \textbf{Fusion} & \textbf{Framework} \\
+\hline
+
+\cite{Zhao2006} & POSSi & Laser & Vehicles, pedestrians & - & No \\
+\hline
+
+\cite{Song2008} & POSSi & Lasers & Pedestrians & Low-Level & No \\
+\hline
+
+\cite{Zhao2008} & POSSi & Lasers & Vehicles, pedestrians & Low-Level & No \\
+\hline
+
+\cite{Zhao2009} & POSSi & Lasers, Camera & Vehicles, pedestrians & Low-Level, High-Level & No \\
+\hline
+
+\cite{Zhao2012} & POSSi & Lasers & Vehicles, pedestrians & Low-Level & No \\
+\hline
+
+\cite{Goldhammer2012} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
+\hline
+
+\cite{Meissner2012} & Ko-PER & Lasers & Pedestrians & Low-Level & No \\
+\hline
+
+\cite{Meissner2013} & Ko-PER & Lasers & Vehicles, pedestrians & Low-Level & No \\
+\hline
+
+\cite{Meissner2013a, Meissner2013b} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
+\hline
+
+\cite{Strigel2013} & Ko-PER & Cameras & Vehicles & Low-Level & No \\
+\hline
+
+\cite{Meissner2014} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
+\hline
+
+%\cite{} &  &  &  &  &  \\
+%\hline
+
+\textbf{Proposed work} & - & \textbf{Lasers, Cameras} & \textbf{Vehicles} & \textbf{Low-Level, Mid-Level, High-Level} & \textbf{Yes} \\
+\hline
+
+\end{tabular}
+\caption{Summary of recent developments involving sensor fusion for Intersection Management Systems}
+\label{summary_FusIMS}
+\end{table}
 

### 2018-06-16 ch1-introduction.tex
Updated document structure
Introduction chapter updated

@@
 % Introduction
-\chapter [Introduction]{Introduction}
+\chapter*{Introduction}
+\addcontentsline{toc}{chapter}{Introduction}%
 \chaptermark{Introduction}
 
-\section{Goals}
+Traditionally, transport systems vision has been constrainted to the set of elements belonging to infrastructure and the vehicles using it.
+As population increases and cities growth, the number of vehicles going through world roads also increases, but the growth rate of road network is lower.
+This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and the costs of eficient and long-lasting solutions are high.
 
-The main goal for this proposal is to conceive a multisensor architecture for an intersection management system and deploy it in a simulated scenario.
+One of the critical places where is imperative to improve safety and efficiency are vehicular intersections, because at these points many vehicles with different directions and speeds meet each other, increasing probability of incidents.
+Almost 40 percent of traffic accidents reported in US in 2008, were intersection related \cite{Choi2010}.
+In Colombia, at 2011 most of accidents in main cities were at intersections \cite{CorporacionFondodePrevencionVial2010}.
+
+In order to address different issues presented at intersections, several types of systems and applications have been proposed for different purposes like intersection management, vehicle counting, events warning, etc.
+These applications relies on different type of monitoring mechanisms, going from human supervision to automated sensors, but, because a high volume of data is generated in an intersection, it is not enough to have just one source of information.
+
+For this reason, various sensors have been used for intersection monitoring, like magnetic sensors, laser-scanners and cameras, each of them providing different types of information about the scene.
+This information needs to be merged into a single model that represents the intersection state.
+The reliability of this model depends on the quality of the processing and on the fusion scheme selected for the data.
+The more reliable the model is, the more precise and efficient management over the intersection will be.
+
+Based on this need of reliabilty in the scene model, the main goal set for this work is to conceive a multisensor architecture for an intersection management system and deploy it in a simulated scenario.
 In order to achieve this goal, these objectives were set:
@@
 \end{itemize}
+
+The following chapters of this report are structured as follows:
+
+Chapter 1 contains a comprehensive review on sensor fusion in intersection management systems, divided in three sections, first, sensor fusion approaches and model are described.
+Second, intersection management systems definition is presented along with a proposed taxonomy of those systems.
+Also a comprehensive list of developments is presented.
+Third, a review on IMS deployments that include a component of sensor fusion is described.
+
+Chapter 2 describes the proposal, starting on explaining what kind of processing is required and how sensor fusion could be performed in an intersection management system.
+Then, two validation approaches for an IMS are considered, simulators and datasets.
+Also, four components for the architecture proposal are detailed, i.e communication scheme, data model, information structure and processing blocks.
+
+Chapter 3 presents the result of three example implementations using the architecture: Single-laser case, multiple laser case and multiple laser and camera case.
+These test cases are evaluated and compared, both in application performance, using vehicle count as evaluation metric, and in computational resources usage.
+
+Chapter 4 summarizes the conclusions of the development of the whole work, remarking on contributions made like software and applications generated, academic products, and future developments and improvements for the system, including application performance, platforms upgrade, UX/UI improvements, scalability and integration with IOT and Smart Cities solutions.

### 2018-06-16 ch2-mdf_ims.tex
Added todo notes and some format fixes in chapter 2

@@
 
+\todo{Create custom figure}
+
 The first stage, referred as level-0 is the source preprocessing in which raw data is handled to concentrate the more pertinent data for the current situation.
@@
 
+\todo{Increase font size of this figure}
+
 Also, they made a clear distinction between multisensor fusion and multisensor integration, being the former the process in which information provided by a set of sensors is combined in any of the three levels aforementioned, and the latter is how sensor fusion could be integrated in a full system in order to assist in a particular task.
@@
 \centering
-\includegraphics[scale=0.4]{fig/2/MFIArch.png}
+\includegraphics[scale=0.5]{fig/2/MFIArch.png}
 \caption{Multisensor Fusion Integration architecture (from \cite{Luo2011}).}
@@
 \hline
-\parbox{2.5cm}{
+\parbox{2.4cm}{
 	Recursive:
@@
  & 
- \parbox{2.5cm}{	 
+ \parbox{2.4cm}{	 
  	Covariance-based:
@@
 &
-\parbox{3cm}{	 
+\parbox{2.9cm}{	 
 	\begin{itemize}[leftmargin=.07in, noitemsep]
@@
 \begin{table}[!t]
-\begin{tabular}{|p{0.13\linewidth}|c|p{0.125\linewidth}|p{0.15\linewidth}|p{0.16\linewidth}|c|}
+\begin{tabular}{|c|p{0.125\linewidth}|p{0.15\linewidth}|p{0.16\linewidth}|c|}
 \hline
 
-\textbf{Reference} & \textbf{Project} & \textbf{Sensors} & \textbf{Target} & \textbf{Fusion} & \textbf{Framework} \\
+\textbf{Project} & \textbf{Sensors} & \textbf{Target} & \textbf{Fusion} & \textbf{Framework} \\
 \hline
 
-\cite{Zhao2006} & POSSi & Laser & Vehicles, pedestrians & - & No \\
+POSSi \cite{Zhao2006}& Laser & Vehicles, pedestrians & - & No \\
 \hline
 
-\cite{Song2008} & POSSi & Lasers & Pedestrians & Low-Level & No \\
+POSSi \cite{Song2008}& Lasers & Pedestrians & Low-Level & No \\
 \hline
 
-\cite{Zhao2008} & POSSi & Lasers & Vehicles, pedestrians & Low-Level & No \\
+POSSi \cite{Zhao2008}& Lasers & Vehicles, pedestrians & Low-Level & No \\
 \hline
 
-\cite{Zhao2009} & POSSi & Lasers, Camera & Vehicles, pedestrians & Low-Level, High-Level & No \\
+POSSi \cite{Zhao2009}& Lasers, Camera & Vehicles, pedestrians & Low-Level, High-Level & No \\
 \hline
 
-\cite{Zhao2012} & POSSi & Lasers & Vehicles, pedestrians & Low-Level & No \\
+POSSi \cite{Zhao2012}& Lasers & Vehicles, pedestrians & Low-Level & No \\
 \hline
 
-\cite{Goldhammer2012} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
+Ko-PER \cite{Goldhammer2012} & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
 \hline
 
-\cite{Meissner2012} & Ko-PER & Lasers & Pedestrians & Low-Level & No \\
+Ko-PER \cite{Meissner2012} & Lasers & Pedestrians & Low-Level & No \\
 \hline
 
-\cite{Meissner2013} & Ko-PER & Lasers & Vehicles, pedestrians & Low-Level & No \\
+Ko-PER \cite{Meissner2013} & Lasers & Vehicles, pedestrians & Low-Level & No \\
 \hline
 
-\cite{Meissner2013a, Meissner2013b} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
+Ko-PER \cite{Meissner2013a, Meissner2013b} & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
 \hline
 
-\cite{Strigel2013} & Ko-PER & Cameras & Vehicles & Low-Level & No \\
+Ko-PER \cite{Strigel2013}& Cameras & Vehicles & Low-Level & No \\
 \hline
 
-\cite{Meissner2014} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
+Ko-PER \cite{Meissner2014}& Lasers, Cameras & Vehicles, pedestrians & Low-Level, Mid-Level & No \\
 \hline
@@
 
-\textbf{Proposed work} & - & \textbf{Lasers, Cameras} & \textbf{Vehicles} & \textbf{Low-Level, Mid-Level, High-Level} & \textbf{Yes} \\
+\textbf{Proposed work} & \textbf{Lasers, Cameras} & \textbf{Vehicles} & \textbf{Low-Level, Mid-Level, High-Level} & \textbf{Yes} \\
 \hline

### 2018-06-18 ch5-conclusions.tex
Almost finished conclusions chapter

--- 2018-06-06 ch5-conclusions.tex
@@
 
-\section{Summary}
-\section{Limitations}
+\section{General Conclusions}
+
+The inclusion of information and communication technologies in transportation systems have been rapidly increasing during the last years, making it possible to test and deploy novel solutions to address issues like safety, congestion, rules violation and many other concerns that affect the quality of transportation.
+
+Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.
+
+When deploying a system for intersection monitoring, it is desirable to have variety of sensors, because this allows to have more complementary information in order to generate an accurate representation of the interection.
+But more important than the quantity of sensors, is how the data for all installed sensors will be merged.
+
+For this reason, data fusion techniques are in constant development.
+Algorithms that were not feasible to use some years ago, are now being deployed thanks to improvements on computational capabilities, storage resources and communications systems.
+
+Before deploy an interesection management system in a real scenario, validation is a must.
+Datasets are the best option for doing it, because simulators are still in an early stage.
+The most suitable simulators, although not conceived for this purpose, are the ones used for autonomous driving platforms.
+These simulators could allow to include complex sensors like lidars and cameras on infrastructure, and include vehicles with autonomous behaviour in the scenario.
+
+\section{Contributions}
+
+The main contribution derived from the execution of this project is a scalable, modular system for traffic monitoring at an intersection.
+This system was concieved for use both in experimentation cases and real deployment.
+The software implementation of the system uses at its core a set of tools and libraries ready for industrial and commercial cases.
+
+Another contribution is a comprehensive review on intersection management systems, including a classification scheme based on its components and its main application.
+This could serve to readers as an introductory resource on how has been the evolutions of those systems and what is the future of them.
+
+In addition to this, a set of software repositories are available, one for the application and another one summarizing available datasets containing intersection data.
+The purpose of this is to let other people review, test and give their opinion about the system.
+This feedback would be used for new features and improvements.
+
+On the other side, a couple of articles are being reviewed previous to be submmited to journal.
+One article is for architecture description and example implementation and another for application comparison.
+
 \section{Future Work}
-\section{Contributions}
-\section{Final Remarks}
+
+Aiming to continue the work started by this project, there are several opportunities of improvement that have been identified. The more relevant and feasible in the short-term are the following:
+
+Generation of our own dataset.
+Taking into account that PSI reserch group have a laser-scanner, it would be great to generate a dataset for local intersections.
+From a low-traffic intersection in the campus to a high-traffic intersection in the surroundings.
+Allowing to test the system under different conditions and do not depend on 3rd party data.
+
+Software and Platforms Improvements.
+As described, the system comprises different elements, and each of them could be improved.
+For example, evaluate alternatives in communication with low-latency.
+Optimize message exchange format in order to reduce bandwith usage.
+Software code optimization to reduce CPU comsumption.
+Improve user experience through the development of a more friendly interface, taking into account desktop, web and /or mobile options.
+
+New types of sensors.
+Although the system was tested with lasers and a camera, scalability is one of the main features of it.
+This allows to include new sensors, and develop the needed processing blocks to integrate their information into the dataflow of the system and improve its quality and its efficiency.
+
+Integration with other technologies and new trends.
+At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefullness and relevance of these projects in real deployements.
+It is important new versions of the system, will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.

### 2018-06-18 ch4-results.tex
Updated document structure
Names and captions fixed
brief edit in results chapter

@@
 \chapter [Deployment and Results]{Deployment and Results}
+
+\section{Experimental Setup}
+
+The selected dataset testing the system is POSSi's \ref{possi_ds}.
+It contains 6 laser-scanners raw readings and a video from a camera located over the intersection.
+The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears.
+This groundtruth data was generated by human inspection.
 
@@
 The first configuration is using just one laser sensor.
-The second configuration is based on multiple laser sensors, Finally, the third configurations uses multiple lasers along with a camera.
+The second configuration is based on multiple laser sensors, Finally, the third configuration uses multiple lasers along with a camera.
 
 Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from sensors, lasers and cameras, to produce an output of higher level.
-In this case, vehicle counting and intersection occupation level are the metrics used for evaluation.
+In this case, vehicle counting is the metric used for evaluation.
 
@@
 \hline
-F & clusters\_leg\_counter \\
+F & clusters\_veh\_counter \\
 \hline
-G & leg\_counter\_merge \\
+G & veh\_counter\_merge \\
 \hline
@@
 \hline
-Q & camera\_object\_filter \\
+Q & camera\_blobs \\
 \hline
-R & camera\_object2occgrid \\
+R & camera\_blobs2occgrid \\
 \hline
@@
 \includegraphics[scale=0.7]{fig/4/test_configuration2.pdf}
-\caption{Single laser configuration}
+\caption{Multiple lasers configuration}
 \label{tconf2}
@@
 \includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
-\caption{Single laser configuration}
+\caption{Multiple lasers and camera configuration}
 \label{tconf3}

### 2018-06-18 ch3-arch_sys.tex
Added new figures. Added label for possi dataset. Added general architecture block diagram.

@@
 
-\subsubsection{POSSi Dataset }
+\subsubsection{POSSi Dataset } \label{possi_ds}
 
@@
 
-The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output.
+The proposal presented in this work is based on MFI model processing entities in the sense that a processing block could take one or more inputs related between them and generate an output of the same type or a higher level output, that means that some blocks perform fusion while others just do some processing on incoming data.
 The communication or data exchange approach is based on JDL model, in which data is available over a "bus", where the processing blocks can write to or read from.
-Four main components of the architecture are defined: communication scheme, data model, information structure and processing blocks.
+And an information model is defined for abstract the elements of the scene, set a format for message exchange and define global and local configuration parameters.
+A general block diagram is shown in figure \ref{proposal_blocks}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.7]{fig/3/proposal_blocks.pdf}
+\caption{General overview of proposed architecture and its components. Red for the communication scheme, green for data model and blue for processing blocks}
+\label{proposal_blocks}
+\end{figure}
 

### 2018-06-18 ch1-introduction.tex
Minor modifications. Apendix removed

@@
 
-Traditionally, transport systems vision has been constrainted to the set of elements belonging to infrastructure and the vehicles using it.
+Traditionally, the vision of transport systems has been constrainted to the set of elements belonging to infrastructure and the vehicles using it.
 As population increases and cities growth, the number of vehicles going through world roads also increases, but the growth rate of road network is lower.
-This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and the costs of eficient and long-lasting solutions are high.
+This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and develop of efficient and long-lasting solutions carries high costs.
 

### 2018-06-18 ch3-arch_sys.tex
General drafting fixes.

@@
 
-\todo{Simulators description (?)}
+%\todo{Simulators description (?)}
 
@@
 
-As mentioned in section \ref{s23}, POSS-i and Ko-PER projects are leading the development of multisensor Intersection Management Systems.
+As mentioned in section \ref{s23}, POSS-i \footnote{Available at http://www.poss.pku.edu.cn/download.html} and Ko-PER \footnote{Available at http://www.uni-ulm.de/in/mrm/forschung/datensaetze.html} projects are leading the development of multisensor Intersection Management Systems.
 One of the contributions of these projects is the creation of datasets of such systems.
 They provide camera and laser information of a monitored intersection in Peking, China and Aschaffenburg, Germany, respectively.
-Next, a description of these two datasets will be given.
 
-\subsubsection{POSSi Dataset } \label{possi_ds}
-
-POSSi dataset\footnote{Available at http://www.poss.pku.edu.cn/download.html}
-
-\todo{Dataset description (?)}
-
-\subsubsection{KoPER Dataset }
-
-Ko-PER dataset\footnote{Available at http://www.uni-ulm.de/in/mrm/forschung/datensaetze.html}
-
-The full description of this dataset is presented in \cite{Strigel2014}.
+%Next, a description of these two datasets will be given.
+%
+%\subsubsection{POSSi Dataset } \label{possi_ds}
+%
+%POSSi dataset\footnote{Available at http://www.poss.pku.edu.cn/download.html}
+%
+%\todo{Dataset description (?)}
+%
+%\subsubsection{KoPER Dataset }
+%
+%Ko-PER dataset\footnote{Available at http://www.uni-ulm.de/in/mrm/forschung/datensaetze.html}
+%
+%The full description of this dataset is presented in \cite{Strigel2014}.
 

### 2018-06-18 ch5-conclusions.tex
General drafting fixes.

@@
 
-When deploying a system for intersection monitoring, it is desirable to have variety of sensors, because this allows to have more complementary information in order to generate an accurate representation of the interection.
-But more important than the quantity of sensors, is how the data for all installed sensors will be merged.
+When deploying a system for intersection monitoring, it is desirable to have variety of sensors, because this allows to have more complementary information in order to generate an accurate representation of the intersection.
+But more important than the quantity of sensors, is how the data for all installed sensors will be processed and unified.
 
@@
 
-Before deploy an interesection management system in a real scenario, validation is a must.
+Before deploying an interesection management system in a real scenario, validation is a must.
 Datasets are the best option for doing it, because simulators are still in an early stage.
@@
 The main contribution derived from the execution of this project is a scalable, modular system for traffic monitoring at an intersection.
-This system was concieved for use both in experimentation cases and real deployment.
+This system was concieved for usage both in experimentation cases and real deployments.
 The software implementation of the system uses at its core a set of tools and libraries ready for industrial and commercial cases.
@@
 In addition to this, a set of software repositories are available, one for the application and another one summarizing available datasets containing intersection data.
-The purpose of this is to let other people review, test and give their opinion about the system.
+The purpose of this is to let community review, test and give their opinion about the system.
 This feedback would be used for new features and improvements.
@@
 Generation of our own dataset.
-Taking into account that PSI reserch group have a laser-scanner, it would be great to generate a dataset for local intersections.
-From a low-traffic intersection in the campus to a high-traffic intersection in the surroundings.
-Allowing to test the system under different conditions and do not depend on 3rd party data.
+Taking into account that PSI research group owns a laser-scanner, it would be great to generate a dataset for local intersections.
+It could be from a low-traffic intersection in the campus or from a high-traffic intersection in the surroundings.
+This would allow to test the system under different conditions and do not depend on 3rd party data.
 
@@
 Integration with other technologies and new trends.
-At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefullness and relevance of these projects in real deployements.
-It is important new versions of the system, will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.
+At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefulness and relevance of these projects in real deployements.
+It is important that new versions of the system will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.

### 2018-06-21 ch3-arch_sys.tex
Final draft

@@
 
-\subsection{Intersection monitoring Datasets}
+\subsection{Intersection monitoring Datasets} \label{possi_ds}
 
@@
 
-\item[camera\_background\_remove] \hfill
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/camera_bg_remove.pdf}
-\caption{camera\_background\_remove block}
-\label{cam_bg_remove}
-\end{figure}
+%\item[camera\_background\_remove] \hfill
+%
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{fig/3/camera_bg_remove.pdf}
+%\caption{camera\_background\_remove block}
+%\label{cam_bg_remove}
+%\end{figure}
 
@@
 
-This block generates a occupancy grid based on cartesian data from laser.
-As parameters, this block receives a cell size for the grid, the laser configuration and the scene configuration.
+This block generates a occupancy grid based on cartesian data from laser sensors.
+The cartesian data received from sensors is merged in a timeslot basis, filling a buffer for each sensor and processing available data using a defined period $T_{om}$.
+As parameters, this block receives a cell size for the grid, the laser sensors configuration and the scene configuration.
 The grid size is of $N_C$ Columns and $N_R$ rows, obtained as follows:
@@
 Then, the cells that form a straigh line between the cell of laser position and the cells of each laser measure, should be marked as empty.
-To get the list of these cells Bresenham's algorithm \todo{Check bresenham algorithm reference} is used.
+To get the list of these cells Bresenham's algorithm is used.
 This algorithm is widely used in computer graphics due to it simplicity and because it uses integer arithmetics, making it computationally cheap.
+The input of this algorithm is a pair of coordinates, the endpoints of the line, and as result, the set of points that completes the line between, is returned.
+%\todo{Check bresenham algorithm reference}
 
-The input of this algorithm is a pair of coordinates, the endpoints of the line, and as result, the set of points that completes the line between, is returned.
-
-Now, the update procedure for the probability in each cell is described for the function $f$:
-
-\todo{update policy}
-
-\item[occgrid\_merge] \hfill
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/occgrid_merge.pdf}
-\caption{occgrid\_merge}
-\label{occgrid_merge}
-\end{figure}
+As the output, this block generates an occupancy grid of the scene, which is published at a rate defined by the previous period $T_{om}$.
+%\todo{update policy}
 
@@
 
+The purpose of this block is to detect the vehicles from the streaming of video from a camera.
+To accomplish this task, the YOLOv3 detection system \cite{yolov3} was wraped into a block.
+The algorithm used by this detector, applies a single neural network to the full image.
+This network divides the image into regions and predicts bounding boxes and probabilities for each region.
+These bounding boxes are weighted by the predicted probabilities.
+The output of this block, are the bounding boxes with high probabilty of being a vehicle.
+
 \item[camera\_blobs2occgrid] \hfill
@@
 \end{figure}
+
+This block receives bounding boxes corresponding to vehicles and transform them from image coordinate system to the global reference system, Then, it maps the area covered by the boxes into an occupancuy grid in order to mark those cells as occupied in the same fashion as described for the block "points\_to\_occgrid" \ref{points_to_grid}.
 
@@
 
-\item[clusters\_to\_occupancy\_level] \hfill
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
-\caption{clusters\_to\_occupancy\_level}
-\label{clusters_to_occupancy_level}
-\end{figure}
+%\item[clusters\_to\_occupancy\_level] \hfill
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
+%\caption{clusters\_to\_occupancy\_level}
+%\label{clusters_to_occupancy_level}
+%\end{figure}
 
@@
 
-\item[occgrid\_to\_occupancy\_level] \hfill
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
-\caption{occgrid\_to\_occupancy\_level}
-\label{occgrid_to_occupancy_level}
-\end{figure}
+%\item[occgrid\_to\_occupancy\_level] \hfill
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
+%\caption{occgrid\_to\_occupancy\_level}
+%\label{occgrid_to_occupancy_level}
+%\end{figure}
 
@@
 \end{figure}
-
-\item[occupancy\_level\_merge] \hfill
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
-\caption{occupancy\_level\_merge}
-\label{occupancy_level_merge}
-\end{figure}
+%
+%\item[occupancy\_level\_merge] \hfill
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
+%\caption{occupancy\_level\_merge}
+%\label{occupancy_level_merge}
+%\end{figure}
 
@@
 \includegraphics[scale=1]{fig/3/laser_publisher.pdf}
-\caption{laser\_publisher}
-\label{laser_publisher}
+\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
+\caption{laser\_publisher and camera\_publisher}
+\label{sensors_publishers}
 \end{figure}
 
-\item[camera\_publisher] \hfill
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
-\caption{camera\_publisher}
-\label{camera_publisher}
-\end{figure}
+These blocks are intended to read dataset files containing the information from the sensors and publish this data with the appropriate format and preserving the original rate of the sensors, if needed.
 
-\item[dataset\_control] \hfill
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/dataset_ctrl.pdf}
-\caption{dataset\_control}
-\label{dataset_control}
-\end{figure}
+%\item[camera\_publisher] \hfill
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{fig/3/camera_publisher.pdf}
+%\caption{camera\_publisher}
+%\label{camera_publisher}
+%\end{figure}
+
+%\item[dataset\_control] \hfill
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{fig/3/dataset_ctrl.pdf}
+%\caption{dataset\_control}
+%\label{dataset_control}
+%\end{figure}
 
@@
 
+The objective of this block is to allow the visualisation of the data in any of the processing stages.
+It has the option to display and XY coordinate system, an occupancy grid or a map of the intersection overlaped with detections of metrics.
+
 \end{description}

### 2018-06-21 ch4-results.tex
Minor modifications. Apendix removed
Final draft

@@
 
-The selected dataset testing the system is POSSi's \ref{possi_ds}.
+The selected dataset for testing the system is the one from POSSi project (section \ref{possi_ds}).
 It contains 6 laser-scanners raw readings and a video from a camera located over the intersection.
 The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears.
-This groundtruth data was generated by human inspection.
+This groundtruth data was generated manually.
 
 \section{Test Configurations}
-In order to test the proposed architecture, three different configurations have been selected.
-The first configuration is using just one laser sensor.
-The second configuration is based on multiple laser sensors, Finally, the third configuration uses multiple lasers along with a camera.
+In order to test the proposed architecture, two different configurations have been selected.
+The first configuration is using just the camera information.
+The second configuration is based on multiple laser sensors along with the camera.
 
-Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from sensors, lasers and cameras, to produce an output of higher level.
+Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level.
 In this case, vehicle counting is the metric used for evaluation.
@@
 
-\subsection{Case 1: Single Laser}
+\subsection{Case 1: Single Camera}
 
@@
 
-\subsection{Case 3: Multiple Lasers and camera}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
-\caption{Multiple lasers and camera configuration}
-\label{tconf3}
-\end{figure}
+%\subsection{Case 3: Multiple Lasers and camera}
+%
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=0.7]{fig/4/test_configuration3.pdf}
+%\caption{Multiple lasers and camera configuration}
+%\label{tconf3}
+%\end{figure}
 

### 2018-06-21 ch5-conclusions.tex
Final draft

@@
 
-Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.
+Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, it is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.
 
@@
 Another contribution is a comprehensive review on intersection management systems, including a classification scheme based on its components and its main application.
-This could serve to readers as an introductory resource on how has been the evolutions of those systems and what is the future of them.
+This could serve to readers as an introductory resource on how such systems have been evolving and what is the future of them.
 
@@
 
-On the other side, a couple of articles are being reviewed previous to be submmited to journal.
+On the other side, a couple of articles are being reviewed previous to be submmited to a journal.
 One article is for architecture description and example implementation and another for application comparison.
@@
 Integration with other technologies and new trends.
-At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefulness and relevance of these projects in real deployements.
+At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefulness and relevance of this kind of projects in real deployements.
 It is important that new versions of the system will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.

### 2018-06-21 main.tex
Updated bibliography. Changed bibliography style
Created draft for chapter 3
Some corrections and modifications
Updated bibliography and redesigned figure 2.5 to a table
Finished table of fusion models.
Fusion algorithms section finished. Enhancement in tables. Included enumitem package.
Some corrections and parragraph added to ch2. conclusions
Created a draft for the structure of Chapter 3
Added list of figures and tables. Corrected some typos.
Inlcuded package for bookmarks. Updated .gitignore
Added third IMS component paragraph, Target
Added packages for multipage tables
Semi-Finished chapt

@@
 \usepackage{courier}
+\usepackage{multirow}
+\usepackage{enumitem}
+% For links
+\usepackage[bookmarks]{hyperref}
+\hypersetup{colorlinks=true,allcolors=blue}
 
 \usepackage[pdftex]{graphicx}
+\usepackage[toc,page]{appendix}
+\usepackage[nottoc]{tocbibind}
+
+\usepackage{longtable}
+\usepackage{pbox}
+%\usepackage[sorting=none]{biblatex}
+\usepackage{gensymb}
+\usepackage{epigraph}
+
+\usepackage{todonotes}
+
+\usepackage{titling}
+\usepackage{setspace}
+
+\def\arraystretch{1.1}
 
 %\renewcommand{\chaptername}{Capítulo}
-\renewcommand{\figurename}{Figure}
+%\renewcommand{\figurename}{Figure}
 
@@
 
+\bibliographystyle{abbrv}
+%\bibliographystyle{apalike}
+
+\hyphenation{detection camera cameras Systems}
+
 \begin{document}
 
-\title{Multisensor Architecture for an Intersection Management System}
-\author{Gustavo Velasco-Hernández}
-\date{\today}
-\maketitle
+\input{title1}
+\input{title2}
+
+%\title{Multisensor Architecture for an Intersection Management System\vspace{8cm}}
+%\vfill
+%\vfill
+%\vfill
+%\author{Gustavo Velasco-Hernandez\vspace{5cm}}
+%\date{\today}
+%\maketitle
+%
+%\title{Multisensor Architecture for an Intersection Management System}
+%\vfill
+%\vfill
+%\vfill
+%\author{Gustavo Velasco-Hernandez}
+%\vfill
+%\vfill
+%\vfill
+%\date{\today}
+%\maketitle
+
+\chapter*{Abstract}
+\addcontentsline{toc}{chapter}{Abstract}%
+Intersections or juntions are critical points in transportation systems due to their dynamic nature, making them prone to safety or efficiency problems.
+For this reason the use of technology in monitoring intersections have been increasing over the last years.
+After a comprehensive review on this topic, a  multisensor architecture for an intersection management system is conceived, having as main features its scalability and modularity.
+This architecture is composed by 4 main elements: communication structure, data model, information structure and processing blocks.
+An example implementation of the architecture is made using the publisher/subscriber approach along with different tools and technologies that allow the whole system to fulfill the proposed criteria, to be scalable and modular.
+After testing the system using a dataset containing data from camera sensors and lasers sensors, some comments about its results, future developments and integration with current needs and new trends, are discussed.
+
+%\chapter*{Acknowledgements}%
+%\addcontentsline{toc}{chapter}{Acknowledgements}%
+
+%I would like to thank to all people that in some way or another BLABLABLA
 
@@
 
+\listoffigures
+
+\listoftables
+
 \input{ch1-introduction}
-\input{ch2-mdf_ims}
-%\input{CH3-ES}
 
-\bibliographystyle{plain}
+\include{ch2-mdf_ims}
+
+\include{ch3-arch_sys}
+
+\include{ch4-results}
+
+\include{ch5-conclusions}
+
+%\begin{appendices}
+%	\chapter {Vehicular Environment Simulators}
+%\end{appendices}
+
 \bibliography{bibliography}
+%\bibliography{ref}
 

### 2018-06-21 title2.tex
Replaced \maketitle with titlepages
Minor modifications. Apendix removed
Final draft

--- 2018-06-12 title1.tex
@@
         \Huge        
-
         Multisensor Architecture for an Intersection Management System
 
-        \vspace{4.5cm}
+        \vspace{3.5cm}
         \LARGE
@@
         \large
-        \vspace{0.8cm}
+
+        A thesis presented in partial fulfillment of the Requirement for the degree of Master of Science in Engineering with emphasis on Electronics.
+
+        \vspace{2cm}
+
+        Advisor: Prof. Eduardo Caicedo Bravo
+
+		\vspace{2cm}
 
         %\includegraphics[width=0.4\textwidth]{university}
-
+        Perception and Intelligent Systems Research Group \\
         School of Electrical and Electronics Engineering\\

### 2018-07-31 ch3-arch_sys.tex
Ch5 ok. Update.

@@
 
-\item[clusters\_vehicle\_counter] \hfill
+\item[vehicle\_counter] \hfill
 
@@
 \includegraphics[scale=1]{fig/3/clusters_veh_counter.pdf}
-\caption{clusters\_vehicle\_counter}
-\label{clusters_vehicle_counter}
+\caption{Vehicle\_counter}
+\label{vehicle_counter}
 \end{figure}
+
+\todo{CHANGE FIGURE}
+
+This block accepts different types of inputs, cluster\_msg and occgrid\_msg.
+It process the incoming data, and generate bounding boxes based on the clusters or based on the occupancy grid, according to the input.
+Having these bounding boxes, which represent detected vehicles, scene configuration data is loaded and the geometric parameters of the legs and lanes are used to generate virtual sensors at the entry and exit points of the intersection and check the overlaping of detected vehicles with aforemetioned virtual sensors.
+
+This detection is made in a frame basis, meaning that if the overlaping area of a virtual sensor is greater than a threshold $ov_{th}$, it is considered that there is a vehicle over the sensor in that frame.
+Thus, the vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
 
@@
 
-\item[occgrid\_vehicle\_counter] \hfill
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
-\caption{occgrid\_vehicle\_counter}
-\label{occgrid_vehicle_counter}
-\end{figure}
+%\item[occgrid\_vehicle\_counter] \hfill
+%
+%\begin{figure}[ht!]
+%\centering
+%\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
+%\caption{occgrid\_vehicle\_counter}
+%\label{occgrid_vehicle_counter}
+%\end{figure}
 
@@
 \subsection{Conclusions}
+
+A whole intersection management system contains many different components, for example the instrumentation of the junction, the handling of data and information, the control policies and requirements, and the interaction between those elements.
+None of these items is more relevant than the others and it is for this reason that each one of them should be well conceived having in mind a common framework that allows their scalability, modularity and reliability.
+When these three features are accomplished, a change or an upgrade of any part of the system will not affect the remaining ones.
+
+It is also important that an Intersection Management System should be flexible, not tied to one deployment or scenario, but also that allows to perform tests over new datasets or junctions, at no extra cost or just with some configuration adjustments.
+Although it is hard to have a one-rules-them-all system due to the variety of intersections (crossroads with different numbers of legs, roundabouts, T-shaped, Y-shaped, etc.), there are common needs, features and requirements that makes relevant to use an interesection management system looking forward to monitor, control and improve safety and efficiency in transportation.

### 2018-07-31 ch4-results.tex
Ch5 ok. Update.

@@
 \chapter [Deployment and Results]{Deployment and Results}
+
+\epigraph{"Testing leads to failure, and failure leads to understanding"}{Burt Rutan}
+
+In this chapter is presented the experimental setup used to deploy and test the proposed architecture.
+First is described the data and hardware and software specifications.
+Then, the two implemented configurations of the system are presented and finally, results are summarized and analysed.
 
@@
 
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.8]{fig/4/intersection-config2.pdf}
+\caption{Possi dataset configuration}
+\label{possi_img}
+\end{figure}
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.2]{fig/4/sensors_overview.jpeg}
+\caption{Overview of sensors data. Left: Laser scanners, Right: Camera.}
+\label{possi_sensors}
+\end{figure}
+
+%\subsection{Data}
 The selected dataset for testing the system is the one from POSSi project (section \ref{possi_ds}).
 It contains 6 laser-scanners raw readings and a video from a camera located over the intersection.
+Figure \ref{possi_img} depicts the configuration used by this dataset.
+In figure \ref{possi_sensors} is shown the data from each type of sensors, laser scanners and camera.
 The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears.
 This groundtruth data was generated manually.
+
+%\subsection{Hardware and software specifications}
+
+The platform used for the implementation is a laptop ASUS GL552VW, with 8GB RAM DDR4, a processor Intel Core i7 6700HQ @ 2.60GHz x 8 cores and graphic card Nvidia GeForce GTX 960M.
+The operating systems running on it is Ubuntu 16.04 LTS.
+The software was developed using primarily Python3 and C++ as programming languages.
+Used libraries are MatplotLib, Scikit, Numpy, OpenCV, and darknet for data processing and visualisation.
+For communication scheme redis was installed along some JSON parsers for formatting.
 
@@
 
-\subsection{Case 2: Multiple Lasers}
+\subsection{Case 2: Camera and Multiple Lasers}
 
@@
 
-\subsection{Results and Comparison}
+\section{Results}
 
-TODO
+\subsection{Case 1: Single camera}
+
+Detection results in three diferent frames are shown in figure \ref{camera_detection}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.115]{fig/4/camera.jpeg}
+\caption{Vehicle detection using camera}
+\label{camera_detection}
+\end{figure}
+
+\subsection{Case 2: Camera and multple lasers}
+
+Vehicle detection based on laser scanners is shown in figure \ref{laser_detection}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.43]{fig/4/laser1.png}
+\caption{Vehicle detection using laser scanners}
+\label{laser_detection}
+\end{figure}
+
+\section{Conclusions}

### 2018-07-31 ch5-conclusions.tex
Ch5 ok. Update.

@@
 
-\section{General Conclusions}
+%\section{General Conclusions}
 
@@
 
-Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, it is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.
+Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.
 
@@
 On the other side, a couple of articles are being reviewed previous to be submmited to a journal.
-One article is for architecture description and example implementation and another for application comparison.
+One article is  a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation , based on chapters 2 and 3.
 

### 2018-07-31 last_version.tex
Ch5 ok. Update.

\begin{titlepage}
    \begin{center}
%        \vspace*{1cm}
%        \Huge        
%        Multisensor Architecture for an Intersection Management System
%   
%        \vspace{3.5cm}
%        \LARGE
%        Gustavo Adolfo Velasco-Hernandez
%        
%        \vfill
%        \large
%		        
%        
%        A thesis presented in partial fulfillment of the Requirement for the degree of Master of Science in Engineering with emphasis on Electronics.
%        
%        \vspace{2cm}
%        
%        Advisor: Prof. Eduardo Caicedo Bravo
%		
%		\vspace{2cm}
%        
%        %\includegraphics[width=0.4\textwidth]{university}
%        Perception and Intelligent Systems Research Group \\
%        School of Electrical and Electronics Engineering\\
%        Universidad del Valle\\
%        Colombia\\
%        \today
%\vfill

Version: 0.8 \\
\vspace{2cm}
An updated version of this report can be downloaded from: \\
\href{https://github.com/gustavovelascoh/msc-report/raw/master/main.pdf}{Multisensor Architecture for an Intersection Management System}      
    \end{center}
\end{titlepage}

### 2018-08-01 ch3-arch_sys.tex
Ch3 ok. Update.

@@
 The table \ref{desc_map} gives a description of the types of information used.
-A more detailed documentation is given in appendix TODO.
+% A more detailed documentation is given in appendix TODO.
 
@@
 \end{table}
+
+\todo{Finish table}
 
@@
 
-\item[vehicle\_counter] \hfill
+\item[virtual\_sensor\_occupancy] \hfill
 
@@
 Having these bounding boxes, which represent detected vehicles, scene configuration data is loaded and the geometric parameters of the legs and lanes are used to generate virtual sensors at the entry and exit points of the intersection and check the overlaping of detected vehicles with aforemetioned virtual sensors.
+The output generated by this block is the occupancy percentage of the virtual sensor, represented as a message of type vsens\_occ\_msg.
+%vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
 
-This detection is made in a frame basis, meaning that if the overlaping area of a virtual sensor is greater than a threshold $ov_{th}$, it is considered that there is a vehicle over the sensor in that frame.
-Thus, the vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
+\begin{description}
 
-%\item[clusters\_to\_occupancy\_level] \hfill
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=1]{fig/3/clusters2occlvl.pdf}
-%\caption{clusters\_to\_occupancy\_level}
-%\label{clusters_to_occupancy_level}
-%\end{figure}
+\item[virtual\_sensor\_merge] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
+\caption{virtual\_sensor\_merge}
+\label{virtual_sensor_merge}
+\end{figure}
 
-%\item[occgrid\_vehicle\_counter] \hfill
-%
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
-%\caption{occgrid\_vehicle\_counter}
-%\label{occgrid_vehicle_counter}
-%\end{figure}
+\todo{CHANGE FIGURE}
 
-%\item[occgrid\_to\_occupancy\_level] \hfill
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=1]{fig/3/occgrid2occlvl.pdf}
-%\caption{occgrid\_to\_occupancy\_level}
-%\label{occgrid_to_occupancy_level}
-%\end{figure}
+This block is intended to take as inputs different messages of type vsens\_occ\_msg and merging them to increase the reliabilty of detection.
+First, a moving average is calculated over each input to reduce the effect of false positives or false negatives in a single frame.
+After this, the inputs are merged by a defined method like average, weighted average, maximum or minimum.
+Then, a new vsens\_occ\_msg message is dispatched as output.
 
@@
 \subsubsection{Situation Assesment}
-\begin{description}
 
-\item[vehicle\_counter\_merge] \hfill
+\item[virtual\_sensor\_to\_flow\_status] \hfill
 \begin{figure}[ht!]
@@
 \includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
-\caption{vehicle\_counter\_merge}
-\label{vehicle_counter_merge}
+\caption{virtual\_sensor\_to\_flow\_statu}
+\label{virtual_sensor_to_flow_status}
 \end{figure}
-%
-%\item[occupancy\_level\_merge] \hfill
-%\begin{figure}[ht!]
-%\centering
-%\includegraphics[scale=1]{fig/3/occlvl_merge.pdf}
-%\caption{occupancy\_level\_merge}
-%\label{occupancy_level_merge}
-%\end{figure}
+
+\todo{CHANGE FIGURE}
+
+When a message of type vsens\_occ\_msg arrives, it is evaluated using a threshold $vo_{th}$, if the occupancy percentage of a virtual sensor is greater than $vo_{th}$, it is considered that there is a vehicle over the sensor in that frame, this is defined as occupied state.
+This detection is made in a frame basis, thus, a vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
+
+Then, a time interval $t_{c}$ is defined for calculating the flow rate $v_{r}$.
+Defined as the number of transitions during that interval divided by $t_{c}$.
+Then, if $v_{r}$ is above a flow threshold $f_{th}$, it is considered that the traffic is flowing.
+Otherwise, traffic is considered stopped.
 

### 2018-08-04 ch4-results.tex
Ch3 ok. Update.
Ch4 ok. Update.

@@
 \section{Test Configurations}
-In order to test the proposed architecture, two different configurations have been selected.
-The first configuration is using just the camera information.
-The second configuration is based on multiple laser sensors along with the camera.
-
-Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level.
-In this case, vehicle counting is the metric used for evaluation.
-
-The following table lists all used blocks and assigns an ID for each one.
-Those IDs are used in the graph description in its own section.
-Also, bold nodes and connections indicate multiple instance of the same element.
 
@@
 \hline
-\textbf{Block ID} & \textbf{Name} \\
+\textbf{Proc. Stage} & \textbf{Block ID} & \textbf{Name} \\
 \hline
-A & laser\_publisher \\
+
+\multirow{2}{*}{Data feeding} &
+A & camera\_publisher \\
+\cline{2-3} 
+& B & laser\_publisher \\
 \hline
-B & laser\_bg\_remover \\
+
+\multirow{3}{*}{Preprocessing} &
+C & laser\_bg\_remover \\
+\cline{2-3}
+& D & laser\_pol2cart \\
+\cline{2-3}
+& E & laser\_cart\_merge \\
 \hline
-C & laser\_pol2cart \\
+
+\multirow{4}{*}{Feature analysis} &
+F & points2clusters \\
+\cline{2-3}
+& G & points2occgrid \\
+\cline{2-3}
+& H & camera\_blobs \\
+\cline{2-3}
+& I & camera\_blobs2occgrid \\
 \hline
-D & laser\_cart\_merge \\
+
+\multirow{2}{*}{Pattern recognition} &
+J & virtual\_sensor\_occupancy \\
+\cline{2-3}
+& K & virtual\_sensor\_merge \\
 \hline
-E & points2clusters \\
+
+Situation Assesment &
+L & virtual\_sensor\_to\_flow\_status \\
 \hline
-F & clusters\_veh\_counter \\
-\hline
-G & veh\_counter\_merge \\
-\hline
-H & clusters2occ\_level \\
-\hline
-I & occ\_level\_merge \\
-\hline
-J & laser\_pol2cart \\
-\hline
-K & points2occgrid \\
-\hline
-L & occgrid\_merge \\
-\hline
-M & occgrid\_leg\_counter \\
-\hline
-N & occgrid2occ\_level \\
-\hline
-O & camera\_publisher \\
-\hline
-P & camera\_bg\_remover \\
-\hline
-Q & camera\_blobs \\
-\hline
-R & camera\_blobs2occgrid \\
-\hline
+
 \end{tabular}
@@
 
-\subsection{Case 1: Single Camera}
+In order to test the proposed architecture, two different configurations have been selected.
+The first configuration is using just the camera information.
+The second configuration is based on multiple laser sensors along with the camera.
+
+Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level.
+In this case, the binary status of a leg (traffic flow, no traffic flow) is the metric used for evaluation, derived from the vehicle count.
+
+The following table lists all used blocks and assigns an ID for each one.
+Those IDs are used in the graph description in its own section.
+Also, bold nodes and connections indicate multiple instance of the same element.
+The figure \ref{tconf1} shows the  configuration used for processing just video data.
+Figure \ref{tconf2} shows the configuration when a set of lasers is added to the single-camera configuration.
 
@@
 \includegraphics[scale=0.7]{fig/4/test_configuration1.pdf}
-\caption{Single laser configuration}
+\caption{Single camera configuration}
 \label{tconf1}
 \end{figure}
-
-TODO
-
-\subsection{Case 2: Camera and Multiple Lasers}
 
@@
 \includegraphics[scale=0.7]{fig/4/test_configuration2.pdf}
-\caption{Multiple lasers configuration}
+\caption{Multiple lasers and camera configuration}
 \label{tconf2}
@@
 
-TODO
+%TODO
 
@@
 \subsection{Case 1: Single camera}
+
+As stated before, the flow status is used for comparing the system with the ground truth.
+This status is derived from the flow rate in vehicles per second.
+If this value is over a threshold, it is considerded to be in "traffic flow" status.
 
@@
 
-\subsection{Case 2: Camera and multple lasers}
+\subsection{Case 2: Camera and multiple lasers}
 

### 2018-08-17 ch1-introduction.tex
Final draft
Corrections and figures updated.

@@
 
-Chapter 3 presents the result of three example implementations using the architecture: Single-laser case, multiple laser case and multiple laser and camera case.
-These test cases are evaluated and compared, both in application performance, using vehicle count as evaluation metric, and in computational resources usage.
+Chapter 3 presents the result of two example implementations using the architecture: Only camera case and multiple laser and camera case.
+For the later, 4 different fusion strategies are evaluated.
+These test cases are implemented and compared using traffic flow status as comparison indicator.
 

### 2018-08-17 ch3-arch_sys.tex
Corrections and figures updated.

@@
 \centering
-\includegraphics[scale=0.5]{fig/3/data_model.pdf}
+\includegraphics[scale=0.75]{fig/3/data_modelA.pdf}
 \caption{UML diagram of defined entities and their relationships}
@@
 \hline
-clustering\_msg & Contains a set of clusters, each of them with an ID and a set of points \\
+clusters\_msg & Contains a set of clusters, each of them with an ID and a set of points \\
 \hline
-clustering\_cfg & Contains configuration about clustering algorithm and parameters \\
+
+clusters\_cfg & Contains configuration about clustering algorithm and parameters \\
 \hline
+
+camera\_msg & Frames generated by camera \\
+\hline
+
+camera\_cfg & Information and parameters of the camera sensor \\
+\hline
+
+blobs\_msg & Bounding boxes detected as objects within a frame from the camera \\
+\hline
+
+blobs\_cfg & Parameters used by the image detection process\\
+\hline
+
+vs\_occ\_msg & Indicates the occupancy level of a virtual sensor, representing the entrace to or exit from the intersection\\
+\hline
+
+vs\_merge\_cfg & Parameters for configuring the merging process of different vs\_occ\_ms messages.\\
+\hline
+
+flow\_rate\_msg & Indicates the flow rate entering or exiting the intersection\\
+\hline
+
+flow\_cfg & Parameters for estimation of the flow rate, flow status and flow merging configuration\\
+\hline
+
+flow\_status\_msg & Indicates the flow status of an entrance or exit at intersection. This is a binary value, with value either "Traffic flowing" or "Traffic stopped".\\
+\hline
+
 \end{tabular}
@@
 
-\todo{Finish table}
+%\todo{Finish table}
 
@@
 \centering
-\includegraphics[scale=1]{fig/3/clusters_veh_counter.pdf}
-\caption{Vehicle\_counter}
+\includegraphics[scale=1]{fig/3/vs_occ.pdf}
+\caption{Virtual\_sensor\_occupancy}
 \label{vehicle_counter}
 \end{figure}
-
-\todo{CHANGE FIGURE}
 
@@
 Having these bounding boxes, which represent detected vehicles, scene configuration data is loaded and the geometric parameters of the legs and lanes are used to generate virtual sensors at the entry and exit points of the intersection and check the overlaping of detected vehicles with aforemetioned virtual sensors.
-The output generated by this block is the occupancy percentage of the virtual sensor, represented as a message of type vsens\_occ\_msg.
+The output generated by this block is the occupancy percentage of the virtual sensor, represented as a message of type vs\_occ\_msg.
 %vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
@@
 \centering
-\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
+\includegraphics[scale=1]{fig/3/vs_merge.pdf}
 \caption{virtual\_sensor\_merge}
@@
 
-\todo{CHANGE FIGURE}
-
-This block is intended to take as inputs different messages of type vsens\_occ\_msg and merging them to increase the reliabilty of detection.
+This block is intended to take as inputs different messages of type vs\_occ\_msg and merging them to increase the reliabilty of detection.
 First, a moving average is calculated over each input to reduce the effect of false positives or false negatives in a single frame.
 After this, the inputs are merged by a defined method like average, weighted average, maximum or minimum.
-Then, a new vsens\_occ\_msg message is dispatched as output.
+Then, a new vs\_occ\_msg message is dispatched as output.
 
@@
 
-\item[virtual\_sensor\_to\_flow\_status] \hfill
+\item[virtual\_sensor\_to\_flow\_rate] \hfill
 \begin{figure}[ht!]
 \centering
-\includegraphics[scale=1]{fig/3/veh_cnt_merge.pdf}
-\caption{virtual\_sensor\_to\_flow\_statu}
+\includegraphics[scale=1]{fig/3/vs2flow.pdf}
+\caption{virtual\_sensor\_to\_flow\_rate}
 \label{virtual_sensor_to_flow_status}
@@
 
-\todo{CHANGE FIGURE}
-
-When a message of type vsens\_occ\_msg arrives, it is evaluated using a threshold $vo_{th}$, if the occupancy percentage of a virtual sensor is greater than $vo_{th}$, it is considered that there is a vehicle over the sensor in that frame, this is defined as occupied state.
+When a message of type vs\_occ\_msg arrives, it is evaluated using a threshold $vo_{th}$, if the occupancy percentage of a virtual sensor is greater than $vo_{th}$, it is considered that there is a vehicle over the sensor in that frame, this is defined as occupied state.
 This detection is made in a frame basis, thus, a vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
@@
 Defined as the number of transitions during that interval divided by $t_{c}$.
-Then, if $v_{r}$ is above a flow threshold $f_{th}$, it is considered that the traffic is flowing.
+The output message type is flow\_rate\_msg.
+
+\item[flow\_rate\_to\_flow\_status] \hfill
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=1]{fig/3/flow2status.pdf}
+\caption{flow\_rate\_to\_flow\_status}
+\label{flow_rate_to_flow_status}
+\end{figure}
+
+This block process one or more inputs of type flow\_rate\_msg.
+If there are more than one input, it merges them using defined policy, like average or maximum.
+Then, if the flow rate $v_{r}$ is above a flow threshold $f_{th}$, it is considered that the traffic is flowing.
 Otherwise, traffic is considered stopped.
@@
 The objective of this block is to allow the visualisation of the data in any of the processing stages.
-It has the option to display and XY coordinate system, an occupancy grid or a map of the intersection overlaped with detections of metrics.
+It has the option to display and XY coordinate system, an occupancy grid or a map of the intersection overlaped with detections or metrics.
 
@@
 
-\subsection{Conclusions}
+\section{Conclusions}
 

### 2018-08-17 ch4-results.tex
Corrections and figures updated.

@@
 First is described the data and hardware and software specifications.
-Then, the two implemented configurations of the system are presented and finally, results are summarized and analysed.
+Then, two implemented configurations of the system are presented.
+Finally, results are summarized and analysed.
 
@@
 
-Situation Assesment &
-L & virtual\_sensor\_to\_flow\_status \\
+\multirow{2}{*}{Situation Assesment} &
+L & virtual\_sensor\_to\_flow\_rate \\
+\cline{2-3}
+& M & flow\_rate\_to\_flow\_status \\
 \hline
@@
 Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level.
-In this case, the binary status of a leg (traffic flow, no traffic flow) is the metric used for evaluation, derived from the vehicle count.
+In this case, the binary status of a leg (traffic flowing, traffic stopped) is the metric used for evaluation, derived from the vehicle count.
 
@@
 Figure \ref{tconf2} shows the configuration when a set of lasers is added to the single-camera configuration.
+The blue line represents the fusion at node K, which is fusion on virtual sensors level.
+The purple line represents the fusion at flow rate level.
 
@@
 \centering
-\includegraphics[scale=0.7]{fig/4/test_configuration1.pdf}
+\includegraphics[scale=0.6]{fig/4/test_configuration1.pdf}
 \caption{Single camera configuration}
@@
 \centering
-\includegraphics[scale=0.7]{fig/4/test_configuration2.pdf}
+\includegraphics[scale=0.6]{fig/4/test_configuration2.pdf}
 \caption{Multiple lasers and camera configuration}
@@
 This status is derived from the flow rate in vehicles per second.
-If this value is over a threshold, it is considerded to be in "traffic flow" status.
+If this value is greater than a defined threshold, it is considerded to be in "traffic flowing" status.
 
-Detection results in three diferent frames are shown in figure \ref{camera_detection}.
+As result of the first stages of processing, vehicle detection in three diferent frames are shown in figure \ref{camera_detection}. This is a representation of the output from node H, camera\_blobs.
 
@@
 \centering
-\includegraphics[scale=0.115]{fig/4/camera.jpeg}
+\includegraphics[scale=0.11]{fig/4/camera.jpeg}
 \caption{Vehicle detection using camera}
@@
 
-\subsection{Case 2: Camera and multiple lasers}
+In the figure \ref{video_res} is shown the comparison between the flow profile obtained from the system and the generated by the ground truth.
+There is also remarked one of the intervals where the output is "traffic flowing".
+After evaluating the performance of the system in a frame basis, a confusion matrix is obtained (table \ref{video_cf}), here $F$ denotes the state "traffic Flowing" and $S$ denotes "traffic Stopped" and we get an accuracy of 91.82\% and a TPR (True Positive Rate) of 55.70\%.
 
-Vehicle detection based on laser scanners is shown in figure \ref{laser_detection}.
+\begin{table}[ht!]
+\footnotesize
+\centering
+\noindent
+\renewcommand\arraystretch{1.5}
+\setlength\tabcolsep{0pt}
+\begin{tabular}{c c c c c}
+  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+    & \multicolumn{2}{c}{\bfseries Outcome} & \\
+  & & \bfseries F & \bfseries S & \bfseries total \\
+  & F$'$ & \MyBox{694}{} & \MyBox{552}{} & 1246 \\[2.4em]
+  & S$'$ & \MyBox{26}{} & \MyBox{5791}{} & 5817 \\
+  & total & 720 & 6343 &
+\end{tabular}
+\caption{Confusion matrix of the system based on video}
+\label{video_cf}
+\end{table}
 
@@
 \centering
-\includegraphics[scale=0.43]{fig/4/laser1.png}
+\includegraphics[scale=0.45]{fig/4/video_res.pdf}
+\caption{Results for the single camera implementation in one of the legs of the intersection}
+\label{video_res}
+\end{figure}
+
+\subsection{Case 2: Camera and multiple lasers}
+%{'TN': 5791, 'TP': 694, 'FP': 26, 'FN': 552}
+%v30 FPR: 0.0045, F1: 0.7060, NPV: 0.5108, reca: 0.5570, spec: 0.9955, PPV: 0.9639, accu: 0.9182, prec: 0.9639, TPR: 0.5570, prev: 0.1764, 
+%{'TN': 5650, 'TP': 23, 'FP': 167, 'FN': 1223}
+%l30 FPR: 0.0287, F1: 0.0320, NPV: 0.0156, reca: 0.0185, spec: 0.9713, PPV: 0.1211, accu: 0.8032, prec: 0.1211, TPR: 0.0185, prev: 0.1764, 
+%{'TN': 5414, 'TP': 1098, 'FP': 403, 'FN': 148}
+%vl_avg_1_30 FPR: 0.0693, F1: 0.7994, NPV: 0.9216, reca: 0.8812, spec: 0.9307, PPV: 0.7315, accu: 0.9220, prec: 0.7315, TPR: 0.8812, prev: 0.1764, 
+%{'TN': 5669, 'TP': 792, 'FP': 148, 'FN': 454}
+%vl_max_1_30 FPR: 0.0254, F1: 0.7246, NPV: 0.6039, reca: 0.6356, spec: 0.9746, PPV: 0.8426, accu: 0.9148, prec: 0.8426, TPR: 0.6356, prev: 0.1764, 
+%{'TN': 5804, 'TP': 161, 'FP': 13, 'FN': 1085}
+%vl_f_avg_30 FPR: 0.0022, F1: 0.2268, NPV: 0.1091, reca: 0.1292, spec: 0.9978, PPV: 0.9253, accu: 0.8445, prec: 0.9253, TPR: 0.1292, prev: 0.1764, 
+%{'TN': 5624, 'TP': 716, 'FP': 193, 'FN': 530}
+%vl_f_max_30 FPR: 0.0332, F1: 0.6645, NPV: 0.5432, reca: 0.5746, spec: 0.9668, PPV: 0.7877, accu: 0.8976, prec: 0.7877, TPR: 0.5746, prev: 0.1764,
+
+%v30         reca: 0.5570, spec: 0.9955, accu: 0.9182, prec: 0.9639, TPR: 0.5570,
+%vl_avg_1_30 reca: 0.8812, spec: 0.9307, accu: 0.9220, prec: 0.7315, TPR: 0.8812,
+%vl_max_1_30 reca: 0.6356, spec: 0.9746, accu: 0.9148, prec: 0.8426, TPR: 0.6356,
+%vl_f_avg_30 reca: 0.1292, spec: 0.9978, accu: 0.8445, prec: 0.9253, TPR: 0.1292,
+%vl_f_max_30 reca: 0.5746, spec: 0.9668, accu: 0.8976, prec: 0.7877, TPR: 0.5746
+
+In this test case, the information from the laser scanners is used with the purpose of increase the performance of the system.
+This required just to include the appropiate nodes for laser data processing, and replace some nodes from the video processing graph to allow data fusion from laser and cameras.
+An example of vehicle detection based on laser scanners is shown in figure \ref{laser_detection}.
+This is the output of the node F, points2clusters.
+
+\begin{figure}[htb!]
+\centering
+\includegraphics[scale=0.4]{fig/4/laser1a.png}
 \caption{Vehicle detection using laser scanners}
@@
 
+For merging information from laser and cameras, it was decided to perform the fusion at two levels, at the virtual sensor occupancy level and at the flow rate level.
+Both of these approaches were implemented using average and maximum policies.
+In the figure \ref{vl_res} is depicted the flow rate output for all of four configurations.
+
+Performing the same frame-based analysis as for the video system, we obtain the confusion matrices presented in table \ref{vl_cf}.
+It is noted that performing the fusion at virtual sensor occupancy level, the accuracy of the systems has almost no change, 92.2\% and 91.48\% for average and maximum policies respectively.
+For the TPR, there is a significative increase, having 88.12\% and 63.56\%, also for average and maximum policies.
+
+When the fusion is performed at flow rate level using average policy, the accuracy and TPR values are reduced to 84.45\% and 12.92\%.
+Using maximum policy, there is a small decrement in the values, with an accuracy of 89.76\% and a TPR of 57.46\%.
+
+\begin{figure}[htb!]
+\centering
+\includegraphics[scale=0.5]{fig/4/vl_res.pdf}
+\caption{Results for the multisensor implementation using four different fusion approaches}
+\label{vl_res}
+\end{figure}
+
+\begin{table}[htb!]
+\footnotesize
+\centering
+\noindent
+\renewcommand\arraystretch{1.5}
+\setlength\tabcolsep{0pt}
+\begin{tabular}{c c c c c}
+  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+     \multicolumn{4}{c}{\bfseries Outcome (avg vs\_occ)} \\
+  & & \bfseries F & \bfseries S & \bfseries total \\
+  & F$'$ & \MyBox{1098}{} & \MyBox{148}{} & 1246 \\[2.4em]
+  & S$'$ & \MyBox{403}{} & \MyBox{5414}{} & 5817 \\
+  & total & 1501 & 5562 &
+\end{tabular}
+
+\begin{tabular}{c c c c c}
+  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+     \multicolumn{4}{c}{\bfseries Outcome (max vs\_occ)}  \\
+  & & \bfseries F & \bfseries S & \bfseries total \\
+  & F$'$ & \MyBox{792}{} & \MyBox{454}{} & 1246 \\[2.4em]
+  & S$'$ & \MyBox{148}{} & \MyBox{5669}{} & 5817 \\
+  & total & 940 & 6123 &
+\end{tabular}
+
+\begin{tabular}{c c c c c}
+  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+     \multicolumn{4}{c}{\bfseries Outcome (avg flow)} \\
+  & & \bfseries F & \bfseries S & \bfseries total \\
+  & F$'$ & \MyBox{161}{} & \MyBox{1085}{} & 1246 \\[2.4em]
+  & S$'$ & \MyBox{13}{} & \MyBox{5804}{} & 5817 \\
+  & total & 174 & 6889 &
+\end{tabular}
+
+\begin{tabular}{c c c c c}
+  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+     \multicolumn{4}{c}{\bfseries Outcome (max flow)}  \\
+  & & \bfseries F & \bfseries S & \bfseries total \\
+  & F$'$ & \MyBox{716}{} & \MyBox{530}{} & 1246 \\[2.4em]
+  & S$'$ & \MyBox{193}{} & \MyBox{5624}{} & 5817 \\
+  & total & 909 & 6154 &
+\end{tabular}
+
+\caption{Fusion configurations from top to bottom: Average on virtual sensor occupancy, Maximum on virtual sensor occupancy, Average on flow rate, Maximum on flow rate}
+\label{vl_cf}
+\end{table}
+
 \section{Conclusions}
+
+An intersection management system is a complex set of subsystems, and for a feasible implementation and deployment as a real solution it is needed for it to be easily tested, adapted and enhanced.
+In this case, after having a well-concieved block design, it was relatively straight forward to start building a video based system for getting an indicator about traffic flow in an intersection using a dataset.
+
+For stakeholders of the system outcome, high level indicators are desired, like traffic status, no matter which low-level hardware or software are used.
+For this reason, modularity and definitions on data and messages types, allow development of new features without compromising the integrity of the system.
+Also, new sources of information and data could be easily integrated if the processing of them is made according to the definitions.
+In that way, it was possible to integrate laser scanner data provided by the dataset, taking into account to generate outputs already defined by the messages specification.
+
+For different sources of information it is not enough to perform a fusion strategy to obtain better results.
+It is needed to analyse the type of data and the level at which fusion should be performed.
+Also, it is important to understand if the fusion is competitive, complementary or cooperative, in order to select the appropiate strategy and increase the performance of the system.
+An example of this, was found when fusing data from camera and lasers at two different levels and using different strategies.
+It was clear from the results that altough the data was the same, one configuration increased the performace while another one decrease it.

### 2018-08-17 ch1-introduction.tex
Corrections in ch 1, 2 and 5

@@
 Traditionally, the vision of transport systems has been constrainted to the set of elements belonging to infrastructure and the vehicles using it.
-As population increases and cities growth, the number of vehicles going through world roads also increases, but the growth rate of road network is lower.
-This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and develop of efficient and long-lasting solutions carries high costs.
+As population increases and cities growth, the number of vehicles using roads also increases, but the growth rate of road network is lower.
+This situation leads to low quality in transportation; congestion and collisions affect movility in all cities in the world and development of efficient and long-lasting solutions carries high costs.
 
-One of the critical places where is imperative to improve safety and efficiency are vehicular intersections, because at these points many vehicles with different directions and speeds meet each other, increasing probability of incidents.
+One of the critical places where is imperative to improve safety and efficiency is at vehicular intersections, because at these points many vehicles with different directions and speeds meet each other, increasing probability of incidents.
 Almost 40 percent of traffic accidents reported in US in 2008, were intersection related \cite{Choi2010}.
@@
 
-Chapter 3 presents the result of two example implementations using the architecture: Only camera case and multiple laser and camera case.
+Chapter 3 presents the result of two test implementations using the proposed architecture: 1) Using one camera and 2) Using multiple laser and one camera.
 For the later, 4 different fusion strategies are evaluated.

### 2018-08-17 ch5-conclusions.tex
Corrections in ch 1, 2 and 5

@@
 %ch5-conclusions
-\chapter {Conclusions}
+\chapter[Conclusions]{Conclusions}
 
+\epigraph{"If you can't explain it simply, you don't understand it well enough"}{Albert Einstein}
 %\section{General Conclusions}
@@
 On the other side, a couple of articles are being reviewed previous to be submmited to a journal.
-One article is  a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation , based on chapters 2 and 3.
+One article is a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation, based on chapters 2 and 3.
 

### 2018-08-17 main.tex
Ch5 ok. Update.
Corrections and figures updated.
Corrections in ch 1, 2 and 5

@@
-%
+%\documentclass[draft]{book}
 \documentclass{book}
@@
 
+\newcommand\MyBox[2]{
+  \fbox{\lower0.75cm
+    \vbox to 1cm{\vfil
+      \hbox to 1cm{\hfil\parbox{1.1cm}{#1\\#2}\hfil}
+      \vfil}%
+  }%
+}
+
 \begin{document}
@@
 \input{title2}
+
+\input{last_version}
 
@@
 \addcontentsline{toc}{chapter}{Abstract}%
-Intersections or juntions are critical points in transportation systems due to their dynamic nature, making them prone to safety or efficiency problems.
-For this reason the use of technology in monitoring intersections have been increasing over the last years.
+Intersections or junctions are critical points in transportation systems due to their dynamic behaviour, making them prone to safety or efficiency problems.
+For this reason the use of technology in monitoring intersections has increased over the last years.
 After a comprehensive review on this topic, a  multisensor architecture for an intersection management system is conceived, having as main features its scalability and modularity.
-This architecture is composed by 4 main elements: communication structure, data model, information structure and processing blocks.
+This architecture is composed by four main elements: communication structure, data model, information structure and processing blocks.
 An example implementation of the architecture is made using the publisher/subscriber approach along with different tools and technologies that allow the whole system to fulfill the proposed criteria, to be scalable and modular.
-After testing the system using a dataset containing data from camera sensors and lasers sensors, some comments about its results, future developments and integration with current needs and new trends, are discussed.
+After testing the system using a dataset containing data from camera sensors and lasers sensors, it has been found that the use of heterogeneous data can lead to better results, at a low cost in complexity using the proposed framework.
+Comments about  obtained results, future developments and integration with current needs and new trends, are discussed.
 

### 2018-11-13 ch2-mdf_ims.tex
updated figures as required
Final draft
Corrections in ch 1, 2 and 5
Added TODOs

@@
 \chaptermark{Sensor Fusion and IMS}
+
+\epigraph{"The goal is to turn data into information, and information into insight"}{Carly Fiorina}
+%\epigraph{"Not everything that can be counted counts, and not everything that counts can be counted"}{Albert Einstein}
 
@@
 \centering
-\includegraphics[scale=0.4]{fig/2/jdlmodel.png}
+\includegraphics[scale=0.7]{fig/2/jdlmodel.pdf}
 \caption{JDL fusion model. (from \cite{Hall1997}).}
@@
 
-\todo{Create custom figure}
+\todo{Describe level 4 and highlight levels}
 
@@
 \centering
-\includegraphics[scale=0.4]{fig/2/fusionClasses.png}
+\includegraphics[scale=1]{fig/2/mfi.pdf}
 \caption{Five classes of Multisensor Fusion.}
@@
 
-\todo{Increase font size of this figure}
+%\todo{Increase font size of this figure}
 
@@
 
+\todo{Highlight architectures types}
 Elmenreich in \cite{Elmenreich2007} classify fusion models in three categories: Abstract models, generic architectures and rigid architectures.
@@
 In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them, and next, a description of each component is given.
+\todo{Fix V2I label}
 

### 2018-11-13 ch3-arch_sys.tex
Added TODOs

@@
 \subsection{Processing Stages}
+
+\todo{Check stages description and figure}
 
@@
 
-%\todo{Simulators description (?)}
+\todo{Simulators description (?)}
 
@@
 This information is loaded into Redis from a JSON file and it is available for any client requiring it.
+\todo{Define JSON HERE!!!!}
 
@@
 The sensors sets are composed of zero or more sensor objects, as defined previously.
-An Area class is defined as having a bounding box and a label	.
+An Area class is defined as having a bounding box and a label.
 From this class, a derived class, Leg, is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type.
@@
 
+\todo{Move JSON definition from here!!!}
 Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.
@@
 \end{description}
-
+\todo{Check formatting here}
 \subsubsection{Tools and Utilities}

### 2018-11-16 paper02/paper02.tex
paper02

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

%\usepackage{longtable}
%\usepackage{supertabular}
\usepackage{xtab}%,afterpage}
\usepackage{multicol}
\usepackage{pbox}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\bibliographystyle{IEEEtran}

\begin{document}

\title{A Review on Intersection Management Systems and recent IoT Integrated Approaches
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Gustavo Velasco-Hernandez}
\IEEEauthorblockA{\textit{School of Electrical and Electronics Engineering} \\
\textit{Universidad del Valle}\\
Cali, Colombia \\
velasco.gustavo@correounivalle.edu.co}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Eduardo Caicedo-Bravo}
\IEEEauthorblockA{\textit{School of Electrical and Electronics Engineering} \\
\textit{Universidad del Valle}\\
Cali, Colombia \\
eduardo.caicedo@correounivalle.edu.co}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\IEEEpeerreviewmaketitle

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Intersection Management Systems}

Intelligent Transportation Systems includes a wide range of applications and services transversal to many knowledge areas. For classifying those services, some taxonomies have been proposed like the ones presented in \cite[Ch.1]{Sussman2005} and \cite{Williams2008}. From described categories and classes, Advanced Traffic Management Systems have to be considered when an intelligent handling of traffic needs to be deployed.

One of the most desirable scenarios to improve efficiency and safety is an intersection. This because intersections are places where vehicles arrive from different directions at different velocities, increasing the chances for incidents and crashes. Choi \cite{Choi2010} states that 40\% of reported traffic accidents in the US, were intersection related. Also, in  \cite{CorporacionFondodePrevencionVial2010}, is reported that for Colombia in 2011, most of the accidents in the main cities were at intersections.

Different types of applications and systems are conceived to address these issues. Some tasks performed by those systems are intersection monitoring, vehicles detection, incident warning, collision avoidance, among others. A typical Intersection Management System is composed by three main components: Data source, that could be infrastructure sensors, like inductive loops, range sensors or cameras, and vehicle sensors and traveling data; decision system, which is the core of the whole system, is in charge of analyse and process information provided by infrastructure, vehicles and authorities in order to identify objects, recognise patterns, predict future incidents, control traffic and generate safe decisions and warnings alerts; and finally, is the presentation and displaying of the output of decision system, through infrastructure using dynamic signals, traffic light controlling, or using direct communication with drivers or vehicles through on-board visualisation/notification system. A block diagram of a generic IMS is presented in figure \ref{arch}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.55]{fig/2/genericIMS.png}
\caption{Generic block diagram of an Intersection Management System.}
\label{arch}
\end{figure}

\subsection{Components in IMS application}

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch} and developments in IMS have a wide range of approaches and objectives. In order to study IMS applications, five components have been defined, which are present on these applications, and on most cases, more than one component could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them, and next, a description of each component is given.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.25]{fig/2/ims_graph5.png}
\caption{Components of an Intersection Management System application.}
\label{imsComps}
\end{figure}

\subsubsection{Application}

Application component could be seen as the final objective of the system. Generally, this includes high-level tasks like monitoring, analysis or control. Monitoring or surveillance systems execute actions like recognition, detection and/or tracking of objects in the scene. 
Other systems analyse the behaviour and interactions between detected objects to recognise path patterns, determine the context of the environment and predict some events of interest. At a higher level there are systems which make decisions based on detection of certain traffic conditions to handle traffic lights, control intersection access, generate warnings to drivers or issue traffic tickets when a rule violation exists.

\subsubsection{Data Source}

The origin of data is considered an independent component because of the variety of possible sources and posterior processing stages. From infrastructure side, data can be captured using a wide range of sensors like inductive loops, lasers, lidars and cameras. Also, monitoring connections to wireless networks. On the other side, data from vehicles is also useful for the system to enhance its representation of the scene and take decisions. This could be low-level data like vehicle state variables, for example, speed, orientation, acceleration, etc., or high-level data like travel information.

\subsubsection{Target}

In an intersection many objects of different kinds interact between them. Pedestrian and vehicles are found at intersections, and latter includes bicycles, motorcycles, cars, vans, buses, trucks and some other types of vehicles. For this reason some applications are designed for a specific element or group of elements. Pedestrian tracking, motorcycles recognition or car counting are examples of targeted applications.

\subsubsection{Communication}

One of the keypoints of ITS is how information technologies and communication advances are included in transportation. The main goal of this is to allow information sharing between vehicles and infrastructure entities. For this reason, 3 communication approaches appear: Vehicle-to-vehicle or Inter-vehicle communication (V2V), vehicle-to-infrastructure communication (V2I) and vehicle to both vehicle and infrastructure (V2X). Several protocols and standars have been proposed for these communication approaches, for example DSRC, WAVE and IEEE 802.11p, but research and development on this component is still active.

\subsubsection{Implementation}

Not all IMS applications are implementable on a real scenario, maybe because is not the scope of the application or because it is in a early stage and it could be validated in other ways. This types of developments are sometimes implemented and evaluated using simulators, making functional prototypes or deploying scale-models. Some other projects use datasets to evaluate new algorithms and data processing techniques, and then compare obtained results with previous works. Augmented reality is also used as a tool for evaluating and validate developments, taking advantage of the interaction of a real system with a simulated/artificial scenario.

\subsection{Developments in Intersection Management Systems}

In the table \ref{reviewtable} is presented a compilation of several developments within IMS field. For each work a brief comment is given, and a remark of how certain components (Data source, communication and application) are related to it. Target and implementation components could be infered from the comment.

%\clearpage 
%\onecolumn

% IMS review table
%\begin{center}
\footnotesize
%\begin{supertabular} {|c|p{0.3\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}|c|}
%\begin{longtable} {|c|p{0.3\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}|c|}
%\begin{xtabular*}{|c|p{0.3\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}|c|}
%\begin{table}
%\afterpage{
%\onecolumn
\begin{table}
\onecolumn
\begin{xtabular*}{\textwidth}{|p{0.1\textwidth}|p{0.4\textwidth}|p{0.15\textwidth}|p{0.1\textwidth}|p{0.121875\linewidth}|}
%\begin{xtabular*}{\linewidth}{@{\extracolsep{\fill}}|*{5}{p{1.2cm}|}}
%\hline
%\multicolumn{5}{|c|}{ \textbf{Developments on Intersection Management Systems} } \\
%
%\hline
%\pbox{0.1\linewidth}{\textbf{Reference}} & 
%\pbox{0.4\linewidth}{\textbf{Comment}} & 
%\pbox{0.15\linewidth}{\textbf{Application}} & 
%\pbox{0.1\linewidth}{\textbf{Data Source}} & 
%\pbox{0.1\linewidth}{\textbf{Communication}} \\

\hline
%\endfirsthead
%\hline
%\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
%\hline
%\endhead

%\include{../extra/ims_review_table}
\input{table_sample}

\end{xtabular*}
\twocolumn
%} % end of scope of "\afterpage" directive
%\caption{Developments related to Intersection Management Systems.}
\label{reviewtable}
%\end{table}
%\end{longtable}
%\end{supertabular}
%\end{center}
\end{table}

%\twocolumn

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\begin {table}[htb]
\begin{tabular*}{\textwidth}{@{\hskip 6pt\extracolsep{\stretch{1}}}*{9}{r}}
\hline
M       & TA    & MO    & P & N & ID & CC & XC & KL \\
\hline
method  & 0.79  & 0.59  & - & - & 4  & 3  & 5  &    \\
ED  []  & 5     & 7     & - & - & 6  &    &    &    \\
CR      & 4     & 7     & - & - & 22 &    &    &    \\
NB[]    & 2     & 75    & - & - & 6  &    &    &    \\
\hline
\end{tabular*}
\caption{Set of observations }
\end{table}

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\bibliography{IEEEabrv,../bibliography}

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2018-11-16 paper02/table_sample.tex
paper02

{\cite{Kamijo1999, Kamijo2000}} & 
{They show an intersection monitoring system based on a fixed camera. This system is divided in three stages: Background modeling, object tracking and accident detection. They propose an innovative feature for accident detection using HMM.} & 
{Accident  detection} & 
{Camera} & 
{N/A} \\
\hline

{\cite{Veeraraghavan2002}} &
{Passive video-based system for monitoring an intersection. They implemented Stauffer's Method for background modeling, PCA for oriented bounding box computation, and Graph-based tracking and motion estimation. Also a simple methods for classification and calibration are described.} &
{Accident  detection} & 
{Camera} & 
{N/A} \\
\hline

\cite{Veeraraghavan2003} &
They present 4 stages for IMS: background modeling, motion tracking, feature extraction, calibration. They propose a 2-level tracking: Blob tracking as low-level and position using Kalman filter as high-level. &
Accident detection / prediction &
Camera & 
N/A \\
\hline

\cite{Messelodi2004} &
A Full implementation of an IMS in a town in northern Italy. The system claims to be independent of intersection geometry and it is based on a monocular camera. Processing stages of the system and classification approaches are described. &
Intersection Monitoring &
Camera &
N/A \\
\hline

%\cite{Dogan2004} &
%Development of a simulator for an Intersection Collision Warning System. Physical and MAC layers were modeled &
%Intersection collision warning simulator &
%N/A &
%V2V \\
%\hline
%
%\cite{Chan2004} &
% Traffic monitoring for two context: Left-Turn-Across-Path-Opposite-Direction and Dilemma zone and red light violation &
%Intersection Monitoring &
%Radar &
%N/A \\
%\hline
%
%\cite{Atev2005} &
%A collision prediction system based on computational geometry is presented. The two main stages are low-level vision system for foreground optimization, with shaking compensation and noise removal, and a collision prediction system based on bounding boxes instead of bounding rectangles. &
%Collision prediction &
%Camera &
%N/A \\
%\hline
%
%\cite{Chan2005} &
%Analysis of Left-Turn-Across-Path-Opossite-Direction conflict situation. &
%Intersection Monitoring &
%Radar; Steering, speed sensors and GPS on-board &
%V2X \\
%\hline
%
%\cite{Avila2005} &
%Based on \cite{Dogan2004}, this works includes and improvement, including network layer and driver behaviour model. &
%Intersection Simulator Architecture &
%N/A &
%V2X \\
%\hline
%
%\cite{Veeraraghavan2005} &
%Tracking system based on Kalman filter for tracking and event detection at intersections, capable of detect 4 events: Acceleration, uniform velocity, stop and turns. &
%Tracking and event detection &
%Camera &
%N/A \\
%
%\hline

### 2018-12-15 paper02/paper02.tex
6 pages version

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+Intersections or junctions are critical points in transportation systems due to their dynamic behaviour, making them prone to safety or efficiency problems.
+For this reason, the use of technology in monitoring intersections has increased over the last years.
+In addition, different proposals based on the Internet of Things (IoT) have been used to handle different traffic issues at intersections, taking advantage of the features it provides regarding hardware, software and communications.
+This work presents a comprehensive review on Intersection Management Systems (IMS), from a component-based point of view, and a special remark on how IoT-based solutions have been adopted recently in this area is presented as well.
 \end{abstract}
@@
 
-\begin{IEEEkeywords}
-component, formatting, style, styling, insert
-\end{IEEEkeywords}
+%\begin{IEEEkeywords}
+%component, formatting, style, styling, insert
+%\end{IEEEkeywords}
 
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Traditionally, the vision of transport systems has been constrained to the set of elements belonging to infrastructure and the vehicles using it.
+As population increases and cities grow, the number of vehicles using roads also increases, but the growth rate of the road network is lower.
+This situation leads to low quality in transportation; congestion and collisions affect mobility in all cities in the world and the development of efficient and long-lasting solutions carry high costs.
 
-\section{Intersection Management Systems}
-
-Intelligent Transportation Systems includes a wide range of applications and services transversal to many knowledge areas.
+The aim of Intelligent Transportation Systems is to address these issues by taking advantage of improvements in information and communication technologies.
+These ITS include a wide range of applications and services transversal to many knowledge areas.
 For classifying those services, some taxonomies have been proposed like the ones presented in \cite[Ch.1]{Sussman2005} and \cite{Williams2008}.
@@
 This because intersections are places where vehicles arrive from different directions at different velocities, increasing the chances for incidents and crashes.
-Choi \cite{Choi2010} states that 40\% of reported traffic accidents in the US, were intersection related.
+Choi \cite{Choi2010} states that 40\% of reported traffic accidents in the US were intersection related.
 Also, in  \cite{CorporacionFondodePrevencionVial2010}, is reported that for Colombia in 2011, most of the accidents in the main cities were at intersections.
+
+On the other side, the Internet of Things has enabled the creation of new sources of data due to the development of low-cost and low-power devices.
+In addition, the computing capabilities of those devices are increasing constantly, allowing the implementation of complex applications in different areas.
+One of the areas where IoT-based solutions are integrated is transportation, with great adoption in the intersection management systems field.
+
+In section II, a general description and a review on intersection management systems are presented, from early developments until recent works.
+Section III describe how IoT-based solutions have been adopted into the field of transportation, specially for optimisation and control at intersections.
+Finally, in section IV some comments are given and future steps in the area are discussed.
+
+\section{Intersection Management Systems}
 
@@
 \centering
-\includegraphics[scale=0.55]{fig/2/genericIMS.png}
+\includegraphics[scale=0.38]{../fig/2/genericIMS.png}
 \caption{Generic block diagram of an Intersection Management System.}
@@
 \centering
-\includegraphics[scale=0.25]{fig/2/ims_graph5.png}
+\includegraphics[scale=0.19]{../fig/2/ims_graph5.png}
 \caption{Components of an Intersection Management System application.}
@@
 
-In the table \ref{reviewtable} is presented a compilation of several developments within IMS field.
-For each work a brief comment is given, and a remark of how certain components (Data source, communication and application) are related to it.
-Target and implementation components could be infered from the comment.
+In the table \ref{reviewtable} is presented a compilation of several developments within IMS field from the last 20 years.
+For each work a description is given in which target and implementation components are highlighted.
+Additionally, Data source, communication and application components are detailed in their own column.
 
@@
 %\afterpage{
+\onecolumn
+%\begin{table}
 %\onecolumn
-\begin{table}
-\onecolumn
-\begin{xtabular*}{\textwidth}{|p{0.1\textwidth}|p{0.4\textwidth}|p{0.15\textwidth}|p{0.1\textwidth}|p{0.121875\linewidth}|}
+%\begin{xtabular*}{\textwidth}{|p{0.1\textwidth}|p{0.4\textwidth}|p{0.15\textwidth}|p{0.1\textwidth}|p{0.121875\linewidth}|}
 %\begin{xtabular*}{\linewidth}{@{\extracolsep{\fill}}|*{5}{p{1.2cm}|}}
@@
 
-\hline
+%\hline
 %\endfirsthead
@@
 \end{xtabular*}
-\twocolumn
+%\twocolumn
 %} % end of scope of "\afterpage" directive
 %\caption{Developments related to Intersection Management Systems.}
-\label{reviewtable}
+
 %\end{table}
@@
 %\end{center}
+\end{table*}
+
+\twocolumn
+
+\section{Internet of Things at Intersections}
+
+Given that the IoT concept is related to the whole stack of a solution, which include hardware, communication, infrastructure and visualization, the benefits that it can provide to IMS is great.
+For this reason, in the recent years IMS applications have been increasing their scope, including almost all of the components described in the previous section.
+
+For example, with the reduced cost of making new sensors, it has been possible to deploy more prototypes rather than work in simulated scenarios.
+Or instead of make architecture proposal of intersection management systems, current IoT infrastructure and platform are ready to deploy such proposed architectures.
+This can be seen in table |\ref{iotrev}, where a description of  IoT-based developments are summarized.
+
+\begin{table}[tp]
+\caption{IoT-based developments for IMS}
+\label{iotrev}
+\begin{xtabular}{|p{0.12\linewidth}|p{0.52\linewidth}|p{0.22\linewidth}|}
+
+\hline
+\textbf{Reference} & \textbf{Comment} & \textbf{Implementation} \\
+\hline
+{\cite{Tan2011}} &
+{Proposal of using IOT-based set of sensors as source of data for intersection control} &
+{Simulation}\\
+
+\hline
+{\cite{Turcu2012}} &
+{IOT-based approach for traffic light control to reduce congestion for environmental conservation } &
+{Proposal} \\
+
+\hline
+{\cite{Chong2016}} & { IOT device developmenr for traffic flow metering and traffic light control using 3rd party IoT ready infrasttructure as backend} & {Prototype} \\
+
+\hline
+{\cite{Talukder2017}} & {Microcontroller-based device for lane monitoring at intersection with a Web application for user interaction} & {Prototype} \\
+
+\hline
+\cite{Nagmode2018} & {Full stack implementation (hardware, communications, web server) for traffic flow metering} & {Prototype} \\
+
+\hline
+{\cite{Khan2018}} & { Metering and control at intersections within a emergency vehicles priority scheme. It includes sensing, control and communication stages} & {Prototype} \\
+
+\hline
+
+\end{xtabular}
 \end{table}
 
-%\twocolumn
+%\cite{Turcu2012} IOT-based approach for traffic light control to reduce congestion for environmental conservation
 
-\section{Ease of Use}
+%\cite{Sommer2014} Virtual Traffic Ligths, V2V, Simulation. Traffic control
 
-\subsection{Maintaining the Integrity of the Specifications}
+%\cite{Hsieh2014} Smart Traffic at intersection with GA. Simulation and prototypes were used
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+%\cite{Nagmode2018} && {Full stack implementation (hardware, communications, web server) for traffic flow metering} && {Prototype} \\
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\section{Conclusions}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+Intersection are complex scenarios that still face efficiency and safety issues, although different approaches have been proposed and implemented.
+The Internet of things adds a new set of tools for several applications, offering improvements and all the stack of an Intersection Management System application, from the hardware up to the control and user interaction.
 
-\begin {table}[htb]
-\begin{tabular*}{\textwidth}{@{\hskip 6pt\extracolsep{\stretch{1}}}*{9}{r}}
-\hline
-M       & TA    & MO    & P & N & ID & CC & XC & KL \\
-\hline
-method  & 0.79  & 0.59  & - & - & 4  & 3  & 5  &    \\
-ED  []  & 5     & 7     & - & - & 6  &    &    &    \\
-CR      & 4     & 7     & - & - & 22 &    &    &    \\
-NB[]    & 2     & 75    & - & - & 6  &    &    &    \\
-\hline
-\end{tabular*}
-\caption{Set of observations }
-\end{table}
+Since the establishment of IoT, intersection management system applications have moved from simulated and proposed scenarios to prototype creation and real world deployments, because the creation of sources of data and the implementation of computing systems is not longer expensive as it was 5 or more years ago.
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+Oncoming advances in computing capabilities, low-power platforms, and a variety of communication protocols, open a door to newer and optimized solutions.
+Also, these allow the generation of joint solution with a wider scope, not just for transportation, but for social or environmental scenarios, having a higher impact on society.
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\bibliography{IEEEabrv,../bibliography}
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\bibliography{IEEEabrv,../bibliography,iot}
 

### 2018-12-15 paper02/table_sample.tex
6 pages version

@@
-{\cite{Kamijo1999, Kamijo2000}} & 
+\begin{table*}[tp]
+\caption{Developments on Intersection Management Systems}
+\label{reviewtable}
+\begin{xtabular*}{\textwidth}{|p{0.08\textwidth}|p{0.41\textwidth}|p{0.15\textwidth}|p{0.12\textwidth}|p{0.121875\linewidth}|}
+
+\hline
+\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
+\hline
+
+\cite{Kamijo1999, Kamijo2000} & 
 {They show an intersection monitoring system based on a fixed camera.
@@
 {Accident  detection} & 
-{Camera} & 
-{N/A} \\
+Camera & 
+N/A \\
 \hline
 
-{\cite{Veeraraghavan2002}} &
+\cite{Veeraraghavan2002} &
 {Passive video-based system for monitoring an intersection.
@@
 {Accident  detection} & 
-{Camera} & 
-{N/A} \\
+Camera & 
+N/A \\
 \hline
+
+%\cite{Gehrig2003} & & & & \\ \hline
 
@@
 
-%\cite{Dogan2004} &
-%Development of a simulator for an Intersection Collision Warning System. Physical and MAC layers were modeled &
-%Intersection collision warning simulator &
-%N/A &
-%V2V \\
-%\hline
-%
-%\cite{Chan2004} &
-% Traffic monitoring for two context: Left-Turn-Across-Path-Opposite-Direction and Dilemma zone and red light violation &
-%Intersection Monitoring &
-%Radar &
-%N/A \\
-%\hline
-%
-%\cite{Atev2005} &
-%A collision prediction system based on computational geometry is presented.
+\cite{Dogan2004} &
+Development of a simulator for an Intersection Collision Warning System. Physical and MAC layers were modeled &
+Intersection collision warning simulator &
+N/A &
+V2V \\
+\hline
+
+\cite{Chan2004} &
+ Traffic monitoring for two context: Left-Turn-Across-Path-Opposite-Direction and Dilemma zone and red light violation &
+Intersection Monitoring &
+Radar &
+N/A \\
+\hline
+
+\cite{Atev2005} &
+A collision prediction system based on computational geometry is presented.
 The two main stages are low-level vision system for foreground optimization, with shaking compensation and noise removal, and a collision prediction system based on bounding boxes instead of bounding rectangles.
 &
-%Collision prediction &
-%Camera &
-%N/A \\
+Collision prediction &
+Camera &
+N/A \\
+\hline
+
+\cite{Chan2005} &
+Analysis of Left-Turn-Across-Path-Opossite-Direction conflict situation. &
+Intersection Monitoring &
+Radar; Steering, speed sensors and GPS on-board &
+V2X \\
+\hline
+
+\cite{Avila2005} &
+Based on \cite{Dogan2004}, this works includes and improvement, including network layer and driver behaviour model. &
+Intersection Simulator Architecture &
+N/A &
+V2X \\
+\hline
+
+\cite{Veeraraghavan2005} &
+Tracking system based on Kalman filter for tracking and event detection at intersections, capable of detect 4 events: Acceleration, uniform velocity, stop and turns. &
+Tracking and event detection &
+Camera &
+N/A \\
+\hline
+
+\cite{Zhao2006} &
+Object tracking and classification at intersection using a single laser scanner.
+The system identifies 3 classes: Pedestrians, 2-wheeled vehicle and cars.
+It is based on points clustering, KL transform and markov chains &
+Object tracking and classification &
+Laser &
+N/A \\
+\hline
+
+\cite{Eguchi2007} &
+A system for discriminate an approaching vehicle to an intersection is described.
+It use a monocular camera and define a number of features for classification.
+Motion vectors are used too and determine the level of approaching.
+&
+Vehicle detection &
+Camera &
+N/A \\
+\hline
+
+\cite{Kuramoto2007} &
+A communication scheme based on nearest to intersection is described.
+Two zones are defined: nearest zone and quasi-nearest zone.
+Based on which zone vehicles are, communicaton is performed.
+Validation of proposal is done using a custom microscopic simulator.
+&
+Intersection Communication Scheme &
+N/A &
+V2I \\
+\hline
+
+\cite{Dresner2008} &
+A multiagent-based intersection control protocol called autonomous intersection management (AIM) is proposed.
+Based on a custom simulation, vehicles are modeled and they comunicate with an intersection manager which allows or deny access to intersection.
+It is possible to set different traffic policies, even for emulate current control approaches lke stop lights and traffic lights.
+&
+Intersection Management &
+On-board state sensors &
+V2I \\
+\hline
+
+\cite{Jarupan2008} &
+Based on \cite{Dogan2004} and \cite{Avila2005}, this simulator architecture emphasize on wireless communications.
+Now the system allows to compare different communication protocols and traffic configurations.
+&
+Intersection Simulator Architecture &
+N/A &
+V2V \\
+\hline
+
+\cite{Zhao2008} &
+Based on \cite{Zhao2006}, the system now includes more laser sensor for get a better representation of the scene, solving some occlusion issues.
+Clustering is used for grouping readings from different sensors belonging to the same object and a tracking approach based on angle of beam, range and time is presented.
+&
+Intersection monitoring &
+Lasers &
+N/A \\
+\hline
+
+\cite{Rawashdeh2008} &
+Proposal of a communication architecture for vehicles approaching to an intersection.
+Two zones are defined: Control Channel Zone (CCHZ) and Service Channel Zone (SCHZ).
+Also, 3 different methods are described for the system to be implmented &
+Collision avoidance &
+N/A &
+V2I \\
+\hline
+
+\cite{Mundewadikar2008} &
+Proposal of a physical-layer protocol for V2I communication at intersections. The system is evaluated in simulation using MATLAB &
+Collision detection and warning &
+N/A &
+V2I \\
+\hline
+
+\cite{Zhao2009} &
+Based on \cite{Zhao2008}, now the system includes a camera for video capture.
+In this video, data obtained from the lasers-based system are projected, drawing bounding boxes for vehicles and lines for trajectories.
+&
+Intersection monitoring &
+Camera, Lasers &
+N/A \\
+\hline
+
+\end{xtabular*}
+\end{table*}
+
+\begin{table*}[tp]
+\begin{xtabular*}{\textwidth}{|p{0.08\textwidth}|p{0.41\textwidth}|p{0.15\textwidth}|p{0.12\textwidth}|p{0.121875\linewidth}|}
+
+\hline
+\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
+\hline
+
+\cite{Abbas2009} &
+Monitoring dilemma zone and efectiveness of control policies using cameras and loop detectors on an intersection &
+Intersection monitoring &
+Cameras, loop detectors &
+N/A \\
+\hline
+
+\cite{Babaei2010} &
+Author presents a system for foreground extraction, vehicle detection and tracking.
+A novel algorithm is proposed based on image division in traffic zones to perform background removal and vehicle detection.
+This proposal is compared with traditional MoG approach.
+&
+Intersection monitoring &
+Camera &
+N/A \\
+\hline
+
+\cite{Meissner2010} &
+A semi-automatic calibration method for a network of lidar sensors is presented using a custom simulation environment. Also, a calibration object were designed based on simulation results. &
+Intersection Monitoring &
+Lidars &
+N/A \\
+\hline
+
+\cite{Quinlan2010} &
+An augmented reality implementation of the system proposed in cite{Dresner2008} is presented.
+In this work, an autonomous vehicle is deployed in a mixed-reality platform and request to an virtual intersection manager for authorisation to cross and is the manager which decides if it is safe to cross or not, depending on the defined traffic policies and the state of virtual vehicles.
+&
+Intersection management &
+On-board state sensors &
+V2I \\
+\hline
+
+\cite{Ball2010} &
+The use of intelligent objects in vehicles is proposed.
+With sharing vehicle state information and jouney plans, the system aims to better control traffic in intersection using a novel back-off protocol instead of time traffic control system.
+&
+Traffic control &
+On-board state sensors, Journey plans &
+V2V \\
+\hline
+
+\cite{Babaei2011} &
+A system for traffic flow measurement based on anormalities detection is presented. Multiple cameras are used SIFT and unsupervised SVM-based clustering are performed for trajectories analysis. &
+Intersection monitoring &
+Cameras &
+N/A \\
+\hline
+
+\cite{Basma2011} &
+In presented system, wireless magnetic nodes are used to detect presence and to send data to a base station, which determines possible collisions and warns driver through a visualisation system in infrastructure.
+&
+Collision Avoidance	 &
+Presence sensors &
+N/A \\
+\hline
+
+\cite{Azimi2012} &
+An intersection control protocol based on V2V communication is proposed.
+This protocol is in charge of handling other vehicles messages and determines if is it safe or not to cross.
+They present two policies for managing intersection access: Concurrent Crossing- Intersection Protocol (CC-IP) and Maximum Progression-Intersection Protocol (MP-IP).
+&
+Intersection management &
+N/A &
+V2V \\
+\hline
+
+\cite{CondeBento2012} &
+A microscopic simulator was developed, with a spatial-temporal-based approach for managing the intersection.
+It is possible to implement different traffic policies for comparison purposes and the system works on crossroads and roundabouts.
+&
+Intersection management &
+On-board state sensors &
+V2X \\
+\hline
+
+\cite{Zhao2012} &
+A novel approach for detecting moving objects and track them is presented.
+The focus of this work relies on process merged data from laser sensors (\cite{Zhao2009}) to get better results at tracking.
+&
+Object detection and tracking &
+Lasers &
+N/A \\
+\hline
+
+\cite{Jin2012} &
+A Multiagent-based system is proposed.
+They define a Vehicle Agent and and Intersection Agent and propose a protocol for controlling intersection access based on timeslots, Also, the present a vehicle motion planning algorithm.
+Validation and testing was done using SUMO platform &
+Intersection Management &
+On-board state sensors &
+V2I \\
+\hline
+
+\cite{Meissner2012} &
+A set of laser scanners is used for detect and track pedestrians. GMM and DBSCAN are proposed for detection stage. For tracking purpose, a random finite set particle filter is used. &
+Pedestrians detection and tracking &
+Lasers &
+N/A \\
+\hline
+
+\cite{Goldhammer2012} &
+In this work is presented the setting and configuration of a multisensor network, based on 14 lasers, 10 cameras, GPS and V2I unit. Calibration and spatial-temporal alignment is performed. &
+System Architecture &
+Cameras, Lasers &
+V2I \\
+\hline
+
+\cite{Friesen2013} &
+A set of wireless probes are deployed to estimate traffic flow based on bluetooth connections.
+Then, using Zigbee, data is send to a master node which handle data for forwarding to a server / database for further processing.
+&
+Traffic monitoring &
+Wireless sensor network &
+N/A \\
+\hline
+
+\cite{Guerrero-Ibanez2013} &
+Two modes of Intersection Access Control: V2I mode and V2V mode. Implementation was done using minirobots in a scale model of an intersection. &
+Intersection access control &
+Loop detectors and RFID nodes &
+V2X \\
+\hline
+
+%\cite{Meissner2013,Meissner2013a} &
+% &
+% &
+% &
+% \\
 %\hline
-%
-%\cite{Chan2005} &
-%Analysis of Left-Turn-Across-Path-Opossite-Direction conflict situation. &
-%Intersection Monitoring &
-%Radar; Steering, speed sensors and GPS on-board &
-%V2X \\
-%\hline
-%
-%\cite{Avila2005} &
-%Based on \cite{Dogan2004}, this works includes and improvement, including network layer and driver behaviour model. &
-%Intersection Simulator Architecture &
-%N/A &
-%V2X \\
-%\hline
-%
-%\cite{Veeraraghavan2005} &
-%Tracking system based on Kalman filter for tracking and event detection at intersections, capable of detect 4 events: Acceleration, uniform velocity, stop and turns. &
-%Tracking and event detection &
-%Camera &
-%N/A \\
-%
-%\hline
+
+\cite{Meissner2013b} &
+A new method for object detection based on lidars data is proposed.
+After perform background removal, they use DBGridSCAN for 3D clustering and 2D pathway tracking.
+Then a combination of 2D-3D is done.
+The proposal is validated using OSPA metric.
+&
+Object Detection &
+Lasers &
+N/A \\
+\hline
+
+\cite{Au2015} &
+On top of AIM (\cite{Dresner2008}) Semi-AIM protocol is proposed.
+Assuming that human-driven vehicles to autonomous vehicles transition will be long, this system is intended for semi-autonomous vehicles.
+Also the author describe the human relation to a semi-autonomous vehicle and analyse how the features of autonomy employed by the car affects the traffic delay.
+&
+Intersection Management &
+On-board state sensors &
+V2I \\
+\hline

### 2018-12-15 paper02/paper02.tex
4 pages version. uploaded

@@
 \centering
-\includegraphics[scale=0.19]{../fig/2/ims_graph5.png}
+\includegraphics[scale=0.17]{../fig/2/ims_graph5.png}
 \caption{Components of an Intersection Management System application.}
@@
 
-In the table \ref{reviewtable} is presented a compilation of several developments within IMS field from the last 20 years.
+In the table \ref{reviewtable} is presented a compilation of several developments within IMS field from the last 10 years.
 For each work a description is given in which target and implementation components are highlighted.
@@
 %\begin{center}
-\footnotesize
+
 %\begin{supertabular} {|c|p{0.3\linewidth}|p{0.15\linewidth}|p{0.1\linewidth}|c|}
@@
 %\afterpage{
-\onecolumn
+%\onecolumn
 %\begin{table}
@@
 
-\twocolumn
+%\twocolumn
 
@@
 
-Given that the IoT concept is related to the whole stack of a solution, which include hardware, communication, infrastructure and visualization, the benefits that it can provide to IMS is great.
-For this reason, in the recent years IMS applications have been increasing their scope, including almost all of the components described in the previous section.
+Given that the IoT concept is related to the whole stack of a solution, which include hardware, communication, infrastructure and visualization, the benefits that it can provide to IMS implementations is great.
+For this reason, in the recent years IMS applications have been increasing their scope, including almost all of the components described in the previous section, and not just one or two.
+This means that IoT improvements affect each of the components making them more modular, scalable and integrable.
 
-For example, with the reduced cost of making new sensors, it has been possible to deploy more prototypes rather than work in simulated scenarios.
+Starting with the data source component, IoT-based sensors allow new kind of data to be integrated into the process flow of the system.
+For example, data from sensors intended for other fields like pollution monitoring or weather conditions could be used to improve or evaluate traffic conditions.
+In the same way, an IMS application could be designed from the beginning to not just a transportation scope but also to be oriented to social or enviromental issues.
+
+In this way, the target component now includes the live users of the road (vehicles, pedestrians) but also all those which are indirectly interested, for example prospective travelers, authorities, and the public in general.
+And due to the new variety of communication possibilities that different IoT protocols offer, the integration of an IMS with other systems is more straightforward, making the data available to a new group of stakeholders.
+
+In the implementation component, with the reduced cost of making new sensors, it has been possible to deploy more prototypes rather than work in simulated scenarios.
 Or instead of make architecture proposal of intersection management systems, current IoT infrastructure and platform are ready to deploy such proposed architectures.
-This can be seen in table |\ref{iotrev}, where a description of  IoT-based developments are summarized.
+In table \ref{iotrev} some IoT-based developments are summarized, where their application in an IMS and their implementation approach are decribed.
 

### 2018-12-15 paper02/table_sample.tex
4 pages version. uploaded

--- 2018-11-16 paper02/table_sample.tex
@@
-{\cite{Kamijo1999, Kamijo2000}} & 
-{They show an intersection monitoring system based on a fixed camera.
+%\begin{table*}[tp]
+%\caption{Developments on Intersection Management Systems}
+%\label{reviewtable}
+%\begin{xtabular*}{\textwidth}{|p{0.08\textwidth}|p{0.41\textwidth}|p{0.15\textwidth}|p{0.12\textwidth}|p{0.121875\linewidth}|}
+%
+%\hline
+%\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
+%\hline
+%
+%
+%\cite{Kamijo1999, Kamijo2000} & 
+%{They show an intersection monitoring system based on a fixed camera.
 This system is divided in three stages: Background modeling, object tracking and accident detection.
 They propose an innovative feature for accident detection using HMM.} &
-{Accident  detection} & 
-{Camera} & 
-{N/A} \\
-\hline
-
-{\cite{Veeraraghavan2002}} &
-{Passive video-based system for monitoring an intersection.
+%{Accident  detection} & 
+%Camera & 
+%N/A \\
+%\hline
+%
+%\cite{Veeraraghavan2002} &
+%{Passive video-based system for monitoring an intersection.
 They implemented Stauffer's Method for background modeling, PCA for oriented bounding box computation, and Graph-based tracking and motion estimation.
 Also a simple methods for classification and calibration are described.} &
-{Accident  detection} & 
-{Camera} & 
-{N/A} \\
-\hline
-
-\cite{Veeraraghavan2003} &
-They present 4 stages for IMS: background modeling, motion tracking, feature extraction, calibration.
+%{Accident  detection} & 
+%Camera & 
+%N/A \\
+%\hline
+%
+%%\cite{Gehrig2003} & & & & \\ \hline
+%
+%\cite{Veeraraghavan2003} &
+%They present 4 stages for IMS: background modeling, motion tracking, feature extraction, calibration.
 They propose a 2-level tracking: Blob tracking as low-level and position using Kalman filter as high-level.
 &
-Accident detection / prediction &
-Camera & 
-N/A \\
-\hline
-
-\cite{Messelodi2004} &
-A Full implementation of an IMS in a town in northern Italy.
+%Accident detection / prediction &
+%Camera & 
+%N/A \\
+%\hline
+%
+%\cite{Messelodi2004} &
+%A Full implementation of an IMS in a town in northern Italy.
 The system claims to be independent of intersection geometry and it is based on a monocular camera.
@@
 &
-Intersection Monitoring &
-Camera &
-N/A \\
-\hline
-
+%Intersection Monitoring &
+%Camera &
+%N/A \\
+%\hline
+%
 %\cite{Dogan2004} &
@@
 %N/A \\
+%\hline
+%
+%\cite{Zhao2006} &
+%Object tracking and classification at intersection using a single laser scanner.
+The system identifies 3 classes: Pedestrians, 2-wheeled vehicle and cars.
+It is based on points clustering, KL transform and markov chains &
+%Object tracking and classification &
+%Laser &
+%N/A \\
+%\hline
+%
+%\cite{Eguchi2007} &
+%A system for discriminate an approaching vehicle to an intersection is described.
+It use a monocular camera and define a number of features for classification.
+Motion vectors are used too and determine the level of approaching.
+&
+%Vehicle detection &
+%Camera &
+%N/A \\
+%\hline
+%
+%\cite{Kuramoto2007} &
+%A communication scheme based on nearest to intersection is described.
+Two zones are defined: nearest zone and quasi-nearest zone.
+Based on which zone vehicles are, communicaton is performed.
+Validation of proposal is done using a custom microscopic simulator.
+&
+%Intersection Communication Scheme &
+%N/A &
+%V2I \\
+%\hline
+%
+%\cite{Dresner2008} &
+%A multiagent-based intersection control protocol called autonomous intersection management (AIM) is proposed.
+Based on a custom simulation, vehicles are modeled and they comunicate with an intersection manager which allows or deny access to intersection.
+It is possible to set different traffic policies, even for emulate current control approaches lke stop lights and traffic lights.
+&
+%Intersection Management &
+%On-board state sensors &
+%V2I \\
+%\hline
+%
+%\cite{Jarupan2008} &
+%Based on \cite{Dogan2004} and \cite{Avila2005}, this simulator architecture emphasize on wireless communications.
+Now the system allows to compare different communication protocols and traffic configurations.
+&
+%Intersection Simulator Architecture &
+%N/A &
+%V2V \\
+%\hline
+%
+%\cite{Zhao2008} &
+%Based on \cite{Zhao2006}, the system now includes more laser sensor for get a better representation of the scene, solving some occlusion issues.
+Clustering is used for grouping readings from different sensors belonging to the same object and a tracking approach based on angle of beam, range and time is presented.
+&
+%Intersection monitoring &
+%Lasers &
+%N/A \\
+%\hline
+%
+%\cite{Rawashdeh2008} &
+%Proposal of a communication architecture for vehicles approaching to an intersection.
+Two zones are defined: Control Channel Zone (CCHZ) and Service Channel Zone (SCHZ).
+Also, 3 different methods are described for the system to be implmented &
+%Collision avoidance &
+%N/A &
+%V2I \\
+%\hline
+%
+%\cite{Mundewadikar2008} &
+%Proposal of a physical-layer protocol for V2I communication at intersections. The system is evaluated in simulation using MATLAB &
+%Collision detection and warning &
+%N/A &
+%V2I \\
+%\hline
+%
+%\cite{Zhao2009} &
+%Based on \cite{Zhao2008}, now the system includes a camera for video capture.
+In this video, data obtained from the lasers-based system are projected, drawing bounding boxes for vehicles and lines for trajectories.
+&
+%Intersection monitoring &
+%Camera, Lasers &
+%N/A \\
+%\hline
+%
+%\end{xtabular*}
+%\end{table*}
+
+%\begin{table*}[tp]
+%\caption{Developments on Intersection Management Systems}
+%\label{reviewtable}
+%\begin{xtabular*}{\textwidth}{|p{0.08\textwidth}|p{0.41\textwidth}|p{0.15\textwidth}|p{0.12\textwidth}|p{0.121875\linewidth}|}
 %
 %\hline
+%\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
+%\hline
+%
+%
+%\cite{Abbas2009} &
+%Monitoring dilemma zone and efectiveness of control policies using cameras and loop detectors on an intersection &
+%Intersection monitoring &
+%Cameras, loop detectors &
+%N/A \\
+%\hline
+%
+%
+%\cite{Babaei2010} &
+%Author presents a system for foreground extraction, vehicle detection and tracking.
+A novel algorithm is proposed based on image division in traffic zones to perform background removal and vehicle detection.
+This proposal is compared with traditional MoG approach.
+&
+%Intersection monitoring &
+%Camera &
+%N/A \\
+%\hline
+%
+%\cite{Meissner2010} &
+%A semi-automatic calibration method for a network of lidar sensors is presented using a custom simulation environment. Also, a calibration object were designed based on simulation results. &
+%Intersection Monitoring &
+%Lidars &
+%N/A \\
+%\hline
+
+\begin{table*}[tp]
+\footnotesize
+\caption{Developments on Intersection Management Systems}
+\label{reviewtable}
+\begin{xtabular*}{\textwidth}{|p{0.08\textwidth}|p{0.45\textwidth}|p{0.11\textwidth}|p{0.12\textwidth}|p{0.121875\linewidth}|}
+
+\hline
+\textbf{Reference} & \textbf{Comment} & \textbf{Application} & \textbf{Data Source} & \textbf{Communication} \\
+\hline
+
+%\cite{Quinlan2010} &
+%An augmented reality implementation of the system proposed in cite{Dresner2008} is presented.
+In this work, an autonomous vehicle is deployed in a mixed-reality platform and request to an virtual intersection manager for authorisation to cross and is the manager which decides if it is safe to cross or not, depending on the defined traffic policies and the state of virtual vehicles.
+&
+%Intersection management &
+%On-board state sensors &
+%V2I \\
+%\hline
+
+%\cite{Ball2010} &
+%The use of intelligent objects in vehicles is proposed.
+With sharing vehicle state information and jouney plans, the system aims to better control traffic in intersection using a novel back-off protocol instead of time traffic control system.
+&
+%Traffic control &
+%On-board state sensors, Journey plans &
+%V2V \\
+%\hline
+
+\cite{Babaei2011} &
+A system for traffic flow measurement based on anormalities detection is presented. Multiple cameras are used SIFT and unsupervised SVM-based clustering are performed for trajectories analysis. &
+Intersection monitoring &
+Cameras &
+N/A \\
+\hline
+
+\cite{Basma2011} &
+In presented system, wireless magnetic nodes are used to detect presence and to send data to a base station, which determines possible collisions and warns driver through a visualisation system in infrastructure.
+&
+Collision Avoidance	 &
+Presence sensors &
+N/A \\
+\hline
+
+\cite{Azimi2012} &
+An intersection control protocol based on V2V communication is proposed.
+This protocol is in charge of handling other vehicles messages and determines if is it safe or not to cross.
+They present two policies for managing intersection access: Concurrent Crossing- Intersection Protocol (CC-IP) and Maximum Progression-Intersection Protocol (MP-IP).
+&
+Intersection management &
+N/A &
+V2V \\
+\hline
+
+\cite{CondeBento2012} &
+A microscopic simulator was developed, with a spatial-temporal-based approach for managing the intersection.
+It is possible to implement different traffic policies for comparison purposes and the system works on crossroads and roundabouts.
+&
+Intersection management &
+On-board state sensors &
+V2X \\
+\hline
+
+\cite{Zhao2012} &
+A novel approach for detecting moving objects and track them is presented.
+The focus of this work relies on process merged data from laser sensors (\cite{Zhao2009}) to get better results at tracking.
+&
+Object detection and tracking &
+Lasers &
+N/A \\
+\hline
+
+\cite{Jin2012} &
+A Multiagent-based system is proposed.
+They define a Vehicle Agent and and Intersection Agent and propose a protocol for controlling intersection access based on timeslots, Also, the present a vehicle motion planning algorithm.
+Validation and testing was done using SUMO platform &
+Intersection Management &
+On-board state sensors &
+V2I \\
+\hline
+
+\cite{Meissner2012} &
+A set of laser scanners is used for detect and track pedestrians. GMM and DBSCAN are proposed for detection stage. For tracking purpose, a random finite set particle filter is used. &
+Pedestrians detection and tracking &
+Lasers &
+N/A \\
+\hline
+
+\cite{Goldhammer2012} &
+In this work is presented the setting and configuration of a multisensor network, based on 14 lasers, 10 cameras, GPS and V2I unit. Calibration and spatial-temporal alignment is performed. &
+System Architecture &
+Cameras, Lasers &
+V2I \\
+\hline
+
+\cite{Friesen2013} &
+A set of wireless probes are deployed to estimate traffic flow based on bluetooth connections.
+Then, using Zigbee, data is send to a master node which handle data for forwarding to a server / database for further processing.
+&
+Traffic monitoring &
+Wireless sensor network &
+N/A \\
+\hline
+
+\cite{Guerrero-Ibanez2013} &
+Two modes of Intersection Access Control: V2I mode and V2V mode. Implementation was done using minirobots in a scale model of an intersection. &
+Intersection access control &
+Loop detectors and RFID nodes &
+V2X \\
+\hline
+
+%\cite{Meissner2013,Meissner2013a} &
+% &
+% &
+% &
+% \\
+%\hline
+
+\cite{Meissner2013b} &
+A new method for object detection based on lidars data is proposed.
+After perform background removal, they use DBGridSCAN for 3D clustering and 2D pathway tracking.
+Then a combination of 2D-3D is done.
+The proposal is validated using OSPA metric.
+&
+Object Detection &
+Lasers &
+N/A \\
+\hline
+
+\cite{Au2015} &
+On top of AIM (\cite{Dresner2008}) Semi-AIM protocol is proposed.
+Assuming that human-driven vehicles to autonomous vehicles transition will be long, this system is intended for semi-autonomous vehicles.
+Also the author describe the human relation to a semi-autonomous vehicle and analyse how the features of autonomy employed by the car affects the traffic delay.
+&
+Intersection Management &
+On-board state sensors &
+V2I \\
+\hline

### 2019-01-17 ch2-mdf_ims.tex
Detailed levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)

@@
 The JDL fusion model was conceived to aid the developments of military applications and comprises 5 levels of data processing at which data fusion could be done.
-These levels and a database are connected by a bus (\ref{JDLmodel}), and are not meant to be execute sequentially and can also be executed concurrently.
+These levels and a database are connected by a bus (\ref{JDLmodel}), and are not meant to be execute sequentially, and can also be executed concurrently.
 
@@
 
-\todo{Describe level 4 and highlight levels}
+%DONE\todo{Describe level 4 and highlight levels}
 
-The first stage, referred as level-0 is the source preprocessing in which raw data is handled to concentrate the more pertinent data for the current situation.
-The level-1 is for object refinement, starting with the alignment of the data in a commonly space-time reference frame.
+The first stage, referred as \textbf{\textit{level-0}} is the source preprocessing in which raw data is handled to concentrate the more pertinent data for the current situation.
+The \textbf{\textit{level-1}} is for object refinement, starting with the alignment of the data in a commonly space-time reference frame.
 Then, performs identification and tracking of objects using different techniques.
-Situation refinement is at level-2, which takes observed and partially-observed object from level-1 and tries to find a contextual description between them.
-Level-3, threat refinement, is the level in which results from level-2 are interpreted looking for possible advantages and disadvantages for the system to operate, based on previous knowledge and predictions about executing an action.
+Situation refinement is at \textbf{\textit{level-2}}, which takes observed and partially-observed object from level-1 and tries to find a contextual description between them.
+\textbf{\textit{Level-3}}, threat refinement, is the level in which results from level-2 are interpreted looking for possible advantages and disadvantages for the system to operate, based on previous knowledge and predictions about executing an action.
+\textbf{\textit{Level-4}} is in the border of the whole diagram because its tasks are not just about sensor fusion but also on resource management.
+This level monitors the overall
+data fusion process to assess and improve real-time system performance and allocate sensors and sources to collect relevant information for the process.
 
@@
 \todo{Highlight architectures types}
+
 Elmenreich in \cite{Elmenreich2007} classify fusion models in three categories: Abstract models, generic architectures and rigid architectures.
-Abstract model are not intended to show how to implement a sensor fusion system, but to explain which processes are done in it.
-Generic architectures gives an outline on how a system could be implemented in an application, but do not specify what type of hardware, database or communication system could be used.
-Finally, rigid architectures, are a good guide for implementation  of data fusion in certain applications, at the cost that several design decisions have been already taken, making expensive the migration to another architecture.
+\textbf{\textit{Abstract models}} are not intended to show how to implement a sensor fusion system, but to explain which processes are done in it.
+\textbf{\textit{Generic architectures}} gives an outline on how a system could be implemented in an application, but do not specify what type of hardware, database or communication system could be used.
+Finally, \textbf{\textit{Rigid architectures}}, are a good guide for implementation  of data fusion in certain applications, at the cost that several design decisions have been already taken, making expensive the migration to another architecture.
 
@@
 
-\begin{table}
+\begin{table}[ht!]
 \footnotesize

### 2019-01-22 ch3-arch_sys.tex
Added TODOs
Reviewed processing stages and detailed simulation models

@@
 In the fourth stage, object behaviour and inter-objects interaction are analysed to identify context and detect situations or events of interest.
-This output could be delivered to an optional fifth stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
-In figure \ref{proc_stages}, previously described stages are depicted, including a list of common tasks performed at each of these stages and also it is shown how the data volume is reduced while data meaning increases in the last stages.
+This output could be delivered to an automated or semi-automated stage of decision and control, to a human operator, or to a traffic agent or institution, to take immediate actions on traffic control, issue traffic tickets, warn drivers about possible incidents or improve transportation policies in a long-term basis.
+In figure \ref{proc_stages}, previously described stages are depicted, including a list of common tasks performed at each of these stages.
 
@@
 The macroscopic model of traffic flow is based on a hydrodynamic analogy, modeling traffic as a fluid process characterized by three main variables, density, volume and speed, and the objective is to describe time-space evolution of those variables.
+The microscopic model aims to detail at a high detail inter-vehicles interactions and their individual state.
+For example, in a lane-change maneuver the state of the car doing the action and those affected by it, is individually tracked.
+The mesoscopic model tries to include features of both macroscopic and mesoscopic model.
+In this case, the same lane-change maneuver could be seen as an instant action triggered by lane density rather than on individual interactions.
 
@@
 \end{figure}
+
+\todo{Design Considerations}
 

### 2019-01-22 ch3-arch_sys.tex
Fixed JSON definition

@@
 Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options.
-This information is loaded into Redis from a JSON file and it is available for any client requiring it.
+This information is loaded into Redis from a configuration file formatted using JavaScript Object Notation (JSON), available for any client requiring it.
 \todo{Define JSON HERE!!!!}
@@
 \todo{Move JSON definition from here!!!}
-Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.
+Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JSON, allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.
 

### 2019-01-22 ch3-arch_sys.tex
Fixed JSON description and Information structure (2.3.3) and Fixed formatting in section 2.3.4

--- 2019-01-22 ch3-arch_sys.tex
@@
 Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options.
-This information is loaded into Redis from a JSON file and it is available for any client requiring it.
+This information is loaded into Redis from a configuration file formatted using JavaScript Object Notation (JSON), and once loaded in Redis, it is available for any client requiring it.
 \todo{Define JSON HERE!!!!}
@@
 
-The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where is data generated from or where is data going to.
+The purpose of all the labels attributes within each class is to serve as an identifier of the channel in which the entity is publishing or subscribing to; in other words, to identify where data is generated from or where data is going to.
 For example, channel \texttt{/sensors/range/laser\_1/data/raw} contains raw data from a laser scanner labeled as \texttt{"laser\_1"} and \texttt{/legs/leg\_3/occupancy/} refers to the occupancy level of the leg labeled as \texttt{leg\_3}.
@@
 \todo{Move JSON definition from here!!!}
-Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.
+Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JSON, allowing to use any JSON parser/formatter available in different languages.
+In addition,  it is possible to create simple scripts to interact with the system.
+Below are described the two types of data used by the systems: the .imscfg file and the messages and configuration parameters.
 
@@
 
-\begin{description}
-
 \item[virtual\_sensor\_merge] \hfill
@@
 \subsubsection{Situation Assesment}
+\begin{description}
 

### 2019-01-22 ch3-arch_sys.tex
Removed TODOs and added revision history. Updated version

@@
 
-\todo{Check stages description and figure}
+%\todo{Check stages description and figure}
 
@@
 This information is loaded into Redis from a configuration file formatted using JavaScript Object Notation (JSON), and once loaded in Redis, it is available for any client requiring it.
-\todo{Define JSON HERE!!!!}
+
+%\todo{Define JSON HERE!!!!}
 
@@
 
-\todo{Move JSON definition from here!!!}
+%\todo{Move JSON definition from here!!!}
+
 Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JSON, allowing to use any JSON parser/formatter available in different languages.

### 2019-01-22 last_version.tex
Corrections and figures updated.
Corrections in ch 1, 2 and 5
Added TODOs
Removed TODOs and added revision history. Updated version

@@
 %\vfill
+\todo{Update version message and link}
+Version: 1.1 \\
+\vspace{2cm}
 
-Version: 0.8 \\
-\vspace{2cm}
-An updated version of this report can be downloaded from: \\
+\end{center}
+
+Check for an updated version at github: 
 \href{https://github.com/gustavovelascoh/msc-report/raw/master/main.pdf}{Multisensor Architecture for an Intersection Management System}
-    \end{center}
+
+\subsection*{Revision history}
+\subsubsection*{Version 1.1 - 2019-01-24:}
+
+	\begin{itemize}
+	\item Detailed processing levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)
+	\item Fixed V2I description in figure 1.6 (1.2.1)
+	\item Reworded description of processing stages in section 2.1.1
+	\item Described three transportation simulation models (2.2.1)
+	\end{itemize}
+
+\subsubsection*{Version 1.0 - 2018-09-21:}
+	\begin{itemize}
+	\item Initial version
+	\end{itemize}
+
 \end{titlepage}

### 2019-01-22 ch1-introduction.tex
Added information about contribution in section 4.1 (Articles, events and journals)

@@
 
-Chapter 4 summarizes the conclusions of the development of the whole work, remarking on contributions made like software and applications generated, academic products, and future developments and improvements for the system, including application performance, platforms upgrade, UX/UI improvements, scalability and integration with IOT and Smart Cities solutions.
+Chapter 4 summarizes the conclusions of the development of the whole work, remarking on contributions made like software and applications generated, academic products, and future developments and improvements for the system, including application performance, platforms upgrade, UX/UI improvements, scalability and integration with Internet of Things (IOT) and Smart Cities solutions.

### 2019-01-22 ch5-conclusions.tex
Added TODOs
Added information about contribution in section 4.1 (Articles, events and journals)

@@
 
-On the other side, a couple of articles are being reviewed previous to be submmited to a journal.
-One article is a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation, based on chapters 2 and 3.
+%\todo{Detail contributions}
+
+On the other side, a couple of articles have been derived from this work.
+One article, titled "\textit{A Review on Intersection Management Systems and Recent IoT Integrated Approaches}" is a review on intersection management systems, based on chapter 1.
+This article is also focused on how Internet of Things (IOT) has been used for IMS and it remarks recent developments and deployments on this field.
+This article has been submitted to the IEEE 5th World Forum on Internet of Things, which will be held during April 2019 at Limerick, Ireland \footnote{http://wfiot2019.iot.ieee.org/}.
+
+ Another article based on chapters 2 and 3, presents a full description of the architecture and an example implementation.
+This article is still on writing stage and is intended to be submitted to the national journal DYNA\footnote{https://revistas.unal.edu.co/index.php/dyna}.
 

### 2019-01-22 last_version.tex
Added information about contribution in section 4.1 (Articles, events and journals)
Updated link for last version downloading

@@
 Check for an updated version at github: 
-\href{https://github.com/gustavovelascoh/msc-report/raw/master/main.pdf}{Multisensor Architecture for an Intersection Management System}
+\href{https://github.com/gustavovelascoh/msc-report/wiki}{Multisensor Architecture for an Intersection Management System}
 
@@
 	\begin{itemize}
+	\item Updated link for last version downloading
 	\item Detailed processing levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)
@@
 	\item Described three transportation simulation models (2.2.1)
+	\item Added information about contribution in section 4.1 (Articles, events and journals)
 	\end{itemize}

### 2019-01-27 ch4-results.tex
Added TODOs
Format improved in section 3.1 and 3.2.

@@
 Then, two implemented configurations of the system are presented.
-Finally, results are summarized and analysed.
+Finally, results are summarized and analysed, comparing both configurations and different fusion approaches.
 
 \section{Experimental Setup}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.8]{fig/4/intersection-config2.pdf}
-\caption{Possi dataset configuration}
-\label{possi_img}
-\end{figure}
-
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.2]{fig/4/sensors_overview.jpeg}
-\caption{Overview of sensors data. Left: Laser scanners, Right: Camera.}
-\label{possi_sensors}
-\end{figure}
+%\todo{First paragraph then figure}
 
@@
 It contains 6 laser-scanners raw readings and a video from a camera located over the intersection.
-Figure \ref{possi_img} depicts the configuration used by this dataset.
-In figure \ref{possi_sensors} is shown the data from each type of sensors, laser scanners and camera.
+Figure \ref{possi_img} depicts the configuration used by this dataset and the data from each type of sensors, laser scanners and camera.
 The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears.
 This groundtruth data was generated manually.
+
+\begin{figure}[ht!]
+\begin{subfigure}{\textwidth}
+\centering
+\includegraphics[scale=0.8]{fig/4/intersection-config2.pdf}
+\caption{Global configuration}
+\label{possi_img}
+\end{subfigure}
+
+\begin{subfigure}{\textwidth}
+\centering
+\includegraphics[scale=0.2]{fig/4/sensors_overview.jpeg}
+\caption{Overview of sensors data. Left: Laser scanners, Right: Camera.}
+\end{subfigure}
+\caption{Possi dataset configuration.}
+\label{possi_sensors:a}
+\end{figure}
 
@@
 \section{Test Configurations}
+%\todo{First paragraph then figure}
 
@@
 
-The following table lists all used blocks and assigns an ID for each one.
+The table \ref{desc_test_config} lists all used blocks and assigns an ID for each one.
 Those IDs are used in the graph description in its own section.
 Also, bold nodes and connections indicate multiple instance of the same element.
-The figure \ref{tconf1} shows the  configuration used for processing just video data.
-Figure \ref{tconf2} shows the configuration when a set of lasers is added to the single-camera configuration.
+The figure \ref{tconf2} shows the  configuration used for processing just video data the configuration when a set of lasers is added to the previous configuration.
 The blue line represents the fusion at node K, which is fusion on virtual sensors level.
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.6]{fig/4/test_configuration1.pdf}
-\caption{Single camera configuration}
-\label{tconf1}
-\end{figure}
+\todo{Explain evaluation params}
 
 \begin{figure}[ht!]
-\centering
+%\centering
+
+\begin{subfigure}{\textwidth}
+
+\includegraphics[scale=0.6]{fig/4/test_configuration1.pdf}
+\caption{Single camera configuration.}
+%\label{tconf1}
+%\end{figure}
+\end{subfigure}
+
+%\begin{figure}[ht!]
+%\centering
+
+\begin{subfigure}{\textwidth}
 \includegraphics[scale=0.6]{fig/4/test_configuration2.pdf}
-\caption{Multiple lasers and camera configuration}
+\caption{Multiple lasers and camera configuration.}
+
+\end{subfigure}
+\caption{Test configurations.}
 \label{tconf2}
@@
 
+\begin{figure}[htb!]
+\centering
+\includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
+\caption{Results for the multisensor implementation using four different fusion approaches}
+\label{vl_res}
+\end{figure}
+
 \begin{table}[htb!]
@@
 
+\todo{Sumarise and discuss results}
+
 An intersection management system is a complex set of subsystems, and for a feasible implementation and deployment as a real solution it is needed for it to be easily tested, adapted and enhanced.

### 2019-01-28 ch4-results.tex
Added summary table and fixed format

@@
 
-Performing the same frame-based analysis as for the video system, we obtain the confusion matrices presented in table \ref{vl_cf}.
+Performing the same frame-based analysis as for the video system, we obtain the confusion matrices presented in figure \ref{vl_cf}.
 It is noted that performing the fusion at virtual sensor occupancy level, the accuracy of the systems has almost no change, 92.2\% and 91.48\% for average and maximum policies respectively.
@@
 \includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
-\caption{Results for the multisensor implementation using four different fusion approaches}
-\label{vl_res}
+\caption{Fusion configurations: top-left, Average on virtual sensor occupancy. Bottom-left, Maximum on virtual sensor occupancy. Top-right, Average on flow rate. Bottom-rigth, Maximum on flow rate}
+\label{vl_cf}
 \end{figure}
 
-\begin{table}[htb!]
-\footnotesize
-\centering
-\noindent
-\renewcommand\arraystretch{1.5}
-\setlength\tabcolsep{0pt}
-\begin{tabular}{c c c c c}
-  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
-     \multicolumn{4}{c}{\bfseries Outcome (avg vs\_occ)} \\
-  & & \bfseries F & \bfseries S & \bfseries total \\
-  & F$'$ & \MyBox{1098}{} & \MyBox{148}{} & 1246 \\[2.4em]
-  & S$'$ & \MyBox{403}{} & \MyBox{5414}{} & 5817 \\
-  & total & 1501 & 5562 &
-\end{tabular}
-
-\begin{tabular}{c c c c c}
-  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
-     \multicolumn{4}{c}{\bfseries Outcome (max vs\_occ)}  \\
-  & & \bfseries F & \bfseries S & \bfseries total \\
-  & F$'$ & \MyBox{792}{} & \MyBox{454}{} & 1246 \\[2.4em]
-  & S$'$ & \MyBox{148}{} & \MyBox{5669}{} & 5817 \\
-  & total & 940 & 6123 &
-\end{tabular}
-
-\begin{tabular}{c c c c c}
-  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
-     \multicolumn{4}{c}{\bfseries Outcome (avg flow)} \\
-  & & \bfseries F & \bfseries S & \bfseries total \\
-  & F$'$ & \MyBox{161}{} & \MyBox{1085}{} & 1246 \\[2.4em]
-  & S$'$ & \MyBox{13}{} & \MyBox{5804}{} & 5817 \\
-  & total & 174 & 6889 &
-\end{tabular}
-
-\begin{tabular}{c c c c c}
-  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
-     \multicolumn{4}{c}{\bfseries Outcome (max flow)}  \\
-  & & \bfseries F & \bfseries S & \bfseries total \\
-  & F$'$ & \MyBox{716}{} & \MyBox{530}{} & 1246 \\[2.4em]
-  & S$'$ & \MyBox{193}{} & \MyBox{5624}{} & 5817 \\
-  & total & 909 & 6154 &
-\end{tabular}
-
-\caption{Fusion configurations from top to bottom: Average on virtual sensor occupancy, Maximum on virtual sensor occupancy, Average on flow rate, Maximum on flow rate}
-\label{vl_cf}
-\end{table}
+%\begin{table}[htb!]
+%\footnotesize
+%\centering
+%\noindent
+%\renewcommand\arraystretch{1.5}
+%\setlength\tabcolsep{0pt}
+%\begin{tabular}{c c c c c}
+%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+%     \multicolumn{4}{c}{\bfseries Outcome (avg vs\_occ)} \\
+%  & & \bfseries F & \bfseries S & \bfseries total \\
+%  & F$'$ & \MyBox{1098}{} & \MyBox{148}{} & 1246 \\[2.4em]
+%  & S$'$ & \MyBox{403}{} & \MyBox{5414}{} & 5817 \\
+%  & total & 1501 & 5562 &
+%\end{tabular}
+%
+%\begin{tabular}{c c c c c}
+%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+%     \multicolumn{4}{c}{\bfseries Outcome (max vs\_occ)}  \\
+%  & & \bfseries F & \bfseries S & \bfseries total \\
+%  & F$'$ & \MyBox{792}{} & \MyBox{454}{} & 1246 \\[2.4em]
+%  & S$'$ & \MyBox{148}{} & \MyBox{5669}{} & 5817 \\
+%  & total & 940 & 6123 &
+%\end{tabular}
+%
+%\begin{tabular}{c c c c c}
+%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+%     \multicolumn{4}{c}{\bfseries Outcome (avg flow)} \\
+%  & & \bfseries F & \bfseries S & \bfseries total \\
+%  & F$'$ & \MyBox{161}{} & \MyBox{1085}{} & 1246 \\[2.4em]
+%  & S$'$ & \MyBox{13}{} & \MyBox{5804}{} & 5817 \\
+%  & total & 174 & 6889 &
+%\end{tabular}
+%
+%\begin{tabular}{c c c c c}
+%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
+%     \multicolumn{4}{c}{\bfseries Outcome (max flow)}  \\
+%  & & \bfseries F & \bfseries S & \bfseries total \\
+%  & F$'$ & \MyBox{716}{} & \MyBox{530}{} & 1246 \\[2.4em]
+%  & S$'$ & \MyBox{193}{} & \MyBox{5624}{} & 5817 \\
+%  & total & 909 & 6154 &
+%\end{tabular}
+%
+%\caption{Fusion configurations from top to bottom: Average on virtual sensor occupancy, Maximum on virtual sensor occupancy, Average on flow rate, Maximum on flow rate}
+%\label{vl_cf}
+%\end{table}
 
@@
 \todo{Sumarise and discuss results}
+
+\begin{table}[ht!]
+\footnotesize
+\begin{tabular}{c c c c c}
+Test Case & Sensors & Fusion Aproaches & Accuracy & TPR \\
+
+Case 1 & Camera & NA & 91.82\% & 55.7\% \\
+Case 2 & Camera + Lasers & Low-level, Mid-level (avg) & 92.2\% & 88.12\%\\
+Case 2 & Camera + Lasers & Low-level, Mid-level (max) & 91.48\% & 63.56\% \\
+Case 2 & Camera + Lasers & Low-level, High-level (avg) & 84.45\% & 12.92\% \\
+Case 2 & Camera + Lasers & Low-level, High-level (max) & 89.76\% & 57.46\%\\
+
+\end{tabular}
+\caption{Summary of results}
+\label{results}
+\end{table}
 

### 2019-01-28 ch4-results.tex
Figure merged in section 3.3 and added results summary as table 3.3

@@
 Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level.
-In this case, the binary status of a leg (traffic flowing, traffic stopped) is the metric used for evaluation, derived from the vehicle count.
+In this case, the binary status of a leg (traffic flowing, traffic stopped) is the output used for evaluation, derived from the vehicle count.
 
@@
 The figure \ref{tconf2} shows the  configuration used for processing just video data the configuration when a set of lasers is added to the previous configuration.
-The blue line represents the fusion at node K, which is fusion on virtual sensors level.
-The purple line represents the fusion at flow rate level.
-
-\todo{Explain evaluation params}
+The blue line represents the fusion at node K, which is fusion on virtual sensors level (Mid-level fusion).
+The purple line represents the fusion at flow rate level (High-level fusion).
 
@@
 
+As this is a binary classification system, the evaluation metrics used for these implementations, derived from the obtained confusion matrices, are Accuracy and True Positive Rate (TPR).
 %TODO
@@
 \centering
-\includegraphics[scale=0.45]{fig/4/video_res.pdf}
+\includegraphics[scale=0.42]{fig/4/video_res.pdf}
 \caption{Results for the single camera implementation in one of the legs of the intersection}
@@
 \centering
-\includegraphics[scale=0.4]{fig/4/laser1a.png}
+\includegraphics[scale=0.35]{fig/4/laser1a.png}
 \caption{Vehicle detection using laser scanners}
@@
 Using maximum policy, there is a small decrement in the values, with an accuracy of 89.76\% and a TPR of 57.46\%.
+A summary of the results obtained on both test cases is presented in table \ref{results}.
+
+% It can be seen in this table that merging laser data with video data in some cases enhance the classification task.
+But it should be noted that this is an unbalanced dataset, with 17.64 \% of True (Flowing traffic) instances and 82.36 \% of False (Stopped traffic),
 
@@
 \includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
-\caption{Fusion configurations: top-left, Average on virtual sensor occupancy. Bottom-left, Maximum on virtual sensor occupancy. Top-right, Average on flow rate. Bottom-rigth, Maximum on flow rate}
+\caption{Fusion configurations: top-left, Average on virtual sensor occupancy. Bottom-left, Maximum on virtual sensor occupancy. Top-right, Average on flow rate. Bottom-right, Maximum on flow rate}
 \label{vl_cf}
@@
 
-\section{Conclusions}
+%\subsection{Discussion}
 
-\todo{Sumarise and discuss results}
+%\todo{Sumarise and discuss results}
 
@@
 \footnotesize
-\begin{tabular}{c c c c c}
-Test Case & Sensors & Fusion Aproaches & Accuracy & TPR \\
+\begin{tabular}{|c| c| c| c| c|}
 
+\hline
+\textbf{Test Case} & \textbf{Sensors} & \textbf{Fusion Aproaches} & \textbf{Accuracy} & \textbf{TPR} \\
+\hline
 Case 1 & Camera & NA & 91.82\% & 55.7\% \\
+\hline
 Case 2 & Camera + Lasers & Low-level, Mid-level (avg) & 92.2\% & 88.12\%\\
+\hline
 Case 2 & Camera + Lasers & Low-level, Mid-level (max) & 91.48\% & 63.56\% \\
+\hline
 Case 2 & Camera + Lasers & Low-level, High-level (avg) & 84.45\% & 12.92\% \\
+\hline
 Case 2 & Camera + Lasers & Low-level, High-level (max) & 89.76\% & 57.46\%\\
-
+\hline
 \end{tabular}
@@
 \end{table}
+
+\section{Conclusions}
 
@@
 Also, it is important to understand if the fusion is competitive, complementary or cooperative, in order to select the appropiate strategy and increase the performance of the system.
-An example of this, was found when fusing data from camera and lasers at two different levels and using different strategies.
-It was clear from the results that altough the data was the same, one configuration increased the performace while another one decrease it.
+An example of this was demonstrated when fusing data from camera and lasers at two different levels and using different strategies.
+It was clear from the results (table \ref{results}) that altough the data was the same, one configuration increased the performace while another one decrease it.

### 2019-01-28 ch3-arch_sys.tex
Figures reordered and format improved in sections 2.3.4

@@
 
-\todo{Design Considerations}
+%\todo{Design Considerations}
+
+As the implementation of a full Intersection Management System is a joint effort among different fields of engineering (Hardware, software, IT, civl) and even non-engineering areas, The two main features chosen for this proposal are scalability and modularity.
+Scalability is desired in the cases where an initial deployment needs to expand or increase its complexity in any of its areas, for example, new communication approaches, add new sensors or hardware, develop new features or policies, etc.
+Modularity allows that the internal blocks of system could be modified, exchanged or enhanced without disturbing the overall function of the deployment.
+This criteria is achieved with the four proposed elements of this architecture: communication scheme, data model, information structure and processing blocks.
 
@@
 For this reason, it also takes a laser\_cfg parameter to include laser position information in the conversion.
-Output message contains a set of x, y points obtained from the following equations:
+Output message contains a set of x, y points, referenced to a global coordinate system.
+This output is obtained from the following equations:
 
@@
 
+\hfill
 \item[laser\_cart\_merge] \hfill
@@
 This block takes as input messages of type laser\_cart\_msg coming from different sensors and merges them into a single message, based on a sampling period $T$.
+The objective of this stage is to set a common time-frame and synchronize all the messages to feed to the next blocks.
 
@@
 \item[points\_to\_cluster] \hfill
+
+The input message for this block is a set of points corresponding to objects scanned by lasers.
+Clustering is performed over this input to identify the points belonging to the same object.
+The algorithm used in this implementation is DBSCAN, which stands for Density-Based Spatial Clustering of Applications with Noise.
+This algorithm does not need an estimated number of clusters as input, instead of this, it requires only two parameters: a minimum number of points per cluster, m, and a neighbourhood measure, $\epsilon$.
+A detailed description of the algorithm, can be found in \cite{Ester96}.
 
@@
 
+\hfill
+
 \item[virtual\_sensor\_merge] \hfill
+This block is intended to take as inputs different messages of type vs\_occ\_msg and merging them to increase the reliabilty of detection.
+First, a moving average is calculated over each input to reduce the effect of false positives or false negatives in a single frame.
+After this, the inputs are merged by a defined method like average, weighted average, maximum or minimum.
+Then, a new vs\_occ\_msg message is dispatched as output.
 \begin{figure}[ht!]
@@
 
-This block is intended to take as inputs different messages of type vs\_occ\_msg and merging them to increase the reliabilty of detection.
-First, a moving average is calculated over each input to reduce the effect of false positives or false negatives in a single frame.
-After this, the inputs are merged by a defined method like average, weighted average, maximum or minimum.
-Then, a new vs\_occ\_msg message is dispatched as output.
-
 \end{description}
@@
 \item[virtual\_sensor\_to\_flow\_rate] \hfill
+
+When a message of type vs\_occ\_msg arrives, it is evaluated using a threshold $vo_{th}$, if the occupancy percentage of a virtual sensor is greater than $vo_{th}$, it is considered that there is a vehicle over the sensor in that frame, this is defined as occupied state.
+This detection is made in a frame basis, thus, a vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
+
 \begin{figure}[ht!]
@@
 
-When a message of type vs\_occ\_msg arrives, it is evaluated using a threshold $vo_{th}$, if the occupancy percentage of a virtual sensor is greater than $vo_{th}$, it is considered that there is a vehicle over the sensor in that frame, this is defined as occupied state.
-This detection is made in a frame basis, thus, a vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.
-
 Then, a time interval $t_{c}$ is defined for calculating the flow rate $v_{r}$.
@@
 
+\hfill
+
 \item[flow\_rate\_to\_flow\_status] \hfill
+
+This block process one or more inputs of type flow\_rate\_msg.
+If there are more than one input, it merges them using defined policy, like average or maximum.
+Then, if the flow rate $v_{r}$ is above a flow threshold $f_{th}$, it is considered that the traffic is flowing.
+Otherwise, traffic is considered stopped.
+
 \begin{figure}[ht!]
@@
 
-This block process one or more inputs of type flow\_rate\_msg.
-If there are more than one input, it merges them using defined policy, like average or maximum.
-Then, if the flow rate $v_{r}$ is above a flow threshold $f_{th}$, it is considered that the traffic is flowing.
-Otherwise, traffic is considered stopped.
-
 \end{description}
@@
 \item[laser\_publisher] \hfill
+
+These blocks are intended to read dataset files containing the information from the sensors and publish this data with the appropriate format and preserving the original rate of the sensors, if needed.
+
 \begin{figure}[ht!]
@@
 \end{figure}
-
-These blocks are intended to read dataset files containing the information from the sensors and publish this data with the appropriate format and preserving the original rate of the sensors, if needed.
 

### 2019-01-28 last_version.tex
Format improved in section 3.1 and 3.2.
Figures reordered and format improved in sections 2.3.4
updated changelog
Updated changelog with pages number.

@@
 %\vfill
-\todo{Update version message and link}
+%\todo{Update version message and link}
 Version: 1.1 \\
@@
 \subsection*{Revision history}
-\subsubsection*{Version 1.1 - 2019-01-24:}
+\footnotesize
+\subsubsection*{Version 1.1 - 2019-01-28:}
 
@@
 	\item Updated link for last version downloading
-	\item Detailed processing levels in JDL model (1.1.1) and detailed categories in data fusion architectures (1.1.2)
-	\item Fixed V2I description in figure 1.6 (1.2.1)
-	\item Reworded description of processing stages in section 2.1.1
-	\item Described three transportation simulation models (2.2.1)
-	\item Added information about contribution in section 4.1 (Articles, events and journals)
+	\item Detailed processing levels in JDL model  in section 1.1.1 (p.15)
+	\item Detailed categories in data fusion architectures in section 1.1.2 (p.17)
+	\item Fixed V2I description in figure 1.6 (p.21)
+	\item Reworded description of processing stages in section 2.1.1 (p.34)
+	\item Described simulation models used in transportation (p.35)
+	\item Explained design considerations in section 2.3 (p.36)
+	\item Figures reordered, format improved and details added in section 2.3.4 (p.39)
+	\item Figures merged in sections 3.1 and 3.2 (p.50)
+	\item Detailed Test configurations in section 3.2 (p.51)
+	\item Figures and tables reordered in section 3.3 (p.52)
+	\item Added results summary in table 3.3 (p.54)
+	\item Added detailed information about contributions in section 4.1 (p.58)
 	\end{itemize}

### 2020-07-15 paper02/paper02.tex
Changes figure 1 to table 1
Update paper02.dvi, paper02.pdf, and 2 more files...

@@
 
+\input{table_comp}
+\end{xtabular*}
+\end{table*}
+
 \section{Intersection Management Systems}
@@
 Those applications have to take into account some of the elements depicted in figure \ref{arch} and developments in IMS have a wide range of approaches and objectives.
-In order to study IMS applications, five components have been defined, which are present on these applications, and on most cases, more than one component could be involved in the same development.
-In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them, and next, a description of each component is given.
+In order to study IMS applications, five components have been defined which are present on those applications, and on most cases, more than one component could be involved in the same development.
+Table \ref{imsComps} describe aforementioned components and elements within them along with a brief description.
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[scale=0.17]{../fig/2/ims_graph5.png}
-\caption{Components of an Intersection Management System application.}
-\label{imsComps}
-\end{figure}
+%INTERSECTION MANAGEMENT SYSTEM	Application	Monitoring	Recognition
+%			Detection
+%			Tracking
+%		Control	Traffic control
+%			Warning advertisement
+%			Traffic rules supervision
+%		Analysis	Traffic flow
+%			Path analysis
+%			Context and behavior
+%	Data source	Infrastructure	Presence sensors
+%			Range sensors
+%			Image sensors 
+%			RFID and wireless
+%		Vehicle	Position
+%			State 
+%			Travel information
+%	Target		Pedestrians
+%			Bicycles / Motorcycles
+%			Small Vehicles
+%			Large Vehicles 
+%	Communication		V2V -Vehicle -to-vehicle
+%			V2I - Vehicle-2-vehicle
+%			V2X
+%	Implementation		Real
+%			Simulation
+%			Augmented Reality
+%			Dataset
+%			Scala-model
 
@@
 \hline
+
 {\cite{Tan2011}} &
-{Proposal of using IOT-based set of sensors as source of data for intersection control} &
+{Proposal of using an IOT-based set of sensors as source of data for intersection control.\vfill} &
 {Simulation}\\

### 2020-07-15 paper02/paper02.tex
Update paper02.pdf, paper02.tex, and table_sample.tex

@@
 
+\section{IoT ready IMS architecture proposal}
+
+The implementation of a full Intersection Management System that is enable for Internet of Things solutions, is a joint effort among different fields of engineering (Hardware, software, IT, civil) and even non-engineering areas, the two main features chosen for this proposal are scalability and modularity.
+Scalability is desired in the cases where an initial deployment needs to expand or increase its complexity in any of its areas, for example, new communication approaches, add new sensors or hardware, develop new features or policies, etc.
+Modularity allows that the internal blocks of system could be modified, exchanged or enhanced without disturbing the overall function of the deployment.
+This criteria is achieved with the four proposed elements of this architecture: communication scheme, data model, information structure and processing blocks.
+A block diagram describin the architecture is shown in figure \ref{proposal_blocks}.
+
+\begin{figure}[ht!]
+\centering
+\includegraphics[scale=0.5]{../fig/3/proposal_blocks.pdf}
+\caption{General overview of proposed architecture and its components. Red for the communication scheme, green for data model and blue for processing blocks}
+\label{proposal_blocks}
+\end{figure}
+
+In order to isolate the processing tasks of the \textit{communication system}, a Publisher-Subscriber approach is selected.
+The benefits of this option is that data can be shared between diferent blocks without generating a dependency from publishers to subscribers.
+Another benefit is that exposing a defined mechanism for publishing or subscribing, allows the system to be implementation agnostic.
+
+The \textit{data model} proposed for the system includes the abstraction of the sensing elements and the intersection model.
+Sensor elements will include the technical parameters and will provide an interface for controlling them and accessing the data generated.
+The intersection has should be modeled as a unit that includes its geometry properties, traffic direction and the relation with the sensors in it.
+
+The \textit{information structure} will define the way in which configuration and runtime information is stored and exchanged.
+In order to keep the system language-agnostic and highly integrable, formats like JSON or markup language should be using for static files and established serialisation option are the way to go for data exchanging, because they usually provide APIs for their adoption in different platforms.
+
+Processing blocks in an IMS can be divided into four stages in the processing flow: preprocessing, feature analysis, pattern recognition and situation assessment.
+To keep the modularity and scalability as principles of the architecture, these block must be isolated processes, exchanging data through the defined communication system and sticking to the data model and the information structure provided.
+This will also allow that the processes could be sparse across different processing units
+
 \section{Conclusions}
@@
 
+The two main contributions derived from this work is a comprehensive review of intersection management systems and a proposed scalable and modular architecture for traffic monitoring at an intersection enable for its integration with IoT systems.
+
 Oncoming advances in computing capabilities, low-power platforms, and a variety of communication protocols, open a door to newer and optimized solutions.
-Also, these allow the generation of joint solution with a wider scope, not just for transportation, but for social or environmental scenarios, having a higher impact on society.
+Also, these allow the generation of joint solutions with a wider scope, not just for transportation, but for social or environmental scenarios, having a higher impact on society.
 

### 2020-07-15 paper02/table_sample.tex
Update paper02.pdf, paper02.tex, and table_sample.tex

@@
 
-%\cite{Quinlan2010} &
-%An augmented reality implementation of the system proposed in cite{Dresner2008} is presented.
+\cite{Quinlan2010} &
+An augmented reality implementation of the system proposed in cite{Dresner2008} is presented.
 In this work, an autonomous vehicle is deployed in a mixed-reality platform and request to an virtual intersection manager for authorisation to cross and is the manager which decides if it is safe to cross or not, depending on the defined traffic policies and the state of virtual vehicles.
-&
-%Intersection management &
-%On-board state sensors &
-%V2I \\
-%\hline
+\vfill &
+Intersection management &
+On-board state sensors &
+V2I  \\
+\hline
 
-%\cite{Ball2010} &
-%The use of intelligent objects in vehicles is proposed.
+\cite{Ball2010} &
+The use of intelligent objects in vehicles is proposed.
 With sharing vehicle state information and jouney plans, the system aims to better control traffic in intersection using a novel back-off protocol instead of time traffic control system.
 &
-%Traffic control &
-%On-board state sensors, Journey plans &
-%V2V \\
-%\hline
+Traffic control &
+On-board state sensors, Journey plans &
+V2V \\
+\hline
 
@@
 Then a combination of 2D-3D is done.
-The proposal is validated using OSPA metric.
-&
+The proposal is validated using OSPA metric.\vfill &
 Object Detection &
